---
title: "Online Appendix C.9: Macro-Level Models — Economic Immigration Attitudes"
subtitle: "National Economic Context, National Identity, and Economic Immigration Attitudes"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-location: left
    theme: cosmo
    embed-resources: true
    echo: false
    warning: false
    message: false
    fig-width: 8
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(lubridate)
library(fixest)
library(haven)
library(modelsummary)
library(kableExtra)

options(modelsummary_factory_default = "kableExtra")

GOF_MAP <- tribble(
  ~raw,                  ~clean,          ~fmt,
  "nobs",                "Observations",  0,
  "FE: id",              "Individual FE", 0,
  "FE: wave",            "Wave FE",       0,
  "adj.r.squared",       "Adj. R²",       3,
  "within.r.squared",    "Within R²",     6,
  "rmse",                "RMSE",          3
)

zap_if_labelled <- function(x) {
  if (inherits(x, "haven_labelled")) return(zap_labels(x))
  x
}

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE          <- "immigEcon"
BRIT_BASE        <- "britishness"
ENG_BASE         <- "englishness"
TIME_BASE        <- "starttime"
AGE_BASE         <- "age"
MACRO_GDP_BASE   <- "gdp_pc"
MACRO_UNEMP_BASE <- "unempl_rate"
MACRO_CLAIM_BASE <- "claimant_k"
MACRO_CPIH_BASE  <- "cpih_rate"

get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base) {
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

macro_long_from_base <- function(df, base, waves_keep) {
  cols <- paste0(base, "W", waves_keep)
  df |>
    select(id, any_of(cols)) |>
    pivot_longer(cols = -id, names_to = "wave",
                 names_pattern = paste0("^", base, "W(\\d+)$"),
                 values_to = base) |>
    mutate(wave = as.integer(wave))
}
```

```{r build-panel-brit, include=FALSE}
w_dv    <- waves_available(df, DV_BASE)
w_brit  <- waves_available(df, BRIT_BASE)
w_time  <- waves_available(df, TIME_BASE)
w_age   <- waves_available(df, AGE_BASE)
w_gdp   <- waves_available(df, MACRO_GDP_BASE)
w_unemp <- waves_available(df, MACRO_UNEMP_BASE)
w_claim <- waves_available(df, MACRO_CLAIM_BASE)
w_cpih  <- waves_available(df, MACRO_CPIH_BASE)

waves_core  <- Reduce(intersect, list(w_dv, w_brit, w_time))
waves_macro <- Reduce(intersect, list(waves_core, w_gdp, w_unemp, w_claim, w_cpih))
waves_age   <- intersect(waves_macro, w_age)

core_cols <- c(
  paste0(DV_BASE,   "W", waves_macro),
  paste0(BRIT_BASE, "W", waves_macro),
  paste0(TIME_BASE, "W", waves_macro),
  paste0(AGE_BASE,  "W", waves_age)
)

df_core <- df |>
  mutate(across(any_of(core_cols), zap_if_labelled)) |>
  select(id, any_of(core_cols))

df_long_core <- df_core |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", BRIT_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), brit = all_of(BRIT_BASE))

df_long_time <- df_core |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long <- left_join(df_long_core, df_long_time, by = c("id", "wave"))

if (length(waves_age) > 0) {
  age_long <- df_core |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long <- left_join(df_long, age_long, by = c("id", "wave"))
}

df_long <- df_long |>
  mutate(time = suppressWarnings(ymd_hms(time, quiet = TRUE)),
         year = year(time),
         brit = as.numeric(brit),
         dv   = as.numeric(dv),
         age  = as.numeric(age)) |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro), by = c("id", "wave")) |>
  mutate(brit_num = as.numeric(brit),
         brit_cat = relevel(factor(brit_num, levels = 1:7), ref = "7"))
```

```{r build-panel-engl, include=FALSE}
w_eng <- waves_available(df, ENG_BASE)
waves_core_eng  <- Reduce(intersect, list(w_dv, w_eng, w_time))
waves_macro_eng <- Reduce(intersect, list(waves_core_eng, w_gdp, w_unemp, w_claim, w_cpih))
waves_age_eng   <- intersect(waves_macro_eng, w_age)

core_cols_eng <- c(
  paste0(DV_BASE,  "W", waves_macro_eng),
  paste0(ENG_BASE, "W", waves_macro_eng),
  paste0(TIME_BASE,"W", waves_macro_eng),
  paste0(AGE_BASE, "W", waves_age_eng)
)

df_core_eng <- df |>
  mutate(across(any_of(core_cols_eng), zap_if_labelled)) |>
  select(id, any_of(core_cols_eng))

df_long_core_eng <- df_core_eng |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", ENG_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), engl = all_of(ENG_BASE))

df_long_time_eng <- df_core_eng |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long_eng <- left_join(df_long_core_eng, df_long_time_eng, by = c("id", "wave"))

if (length(waves_age_eng) > 0) {
  age_long_eng <- df_core_eng |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long_eng <- left_join(df_long_eng, age_long_eng, by = c("id", "wave"))
}

df_long_eng <- df_long_eng |>
  mutate(time = suppressWarnings(ymd_hms(time, quiet = TRUE)),
         year = year(time),
         dv   = as.numeric(dv),
         engl = as.numeric(engl),
         age  = as.numeric(age),
         engl = dplyr::na_if(engl, 9999)) |>
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave)) |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro_eng), by = c("id", "wave")) |>
  mutate(engl_num = as.numeric(engl),
         engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7"))

stopifnot(all(c("dv", "engl", "wave", "id") %in% names(df_long_eng)))
```

```{r estimate-brit, include=FALSE}
models_unemp <- list(
  main_0     = feols(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main       = feols(dv ~ brit + unempl_rate        | id + wave,        data = df_long, cluster = ~id),
  main_age_0 = feols(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age   = feols(dv ~ brit + unempl_rate + age  | id + wave,        data = df_long, cluster = ~id),
  int        = feols(dv ~ brit * unempl_rate        | id + wave,        data = df_long, cluster = ~id),
  int_age    = feols(dv ~ brit * unempl_rate + age  | id + wave,        data = df_long, cluster = ~id)
)

models_claim <- list(
  main_0     = feols(dv ~ claimant_k + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main       = feols(dv ~ brit + claimant_k        | id + wave,        data = df_long, cluster = ~id),
  main_age_0 = feols(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age   = feols(dv ~ brit + claimant_k + age  | id + wave,        data = df_long, cluster = ~id),
  int        = feols(dv ~ brit * claimant_k        | id + wave,        data = df_long, cluster = ~id),
  int_age    = feols(dv ~ brit * claimant_k + age  | id + wave,        data = df_long, cluster = ~id)
)

models_gdp <- list(
  main_0     = feols(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main       = feols(dv ~ brit + gdp_pc        | id + wave,        data = df_long, cluster = ~id),
  main_age_0 = feols(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age   = feols(dv ~ brit + gdp_pc + age  | id + wave,        data = df_long, cluster = ~id),
  int        = feols(dv ~ brit * gdp_pc        | id + wave,        data = df_long, cluster = ~id),
  int_age    = feols(dv ~ brit * gdp_pc + age  | id + wave,        data = df_long, cluster = ~id)
)

models_cpih <- list(
  main_0     = feols(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main       = feols(dv ~ brit + cpih_rate        | id + wave,        data = df_long, cluster = ~id),
  main_age_0 = feols(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age   = feols(dv ~ brit + cpih_rate + age  | id + wave,        data = df_long, cluster = ~id),
  int        = feols(dv ~ brit * cpih_rate        | id + wave,        data = df_long, cluster = ~id),
  int_age    = feols(dv ~ brit * cpih_rate + age  | id + wave,        data = df_long, cluster = ~id)
)

brit_econ_rob <- list(
  gdp   = feols(brit ~ gdp_pc      + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  unemp = feols(brit ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  claim = feols(brit ~ claimant_k  + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  cpih  = feols(brit ~ cpih_rate   + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id)
)
```

```{r estimate-brit-cat, include=FALSE}
run_macro_cat_brit <- function(varname) {
  list(
    main     = feols(as.formula(paste0("dv ~ brit_cat + ", varname, " | id + wave")),
                     data = df_long, cluster = ~id),
    main_age = feols(as.formula(paste0("dv ~ brit_cat + ", varname, " + age | id + wave")),
                     data = df_long, cluster = ~id),
    int      = feols(as.formula(paste0("dv ~ brit_cat * ", varname, " | id + wave")),
                     data = df_long, cluster = ~id),
    int_age  = feols(as.formula(paste0("dv ~ brit_cat * ", varname, " + age | id + wave")),
                     data = df_long, cluster = ~id)
  )
}

models_unemp_cat <- run_macro_cat_brit("unempl_rate")
models_claim_cat <- run_macro_cat_brit("claimant_k")
models_gdp_cat   <- run_macro_cat_brit("gdp_pc")
models_cpih_cat  <- run_macro_cat_brit("cpih_rate")
```

```{r estimate-engl, include=FALSE}
models_unemp_eng <- list(
  main_0     = feols(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main       = feols(dv ~ engl + unempl_rate        | id + wave,        data = df_long_eng, cluster = ~id),
  main_age_0 = feols(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age   = feols(dv ~ engl + unempl_rate + age  | id + wave,        data = df_long_eng, cluster = ~id),
  int        = feols(dv ~ engl * unempl_rate        | id + wave,        data = df_long_eng, cluster = ~id),
  int_age    = feols(dv ~ engl * unempl_rate + age  | id + wave,        data = df_long_eng, cluster = ~id)
)

models_claim_eng <- list(
  main_0     = feols(dv ~ claimant_k + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main       = feols(dv ~ engl + claimant_k        | id + wave,        data = df_long_eng, cluster = ~id),
  main_age_0 = feols(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age   = feols(dv ~ engl + claimant_k + age  | id + wave,        data = df_long_eng, cluster = ~id),
  int        = feols(dv ~ engl * claimant_k        | id + wave,        data = df_long_eng, cluster = ~id),
  int_age    = feols(dv ~ engl * claimant_k + age  | id + wave,        data = df_long_eng, cluster = ~id)
)

models_gdp_eng <- list(
  main_0     = feols(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main       = feols(dv ~ engl + gdp_pc        | id + wave,        data = df_long_eng, cluster = ~id),
  main_age_0 = feols(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age   = feols(dv ~ engl + gdp_pc + age  | id + wave,        data = df_long_eng, cluster = ~id),
  int        = feols(dv ~ engl * gdp_pc        | id + wave,        data = df_long_eng, cluster = ~id),
  int_age    = feols(dv ~ engl * gdp_pc + age  | id + wave,        data = df_long_eng, cluster = ~id)
)

models_cpih_eng <- list(
  main_0     = feols(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main       = feols(dv ~ engl + cpih_rate        | id + wave,        data = df_long_eng, cluster = ~id),
  main_age_0 = feols(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age   = feols(dv ~ engl + cpih_rate + age  | id + wave,        data = df_long_eng, cluster = ~id),
  int        = feols(dv ~ engl * cpih_rate        | id + wave,        data = df_long_eng, cluster = ~id),
  int_age    = feols(dv ~ engl * cpih_rate + age  | id + wave,        data = df_long_eng, cluster = ~id)
)

engl_econ_rob <- list(
  gdp   = feols(engl ~ gdp_pc      + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  unemp = feols(engl ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  claim = feols(engl ~ claimant_k  + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  cpih  = feols(engl ~ cpih_rate   + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id)
)
```

```{r estimate-engl-cat, include=FALSE}
run_macro_cat_engl <- function(varname) {
  list(
    main     = feols(as.formula(paste0("dv ~ engl_cat + ", varname, " | id + wave")),
                     data = df_long_eng, cluster = ~id),
    main_age = feols(as.formula(paste0("dv ~ engl_cat + ", varname, " + age | id + wave")),
                     data = df_long_eng, cluster = ~id),
    int      = feols(as.formula(paste0("dv ~ engl_cat * ", varname, " | id + wave")),
                     data = df_long_eng, cluster = ~id),
    int_age  = feols(as.formula(paste0("dv ~ engl_cat * ", varname, " + age | id + wave")),
                     data = df_long_eng, cluster = ~id)
  )
}

models_unemp_eng_cat <- run_macro_cat_engl("unempl_rate")
models_claim_eng_cat <- run_macro_cat_engl("claimant_k")
models_gdp_eng_cat   <- run_macro_cat_engl("gdp_pc")
models_cpih_eng_cat  <- run_macro_cat_engl("cpih_rate")
```

---

This appendix reports the full model output supporting the macro-level analysis of economic immigration attitudes. All models use individual fixed effects with standard errors clustered at the respondent level. The outcome throughout is `immigEcon`, which asks respondents whether immigration undermines or enriches British economic performance; higher values indicate more permissive attitudes. The structure mirrors Appendix C exactly: Section C.9.1 presents the main Britishness models for all four macro indicators; Section C.9.2 reports the categorical Britishness robustness check; Section C.9.3 presents the Englishness models; Section C.9.4 reports the categorical Englishness robustness check; and Section C.9.5 reports the auxiliary models testing whether macro conditions predict national identification. The macro-level identification strategy is identical to Appendix C: macro indicators vary only at the national–wave level, so their main effects are absorbed by wave fixed effects in the `id + wave` FE models; polynomial-trend models (`poly(wave, 3)`) are used where the direct association needs to be identified.

---

# C.9.1 Main Models: Britishness (Continuous) {#sec-c8-brit}

## C.9.1.1 National Unemployment Rate {#sec-c8-brit-unemp}

```{r c8-brit-unemp-main}
modelsummary(
  list("(1) Direct (poly)" = models_unemp$main_0, "(2) + Britishness" = models_unemp$main,
       "(3) Direct + Age (poly)" = models_unemp$main_age_0, "(4) + Britishness" = models_unemp$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.1. National Unemployment Rate and Economic Immigration Attitudes: Main Effects (Britishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp$int, "(2) Interaction + Age" = models_unemp$int_age),
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate",
                  "brit:unempl_rate" = "Britishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.2. National Unemployment Rate × Britishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.1.2 National Claimant Count {#sec-c8-brit-claim}

```{r c8-brit-claim-main}
modelsummary(
  list("(1) Direct (poly)" = models_claim$main_0, "(2) + Britishness" = models_claim$main,
       "(3) Direct + Age (poly)" = models_claim$main_age_0, "(4) + Britishness" = models_claim$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.3. National Claimant Count and Economic Immigration Attitudes: Main Effects (Britishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-brit-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim$int, "(2) Interaction + Age" = models_claim$int_age),
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)",
                  "brit:claimant_k" = "Britishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.4. National Claimant Count × Britishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.1.3 GDP per Capita {#sec-c8-brit-gdp}

```{r c8-brit-gdp-main}
modelsummary(
  list("(1) Direct (poly)" = models_gdp$main_0, "(2) + Britishness" = models_gdp$main,
       "(3) Direct + Age (poly)" = models_gdp$main_age_0, "(4) + Britishness" = models_gdp$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.5. GDP per Capita and Economic Immigration Attitudes: Main Effects (Britishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-brit-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp$int, "(2) Interaction + Age" = models_gdp$int_age),
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita",
                  "brit:gdp_pc" = "Britishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.6. GDP per Capita × Britishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.1.4 CPIH Inflation {#sec-c8-brit-cpih}

```{r c8-brit-cpih-main}
modelsummary(
  list("(1) Direct (poly)" = models_cpih$main_0, "(2) + Britishness" = models_cpih$main,
       "(3) Direct + Age (poly)" = models_cpih$main_age_0, "(4) + Britishness" = models_cpih$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.7. CPIH Inflation and Economic Immigration Attitudes: Main Effects (Britishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-brit-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih$int, "(2) Interaction + Age" = models_cpih$int_age),
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation",
                  "brit:cpih_rate" = "Britishness × CPIH", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.8. CPIH Inflation × Britishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.9.2 Robustness: Britishness (Categorical) {#sec-c8-brit-cat}

Categorical Britishness specifications confirm the gradient structure and moderation patterns documented in Section C.9.1. Britishness category coefficients are positive, precisely estimated, and monotonically ordered across all four indicators, indicating that respondents with weaker national identification are consistently more permissive toward immigration in economic terms relative to the most strongly British group. The interaction patterns mirror those in Appendix C.2.

## C.9.2.1 National Unemployment Rate {#sec-c8-cat-brit-unemp}

```{r c8-cat-brit-unemp}
modelsummary(
  list("(1) No age" = models_unemp_cat$main, "(2) Age" = models_unemp_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.9. Unemployment Rate: Britishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_cat$int, "(2) Interaction + Age" = models_unemp_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.10. Unemployment Rate × Britishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.2.2 National Claimant Count {#sec-c8-cat-brit-claim}

```{r c8-cat-brit-claim}
modelsummary(
  list("(1) No age" = models_claim_cat$main, "(2) Age" = models_claim_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.11. Claimant Count: Britishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-brit-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_cat$int, "(2) Interaction + Age" = models_claim_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.12. Claimant Count × Britishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.2.3 GDP per Capita {#sec-c8-cat-brit-gdp}

```{r c8-cat-brit-gdp}
modelsummary(
  list("(1) No age" = models_gdp_cat$main, "(2) Age" = models_gdp_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.13. GDP per Capita: Britishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-brit-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_cat$int, "(2) Interaction + Age" = models_gdp_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.14. GDP per Capita × Britishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.2.4 CPIH Inflation {#sec-c8-cat-brit-cpih}

```{r c8-cat-brit-cpih}
modelsummary(
  list("(1) No age" = models_cpih_cat$main, "(2) Age" = models_cpih_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.15. CPIH Inflation: Britishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-brit-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_cat$int, "(2) Interaction + Age" = models_cpih_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.16. CPIH Inflation × Britishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.9.3 Main Models: Englishness (Continuous) {#sec-c8-engl}

The Englishness cultural DV models replicate the Britishness structure with Englishness as the identity moderator, following the same logic as Appendix C.3. Consistent with the `immigSelf` results, macro-economic conditions condition economic immigration attitudes more strongly through Englishness than through Britishness across most indicators.

## C.9.3.1 National Unemployment Rate {#sec-c8-engl-unemp}

```{r c8-engl-unemp-main}
modelsummary(
  list("(1) Direct (poly)" = models_unemp_eng$main_0, "(2) + Englishness" = models_unemp_eng$main,
       "(3) Direct + Age (poly)" = models_unemp_eng$main_age_0, "(4) + Englishness" = models_unemp_eng$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.17. National Unemployment Rate and Economic Immigration Attitudes: Main Effects (Englishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng$int, "(2) Interaction + Age" = models_unemp_eng$int_age),
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate",
                  "engl:unempl_rate" = "Englishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.18. National Unemployment Rate × Englishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.3.2 National Claimant Count {#sec-c8-engl-claim}

```{r c8-engl-claim-main}
modelsummary(
  list("(1) Direct (poly)" = models_claim_eng$main_0, "(2) + Englishness" = models_claim_eng$main,
       "(3) Direct + Age (poly)" = models_claim_eng$main_age_0, "(4) + Englishness" = models_claim_eng$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.19. National Claimant Count and Economic Immigration Attitudes: Main Effects (Englishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng$int, "(2) Interaction + Age" = models_claim_eng$int_age),
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)",
                  "engl:claimant_k" = "Englishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.20. National Claimant Count × Englishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.3.3 GDP per Capita {#sec-c8-engl-gdp}

```{r c8-engl-gdp-main}
modelsummary(
  list("(1) Direct (poly)" = models_gdp_eng$main_0, "(2) + Englishness" = models_gdp_eng$main,
       "(3) Direct + Age (poly)" = models_gdp_eng$main_age_0, "(4) + Englishness" = models_gdp_eng$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.21. GDP per Capita and Economic Immigration Attitudes: Main Effects (Englishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng$int, "(2) Interaction + Age" = models_gdp_eng$int_age),
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita",
                  "engl:gdp_pc" = "Englishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.22. GDP per Capita × Englishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.3.4 CPIH Inflation {#sec-c8-engl-cpih}

```{r c8-engl-cpih-main}
modelsummary(
  list("(1) Direct (poly)" = models_cpih_eng$main_0, "(2) + Englishness" = models_cpih_eng$main,
       "(3) Direct + Age (poly)" = models_cpih_eng$main_age_0, "(4) + Englishness" = models_cpih_eng$main_age),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.23. CPIH Inflation and Economic Immigration Attitudes: Main Effects (Englishness)",
  notes = "Cols 1 & 3: individual FE + cubic wave polynomial. Cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng$int, "(2) Interaction + Age" = models_cpih_eng$int_age),
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation",
                  "engl:cpih_rate" = "Englishness × CPIH", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.24. CPIH Inflation × Englishness: Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. DV: immigEcon. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.9.4 Robustness: Englishness (Categorical) {#sec-c8-engl-cat}

Categorical Englishness specifications confirm the gradient and moderation patterns from Section C.9.3. Englishness category coefficients are positive, precisely estimated, and monotonically ordered across all four indicators.

## C.9.4.1 National Unemployment Rate {#sec-c8-cat-engl-unemp}

```{r c8-cat-engl-unemp}
modelsummary(
  list("(1) No age" = models_unemp_eng_cat$main, "(2) Age" = models_unemp_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.25. Unemployment Rate: Englishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng_cat$int, "(2) Interaction + Age" = models_unemp_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.26. Unemployment Rate × Englishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.4.2 National Claimant Count {#sec-c8-cat-engl-claim}

```{r c8-cat-engl-claim}
modelsummary(
  list("(1) No age" = models_claim_eng_cat$main, "(2) Age" = models_claim_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.27. Claimant Count: Englishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng_cat$int, "(2) Interaction + Age" = models_claim_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.28. Claimant Count × Englishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.4.3 GDP per Capita {#sec-c8-cat-engl-gdp}

```{r c8-cat-engl-gdp}
modelsummary(
  list("(1) No age" = models_gdp_eng_cat$main, "(2) Age" = models_gdp_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.29. GDP per Capita: Englishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng_cat$int, "(2) Interaction + Age" = models_gdp_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.30. GDP per Capita × Englishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.9.4.4 CPIH Inflation {#sec-c8-cat-engl-cpih}

```{r c8-cat-engl-cpih}
modelsummary(
  list("(1) No age" = models_cpih_eng_cat$main, "(2) Age" = models_cpih_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.31. CPIH Inflation: Englishness (Categorical) Main Effects (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-cat-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng_cat$int, "(2) Interaction + Age" = models_cpih_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.32. CPIH Inflation × Englishness (Categorical): Interaction Models (Economic DV)",
  notes = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigEcon.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.9.5 Auxiliary: Do Macro Conditions Predict National Identification? {#sec-c8-rob}

As in Appendix C.5, the tables below confirm that none of the four macro indicators predicts within-individual changes in Britishness or Englishness. The interaction effects in Sections C.9.1–C.9.4 therefore reflect contextual moderation of the identity–attitude relationship rather than macro-induced identity change, consistent with the `immigSelf` findings.

```{r c8-rob-brit}
modelsummary(
  list("GDP" = brit_econ_rob$gdp, "Unemp." = brit_econ_rob$unemp,
       "Claimant" = brit_econ_rob$claim, "CPIH" = brit_econ_rob$cpih),
  coef_omit   = "poly\\(wave",
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.33. Auxiliary: Do Macro Conditions Predict Britishness?",
  notes = "Individual FE + cubic wave polynomial. SEs clustered by respondent. DV: Britishness (1–7). Wave polynomial suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c8-rob-engl}
modelsummary(
  list("GDP" = engl_econ_rob$gdp, "Unemp." = engl_econ_rob$unemp,
       "Claimant" = engl_econ_rob$claim, "CPIH" = engl_econ_rob$cpih),
  coef_omit   = "poly\\(wave",
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C9.34. Auxiliary: Do Macro Conditions Predict Englishness?",
  notes = "Individual FE + cubic wave polynomial. SEs clustered by respondent. DV: Englishness (1–7). Wave polynomial suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

*End of Appendix C.9.*
