---
title: "BES_Micro_Random_Effects"
format: html
editor: visual
---

```{r 0, include=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(fixest)
library(haven)
library(purrr)
library(lme4)      # for lmer (random effects)
library(lmerTest)  # for p-values in lmer

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE   <- "immigSelf"
BRIT_BASE <- "britishness"
TIME_BASE <- "starttime"
AGE_BASE  <- "age"   

get_wave_num2 <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available2 <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num2)))
}

make_long_with_age <- function(df,
                               dv_base   = "immigSelf",
                               brit_base = "britishness",
                               time_base = "starttime",
                               age_base  = "age"){

  w_dv   <- waves_available2(df, dv_base)
  w_brit <- waves_available2(df, brit_base)
  w_time <- waves_available2(df, time_base)
  w_age  <- waves_available2(df, age_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_age))
  if(length(waves) < 3) stop("Too few overlapping waves across DV, britishness, starttime, and age.")

  dv_cols   <- paste0(dv_base,   "W", waves)
  brit_cols <- paste0(brit_base, "W", waves)
  time_cols <- paste0(time_base, "W", waves)
  age_cols  <- paste0(age_base,  "W", waves)

  df2 <- df |>
    mutate(
      across(all_of(dv_cols),   ~ as.numeric(zap_labels(.x))),
      across(all_of(brit_cols), ~ as.numeric(zap_labels(.x))),
      across(all_of(age_cols),  ~ as.numeric(zap_labels(.x)))
    )

  df2 |>
    select(id, all_of(dv_cols), all_of(brit_cols), all_of(time_cols), all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(starttime_parsed, suppressWarnings(ymd(starttime_chr, quiet = TRUE))),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv   = all_of(dv_base),
      brit = all_of(brit_base),
      age  = all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(age), !is.na(wave))
}

panel_self <- make_long_with_age(df, DV_BASE, BRIT_BASE, TIME_BASE, AGE_BASE)
```

```{r 1 sanity, warning=FALSE, message=FALSE, echo=FALSE}
panel_self |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(id),
    min_wave = min(wave),
    max_wave = max(wave),
    min_year = min(year, na.rm = TRUE),
    max_year = max(year, na.rm = TRUE),
    age_min = min(age, na.rm = TRUE),
    age_max = max(age, na.rm = TRUE)
  )
```

## Micro level results — Random Effects

### Base Models

```{r models_re, echo=FALSE, message=FALSE, warning=FALSE}

# Model 1 RE: brit + (1|id) + (1|wave)
m1_re <- lmer(
  dv ~ brit + (1 | id) + (1 | wave),
  data = panel_self,
  REML = TRUE
)

summary(m1_re)

# Model 2 RE: brit + age + (1|id) + (1|wave)
m2_re <- lmer(
  dv ~ brit + age + (1 | id) + (1 | wave),
  data = panel_self,
  REML = TRUE
)

summary(m2_re)

```

TEXT HERE - TBD

```{r flexible_wave_re, echo=FALSE, warning=FALSE, message=FALSE}

# Wave-specific effect of Britishness (wave × brit interaction; random intercept for id)
m_wave_re <- lmer(
  dv ~ brit * factor(wave) + (1 | id),
  data = panel_self,
  REML = TRUE
)

summary(m_wave_re)

```

TEXT HERE - TBD

### Economic Context Moderation: Individual Income

```{r income_0_re, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

INCOME_BASE <- "income"

get_wave_num <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num)))
}

make_long_with_income <- function(df,
                                  dv_base,
                                  brit_base,
                                  time_base,
                                  income_base,
                                  age_base = NULL){

  w_dv     <- waves_available(df, dv_base)
  w_brit   <- waves_available(df, brit_base)
  w_time   <- waves_available(df, time_base)
  w_income <- waves_available(df, income_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_income))

  if(!is.null(age_base)){
    w_age <- waves_available(df, age_base)
    waves <- intersect(waves, w_age)
  }

  if(length(waves) < 3){
    stop("Too few overlapping waves across DV, britishness, time, income (and age).")
  }

  dv_cols     <- paste0(dv_base,     "W", waves)
  brit_cols   <- paste0(brit_base,   "W", waves)
  time_cols   <- paste0(time_base,   "W", waves)
  income_cols <- paste0(income_base, "W", waves)
  age_cols    <- if(!is.null(age_base)) paste0(age_base, "W", waves) else NULL

  df2 <- df |>
    mutate(
      across(all_of(dv_cols),     ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(brit_cols),   ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(income_cols), ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(age_cols),    ~ as.numeric(haven::zap_labels(.x)))
    )

  df2 |>
    select(id,
           all_of(dv_cols),
           all_of(brit_cols),
           all_of(time_cols),
           all_of(income_cols),
           all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(
        starttime_parsed,
        suppressWarnings(ymd(starttime_chr, quiet = TRUE))
      ),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv     = all_of(dv_base),
      brit   = all_of(brit_base),
      income = all_of(income_base),
      age    = if(!is.null(age_base)) all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(income), !is.na(wave))
}

panel_income_noage <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, INCOME_BASE, age_base = NULL
)

panel_income_age <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, INCOME_BASE, age_base = AGE_BASE
)

# (0.1) Income sole, no age
m_inc_0.1_re <- lmer(
  dv ~ income + (1 | id) + (1 | wave),
  data = panel_income_noage,
  REML = TRUE
)

# (1) brit + income, no age
m_inc_1_re <- lmer(
  dv ~ brit + income + (1 | id) + (1 | wave),
  data = panel_income_noage,
  REML = TRUE
)

# (0.2) Income sole, with age
m_inc_0.2_re <- lmer(
  dv ~ income + age + (1 | id) + (1 | wave),
  data = panel_income_age,
  REML = TRUE
)

# (2) brit + income + age
m_inc_2_re <- lmer(
  dv ~ brit + income + age + (1 | id) + (1 | wave),
  data = panel_income_age,
  REML = TRUE
)

# (3) Moderation, no age
m_inc_3_re <- lmer(
  dv ~ brit * income + (1 | id) + (1 | wave),
  data = panel_income_noage,
  REML = TRUE
)

# (4) Moderation, with age
m_inc_4_re <- lmer(
  dv ~ brit * income + age + (1 | id) + (1 | wave),
  data = panel_income_age,
  REML = TRUE
)
```

```{r income_1_re, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_inc_0.1_re)
summary(m_inc_1_re)
summary(m_inc_0.2_re)
summary(m_inc_2_re)
summary(m_inc_3_re)
summary(m_inc_4_re)
```

TEXT HERE - TBD

```{r income_equivalised_re, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

eq_long <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/equivalised_income_long.rds")

eq_long <- eq_long %>%
  mutate(
    id   = as.character(id),
    wave = as.integer(wave)
  )

panel_eq_noage <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, income_base = INCOME_BASE, age_base = NULL
) %>%
  left_join(eq_long, by = c("id", "wave"))

panel_eq_age <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, income_base = INCOME_BASE, age_base = AGE_BASE
) %>%
  left_join(eq_long, by = c("id", "wave"))

panel_eq03_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child03))
panel_eq03_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child03))
panel_eq05_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child05))
panel_eq05_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child05))

if(nrow(panel_eq03_noage) == 0 || nrow(panel_eq03_age) == 0){
  stop("No non-missing income_eq_child03 observations after merge.")
}
if(nrow(panel_eq05_noage) == 0 || nrow(panel_eq05_age) == 0){
  stop("No non-missing income_eq_child05 observations after merge.")
}

# --- Bound A: child weight = 0.3 ---
m_eq03_0.1_re <- lmer(dv ~ income_eq_child03 + (1|id) + (1|wave),               data = panel_eq03_noage, REML = TRUE)
m_eq03_1_re   <- lmer(dv ~ brit + income_eq_child03 + (1|id) + (1|wave),         data = panel_eq03_noage, REML = TRUE)
m_eq03_0.2_re <- lmer(dv ~ income_eq_child03 + age + (1|id) + (1|wave),          data = panel_eq03_age,   REML = TRUE)
m_eq03_2_re   <- lmer(dv ~ brit + income_eq_child03 + age + (1|id) + (1|wave),   data = panel_eq03_age,   REML = TRUE)
m_eq03_3_re   <- lmer(dv ~ brit * income_eq_child03 + (1|id) + (1|wave),         data = panel_eq03_noage, REML = TRUE)
m_eq03_4_re   <- lmer(dv ~ brit * income_eq_child03 + age + (1|id) + (1|wave),   data = panel_eq03_age,   REML = TRUE)

# --- Bound B: child weight = 0.5 ---
m_eq05_0.1_re <- lmer(dv ~ income_eq_child05 + (1|id) + (1|wave),               data = panel_eq05_noage, REML = TRUE)
m_eq05_1_re   <- lmer(dv ~ brit + income_eq_child05 + (1|id) + (1|wave),         data = panel_eq05_noage, REML = TRUE)
m_eq05_0.2_re <- lmer(dv ~ income_eq_child05 + age + (1|id) + (1|wave),          data = panel_eq05_age,   REML = TRUE)
m_eq05_2_re   <- lmer(dv ~ brit + income_eq_child05 + age + (1|id) + (1|wave),   data = panel_eq05_age,   REML = TRUE)
m_eq05_3_re   <- lmer(dv ~ brit * income_eq_child05 + (1|id) + (1|wave),         data = panel_eq05_noage, REML = TRUE)
m_eq05_4_re   <- lmer(dv ~ brit * income_eq_child05 + age + (1|id) + (1|wave),   data = panel_eq05_age,   REML = TRUE)
```

```{r income_equivalised_results_1_re, echo=FALSE, warning=FALSE, message=FALSE}
# Bound A: child weight = 0.3
summary(m_eq03_0.1_re)
summary(m_eq03_1_re)
summary(m_eq03_0.2_re)
summary(m_eq03_2_re)
summary(m_eq03_3_re)
summary(m_eq03_4_re)
```

TEXT HERE - TBD

```{r income_equivalised_results_2_re, echo=FALSE, warning=FALSE, message=FALSE}
# Bound B: child weight = 0.5
summary(m_eq05_0.1_re)
summary(m_eq05_1_re)
summary(m_eq05_0.2_re)
summary(m_eq05_2_re)
summary(m_eq05_3_re)
summary(m_eq05_4_re)
```

TEXT HERE - TBD

### Economic Context Moderation: Individual risk (fear of unemployment)

```{r risk_0_re, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

RISK_BASE <- "riskUnemployment"

panel_risk_noage <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, income_base = RISK_BASE, age_base = NULL
) %>%
  rename(risk_unemp = income) %>%
  mutate(risk_unemp = if_else(between(risk_unemp, 0, 10), risk_unemp, NA_real_)) %>%
  filter(!is.na(risk_unemp))

panel_risk_age <- make_long_with_income(
  df, DV_BASE, BRIT_BASE, TIME_BASE, income_base = RISK_BASE, age_base = AGE_BASE
) %>%
  rename(risk_unemp = income) %>%
  mutate(risk_unemp = if_else(between(risk_unemp, 0, 10), risk_unemp, NA_real_)) %>%
  filter(!is.na(risk_unemp))

m_risk_0.1_re <- lmer(dv ~ risk_unemp + (1|id) + (1|wave),                data = panel_risk_noage, REML = TRUE)
m_risk_1_re   <- lmer(dv ~ brit + risk_unemp + (1|id) + (1|wave),          data = panel_risk_noage, REML = TRUE)
m_risk_0.2_re <- lmer(dv ~ risk_unemp + age + (1|id) + (1|wave),           data = panel_risk_age,   REML = TRUE)
m_risk_2_re   <- lmer(dv ~ brit + risk_unemp + age + (1|id) + (1|wave),    data = panel_risk_age,   REML = TRUE)
m_risk_3_re   <- lmer(dv ~ brit * risk_unemp + (1|id) + (1|wave),          data = panel_risk_noage, REML = TRUE)
m_risk_4_re   <- lmer(dv ~ brit * risk_unemp + age + (1|id) + (1|wave),    data = panel_risk_age,   REML = TRUE)
```

```{r risk_1_re, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_risk_0.1_re)
summary(m_risk_1_re)
summary(m_risk_0.2_re)
summary(m_risk_2_re)
summary(m_risk_3_re)
summary(m_risk_4_re)
```

TEXT HERE - TBD

```{r risk_2_re, echo=FALSE, warning=FALSE, message=FALSE}

# Diagnostic: Does unemployment risk predict Britishness?
m_brit_risk_noage_re <- lmer(
  brit ~ risk_unemp + (1|id) + (1|wave),
  data = panel_risk_noage,
  REML = TRUE
)

m_brit_risk_re <- lmer(
  brit ~ risk_unemp + age + (1|id) + (1|wave),
  data = panel_risk_age,
  REML = TRUE
)

summary(m_brit_risk_noage_re)
summary(m_brit_risk_re)
```

TEXT HERE - TBD

## Robustness Checks

### Britishness as Categorical

```{r 0.1_re, include=FALSE, echo=FALSE}

panel_self <- panel_self |>
  mutate(
    brit_cat = factor(brit, levels = 1:7),
    brit_cat = relevel(brit_cat, ref = "7")
  )

panel_income_noage <- panel_income_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_income_age <- panel_income_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_risk_noage <- panel_risk_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_risk_age <- panel_risk_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq_noage <- panel_eq_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq_age <- panel_eq_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq03_noage <- panel_eq03_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq03_age <- panel_eq03_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq05_noage <- panel_eq05_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq05_age <- panel_eq05_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

# Global optimizer settings for all lmer models
ctrl <- lmerControl(
  optimizer = "bobyqa",
  optCtrl = list(maxfun = 2e5)
)

```

#### Base Models

```{r brit_cat_re, echo=FALSE, warning=FALSE, message=FALSE}

m1_cat_re <- lmer(
  dv ~ brit_cat + (1|id) + (1|wave),
  data = panel_self,
  REML = TRUE,
  control = ctrl
)

m2_cat_re <- lmer(
  dv ~ brit_cat + age + (1|id) + (1|wave),
  data = panel_self,
  REML = TRUE,
  control = ctrl
)

# Wave-specific categorical: brit_cat × wave interaction
m_wave_cat_re <- lmer(
  dv ~ brit_cat * factor(wave) + (1|id),
  data = panel_self,
  REML = TRUE
)

summary(m1_cat_re)
summary(m2_cat_re)
summary(m_wave_cat_re)
```

TEXT HERE - TBD

#### Economic Context Moderation: Individual Income

```{r brit_cat_income_re, echo=FALSE, warning=FALSE, message=FALSE}

m_inc_cat_1_re <- lmer(dv ~ brit_cat + income + (1|id) + (1|wave),               data = panel_income_noage, REML = TRUE,
  control = ctrl)
m_inc_cat_2_re <- lmer(dv ~ brit_cat + income + age + (1|id) + (1|wave),          data = panel_income_age,   REML = TRUE,
  control = ctrl)
m_inc_cat_3_re <- lmer(dv ~ brit_cat * income + (1|id) + (1|wave),                data = panel_income_noage, REML = TRUE,
  control = ctrl)
m_inc_cat_4_re <- lmer(dv ~ brit_cat * income + age + (1|id) + (1|wave),          data = panel_income_age,   REML = TRUE,
  control = ctrl)

m_eq03_cat_1_re <- lmer(dv ~ brit_cat + income_eq_child03 + (1|id) + (1|wave),              data = panel_eq03_noage, REML = TRUE,
  control = ctrl)
m_eq03_cat_2_re <- lmer(dv ~ brit_cat + income_eq_child03 + age + (1|id) + (1|wave),         data = panel_eq03_age,   REML = TRUE,
  control = ctrl)
m_eq03_cat_3_re <- lmer(dv ~ brit_cat * income_eq_child03 + (1|id) + (1|wave),               data = panel_eq03_noage, REML = TRUE,
  control = ctrl)
m_eq03_cat_4_re <- lmer(dv ~ brit_cat * income_eq_child03 + age + (1|id) + (1|wave),         data = panel_eq03_age,   REML = TRUE,
  control = ctrl)

m_eq05_cat_1_re <- lmer(dv ~ brit_cat + income_eq_child05 + (1|id) + (1|wave),              data = panel_eq05_noage, REML = TRUE,
  control = ctrl)
m_eq05_cat_2_re <- lmer(dv ~ brit_cat + income_eq_child05 + age + (1|id) + (1|wave),         data = panel_eq05_age,   REML = TRUE,
  control = ctrl)
m_eq05_cat_3_re <- lmer(dv ~ brit_cat * income_eq_child05 + (1|id) + (1|wave),               data = panel_eq05_noage, REML = TRUE,
  control = ctrl)
m_eq05_cat_4_re <- lmer(dv ~ brit_cat * income_eq_child05 + age + (1|id) + (1|wave),         data = panel_eq05_age,   REML = TRUE,
  control = ctrl)

summary(m_inc_cat_1_re)
summary(m_inc_cat_2_re)
summary(m_inc_cat_3_re)
summary(m_inc_cat_4_re)
summary(m_eq03_cat_1_re)
summary(m_eq03_cat_2_re)
summary(m_eq03_cat_3_re)
summary(m_eq03_cat_4_re)
summary(m_eq05_cat_1_re)
summary(m_eq05_cat_2_re)
summary(m_eq05_cat_3_re)
summary(m_eq05_cat_4_re)
```

TEXT HERE - TBD

#### Economic Context Moderation: Individual risk (fear of unemployment)

```{r brit_cat_risk_re, echo=FALSE, warning=FALSE, message=FALSE}

m_risk_cat_1_re <- lmer(dv ~ brit_cat + risk_unemp + (1|id) + (1|wave),            data = panel_risk_noage, REML = TRUE,
  control = ctrl)
m_risk_cat_2_re <- lmer(dv ~ brit_cat + risk_unemp + age + (1|id) + (1|wave),       data = panel_risk_age,   REML = TRUE,
  control = ctrl)
m_risk_cat_3_re <- lmer(dv ~ brit_cat * risk_unemp + (1|id) + (1|wave),             data = panel_risk_noage, REML = TRUE,
  control = ctrl)
m_risk_cat_4_re <- lmer(dv ~ brit_cat * risk_unemp + age + (1|id) + (1|wave),       data = panel_risk_age,   REML = TRUE,
  control = ctrl)

summary(m_risk_cat_1_re)
summary(m_risk_cat_2_re)
summary(m_risk_cat_3_re)
summary(m_risk_cat_4_re)
```

TEXT HERE - TBD

### Other measures of nationalism

TEXT HERE - TBD

```{r eng_brit_plot_re, echo=FALSE, message=FALSE, warning=FALSE}

library(ggplot2)

ids_wave <- df %>%
  select(
    id,
    matches("^britishnessW\\d+$"),
    matches("^englishnessW\\d+$")
  ) %>%
  mutate(across(-id, ~ as.numeric(zap_labels(.)))) %>%
  pivot_longer(
    cols = -id,
    names_to = c("identity", "wave"),
    names_pattern = "(britishness|englishness)W(\\d+)",
    values_to = "value"
  ) %>%
  mutate(
    wave = as.integer(wave),
    identity = recode(identity,
                      britishness = "Britishness",
                      englishness = "Englishness"),
    value = if_else(value %in% 1:7, value, NA_real_)
  ) %>%
  group_by(identity, wave) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), .groups = "drop")

ggplot(ids_wave, aes(wave, mean_value, color = identity)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(
    x = "BES Wave",
    y = "Mean identity strength (1–7)",
    color = "Identity",
    title = "Evolution of Britishness and Englishness across BES waves"
  )

ids_wave_dm <- ids_wave %>%
  group_by(identity) %>%
  mutate(mean_dm = mean_value - mean(mean_value, na.rm = TRUE))

ggplot(ids_wave_dm, aes(wave, mean_dm, color = identity)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey60") +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(
    x = "BES Wave",
    y = "Deviation from identity mean",
    color = "Identity",
    title = "Within-wave change: Britishness vs Englishness"
  )
```

TEXT HERE - TBD

::: callout-note
Britishness and Englishness are not measured in every BES wave. The figure plots wave-specific means for each identity in the waves in which it is observed, aligned to the common BES wave index for descriptive comparison.
:::

```{r englishness_base_models_re, echo=FALSE, message=FALSE, warning=FALSE}

ENG_BASE <- "englishness"

panel_self_eng <- make_long_with_age(
  df,
  dv_base   = DV_BASE,
  brit_base = ENG_BASE,
  time_base = TIME_BASE,
  age_base  = AGE_BASE
) %>%
  rename(engl = brit) %>%
  mutate(engl = if_else(engl %in% 1:7, engl, NA_real_))

m1_eng_re <- lmer(
  dv ~ engl + (1|id) + (1|wave),
  data = panel_self_eng,
  REML = TRUE
)

m2_eng_re <- lmer(
  dv ~ engl + age + (1|id) + (1|wave),
  data = panel_self_eng,
  REML = TRUE
)

m_wave_eng_re <- lmer(
  dv ~ engl * factor(wave) + (1|id),
  data = panel_self_eng,
  REML = TRUE
)

summary(m1_eng_re)
summary(m2_eng_re)
summary(m_wave_eng_re)
```

TEXT HERE - TBD

```{r englishness_income_models_re, echo=FALSE, message=FALSE, warning=FALSE}

ENG_BASE <- "englishness"

panel_eng_eq_noage <- make_long_with_income(
  df, dv_base = DV_BASE, brit_base = ENG_BASE,
  time_base = TIME_BASE, income_base = INCOME_BASE, age_base = NULL
) %>%
  dplyr::rename(engl = brit) %>%
  dplyr::mutate(engl = dplyr::if_else(engl %in% 1:7, engl, NA_real_)) %>%
  dplyr::left_join(eq_long, by = c("id", "wave"))

panel_eng_eq_age <- make_long_with_income(
  df, dv_base = DV_BASE, brit_base = ENG_BASE,
  time_base = TIME_BASE, income_base = INCOME_BASE, age_base = AGE_BASE
) %>%
  dplyr::rename(engl = brit) %>%
  dplyr::mutate(engl = dplyr::if_else(engl %in% 1:7, engl, NA_real_)) %>%
  dplyr::left_join(eq_long, by = c("id", "wave"))

panel_eng_eq03_noage <- panel_eng_eq_noage %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child03))
panel_eng_eq03_age   <- panel_eng_eq_age   %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child03))
panel_eng_eq05_noage <- panel_eng_eq_noage %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child05))
panel_eng_eq05_age   <- panel_eng_eq_age   %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child05))

# child weight = 0.3
m_eng_eq03_0.1_re <- lmer(dv ~ income_eq_child03 + (1|id) + (1|wave),              data = panel_eng_eq03_noage, REML = TRUE)
m_eng_eq03_1_re   <- lmer(dv ~ engl + income_eq_child03 + (1|id) + (1|wave),        data = panel_eng_eq03_noage, REML = TRUE)
m_eng_eq03_0.2_re <- lmer(dv ~ income_eq_child03 + age + (1|id) + (1|wave),         data = panel_eng_eq03_age,   REML = TRUE)
m_eng_eq03_2_re   <- lmer(dv ~ engl + income_eq_child03 + age + (1|id) + (1|wave),  data = panel_eng_eq03_age,   REML = TRUE)
m_eng_eq03_3_re   <- lmer(dv ~ engl * income_eq_child03 + (1|id) + (1|wave),        data = panel_eng_eq03_noage, REML = TRUE)
m_eng_eq03_4_re   <- lmer(dv ~ engl * income_eq_child03 + age + (1|id) + (1|wave),  data = panel_eng_eq03_age,   REML = TRUE)

# child weight = 0.5
m_eng_eq05_0.1_re <- lmer(dv ~ income_eq_child05 + (1|id) + (1|wave),              data = panel_eng_eq05_noage, REML = TRUE)
m_eng_eq05_1_re   <- lmer(dv ~ engl + income_eq_child05 + (1|id) + (1|wave),        data = panel_eng_eq05_noage, REML = TRUE)
m_eng_eq05_0.2_re <- lmer(dv ~ income_eq_child05 + age + (1|id) + (1|wave),         data = panel_eng_eq05_age,   REML = TRUE)
m_eng_eq05_2_re   <- lmer(dv ~ engl + income_eq_child05 + age + (1|id) + (1|wave),  data = panel_eng_eq05_age,   REML = TRUE)
m_eng_eq05_3_re   <- lmer(dv ~ engl * income_eq_child05 + (1|id) + (1|wave),        data = panel_eng_eq05_noage, REML = TRUE)
m_eng_eq05_4_re   <- lmer(dv ~ engl * income_eq_child05 + age + (1|id) + (1|wave),  data = panel_eng_eq05_age,   REML = TRUE)

summary(m_eng_eq03_0.1_re); summary(m_eng_eq03_1_re); summary(m_eng_eq03_0.2_re)
summary(m_eng_eq03_2_re);   summary(m_eng_eq03_3_re); summary(m_eng_eq03_4_re)
summary(m_eng_eq05_0.1_re); summary(m_eng_eq05_1_re); summary(m_eng_eq05_0.2_re)
summary(m_eng_eq05_2_re);   summary(m_eng_eq05_3_re); summary(m_eng_eq05_4_re)
```

TEXT HERE - TBD

```{r englishness_risk_models_re, echo=FALSE, message=FALSE, warning=FALSE}

ENG_BASE  <- "englishness"
RISK_BASE <- "riskUnemployment"

panel_risk_noage_eng <- make_long_with_income(
  df, dv_base = DV_BASE, brit_base = ENG_BASE,
  time_base = TIME_BASE, income_base = RISK_BASE, age_base = NULL
) %>%
  rename(engl = brit, risk_unemp = income) %>%
  mutate(
    engl       = if_else(engl %in% 1:7, engl, NA_real_),
    risk_unemp = if_else(risk_unemp >= 0 & risk_unemp <= 10, risk_unemp, NA_real_)
  )

panel_risk_age_eng <- make_long_with_income(
  df, dv_base = DV_BASE, brit_base = ENG_BASE,
  time_base = TIME_BASE, income_base = RISK_BASE, age_base = AGE_BASE
) %>%
  rename(engl = brit, risk_unemp = income) %>%
  mutate(
    engl       = if_else(engl %in% 1:7, engl, NA_real_),
    risk_unemp = if_else(risk_unemp >= 0 & risk_unemp <= 10, risk_unemp, NA_real_)
  )

m_risk_eng_0.1_re <- lmer(dv ~ risk_unemp + (1|id) + (1|wave),               data = panel_risk_noage_eng, REML = TRUE)
m_risk_eng_1_re   <- lmer(dv ~ engl + risk_unemp + (1|id) + (1|wave),         data = panel_risk_noage_eng, REML = TRUE)
m_risk_eng_0.2_re <- lmer(dv ~ risk_unemp + age + (1|id) + (1|wave),          data = panel_risk_age_eng,   REML = TRUE)
m_risk_eng_2_re   <- lmer(dv ~ engl + risk_unemp + age + (1|id) + (1|wave),   data = panel_risk_age_eng,   REML = TRUE)
m_risk_eng_3_re   <- lmer(dv ~ engl * risk_unemp + (1|id) + (1|wave),         data = panel_risk_noage_eng, REML = TRUE)
m_risk_eng_4_re   <- lmer(dv ~ engl * risk_unemp + age + (1|id) + (1|wave),   data = panel_risk_age_eng,   REML = TRUE)

summary(m_risk_eng_0.1_re)
summary(m_risk_eng_1_re)
summary(m_risk_eng_0.2_re)
summary(m_risk_eng_2_re)
summary(m_risk_eng_3_re)
summary(m_risk_eng_4_re)
```

TEXT HERE - TBD

```{r englishness_risk_diagnostic_re, echo=FALSE, message=FALSE, warning=FALSE}

# Diagnostic: Does unemployment risk predict Englishness?
m_engl_risk_noage_re <- lmer(
  engl ~ risk_unemp + (1|id) + (1|wave),
  data = panel_risk_noage_eng,
  REML = TRUE
)

m_engl_risk_re <- lmer(
  engl ~ risk_unemp + age + (1|id) + (1|wave),
  data = panel_risk_age_eng,
  REML = TRUE
)

summary(m_engl_risk_noage_re)
summary(m_engl_risk_re)
```

TEXT HERE - TBD

```{r englishness_categorical_micro_re, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

panel_self_eng <- panel_self_eng %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_num = if_else(engl_num %in% 1:7, engl_num, NA_real_),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_eng_eq03_noage <- panel_eng_eq03_noage %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

panel_eng_eq03_age <- panel_eng_eq03_age %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

panel_eng_eq05_noage <- panel_eng_eq05_noage %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

panel_eng_eq05_age <- panel_eng_eq05_age %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

panel_risk_noage_eng <- panel_risk_noage_eng %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

panel_risk_age_eng <- panel_risk_age_eng %>%
  mutate(engl_num = as.numeric(engl), engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")) %>%
  filter(!is.na(engl_num))

# Base models
m1_eng_cat_re <- lmer(dv ~ engl_cat + (1|id) + (1|wave),          data = panel_self_eng, REML = TRUE,
  control = ctrl)
m2_eng_cat_re <- lmer(dv ~ engl_cat + age + (1|id) + (1|wave),     data = panel_self_eng, REML = TRUE,
  control = ctrl)
m_wave_eng_cat_re <- lmer(dv ~ engl_cat * factor(wave) + (1|id),   data = panel_self_eng, REML = TRUE,
  control = ctrl)

# eq03
m_eng_eq03_cat_1_re <- lmer(dv ~ engl_cat + income_eq_child03 + (1|id) + (1|wave),             data = panel_eng_eq03_noage, REML = TRUE,
  control = ctrl)
m_eng_eq03_cat_2_re <- lmer(dv ~ engl_cat + income_eq_child03 + age + (1|id) + (1|wave),        data = panel_eng_eq03_age,   REML = TRUE,
  control = ctrl)
m_eng_eq03_cat_3_re <- lmer(dv ~ engl_cat * income_eq_child03 + (1|id) + (1|wave),              data = panel_eng_eq03_noage, REML = TRUE,
  control = ctrl)
m_eng_eq03_cat_4_re <- lmer(dv ~ engl_cat * income_eq_child03 + age + (1|id) + (1|wave),        data = panel_eng_eq03_age,   REML = TRUE,
  control = ctrl)

# eq05
m_eng_eq05_cat_1_re <- lmer(dv ~ engl_cat + income_eq_child05 + (1|id) + (1|wave),             data = panel_eng_eq05_noage, REML = TRUE,
  control = ctrl)
m_eng_eq05_cat_2_re <- lmer(dv ~ engl_cat + income_eq_child05 + age + (1|id) + (1|wave),        data = panel_eng_eq05_age,   REML = TRUE,
  control = ctrl)
m_eng_eq05_cat_3_re <- lmer(dv ~ engl_cat * income_eq_child05 + (1|id) + (1|wave),              data = panel_eng_eq05_noage, REML = TRUE,
  control = ctrl)
m_eng_eq05_cat_4_re <- lmer(dv ~ engl_cat * income_eq_child05 + age + (1|id) + (1|wave),        data = panel_eng_eq05_age,   REML = TRUE,
  control = ctrl)

# risk
m_risk_eng_cat_1_re <- lmer(dv ~ engl_cat + risk_unemp + (1|id) + (1|wave),            data = panel_risk_noage_eng, REML = TRUE,
  control = ctrl)
m_risk_eng_cat_2_re <- lmer(dv ~ engl_cat + risk_unemp + age + (1|id) + (1|wave),       data = panel_risk_age_eng,   REML = TRUE,
  control = ctrl)
m_risk_eng_cat_3_re <- lmer(dv ~ engl_cat * risk_unemp + (1|id) + (1|wave),             data = panel_risk_noage_eng, REML = TRUE,
  control = ctrl)
m_risk_eng_cat_4_re <- lmer(dv ~ engl_cat * risk_unemp + age + (1|id) + (1|wave),       data = panel_risk_age_eng,   REML = TRUE,
  control = ctrl)

```

```{r englishness_categorical_micro_results_re, echo=FALSE, message=FALSE, warning=FALSE}

summary(m1_eng_cat_re)
summary(m2_eng_cat_re)
summary(m_wave_eng_cat_re)

summary(m_eng_eq03_cat_1_re); summary(m_eng_eq03_cat_2_re)
summary(m_eng_eq03_cat_3_re); summary(m_eng_eq03_cat_4_re)

summary(m_eng_eq05_cat_1_re); summary(m_eng_eq05_cat_2_re)
summary(m_eng_eq05_cat_3_re); summary(m_eng_eq05_cat_4_re)

summary(m_risk_eng_cat_1_re); summary(m_risk_eng_cat_2_re)
summary(m_risk_eng_cat_3_re); summary(m_risk_eng_cat_4_re)
```

```{r save_micro_models_re, echo=FALSE, message=FALSE, warning=FALSE}
# ============================================================
# Save RANDOM EFFECTS MICRO models with "_re" suffix
# ============================================================

micro_model_names_re <- c(

  # Base (Britishness continuous)
  "m1_re", "m2_re", "m_wave_re",

  # Income (raw)
  "m_inc_0.1_re", "m_inc_1_re", "m_inc_0.2_re", "m_inc_2_re", "m_inc_3_re", "m_inc_4_re",

  # Equivalised income (0.3)
  "m_eq03_0.1_re", "m_eq03_1_re", "m_eq03_0.2_re", "m_eq03_2_re", "m_eq03_3_re", "m_eq03_4_re",

  # Equivalised income (0.5)
  "m_eq05_0.1_re", "m_eq05_1_re", "m_eq05_0.2_re", "m_eq05_2_re", "m_eq05_3_re", "m_eq05_4_re",

  # Risk (Britishness)
  "m_risk_0.1_re", "m_risk_1_re", "m_risk_0.2_re", "m_risk_2_re", "m_risk_3_re", "m_risk_4_re",

  # Diagnostics
  "m_brit_risk_noage_re", "m_brit_risk_re",

  # Britishness categorical base
  "m1_cat_re", "m2_cat_re", "m_wave_cat_re",

  # Britishness categorical × income
  "m_inc_cat_1_re", "m_inc_cat_2_re", "m_inc_cat_3_re", "m_inc_cat_4_re",
  "m_eq03_cat_1_re", "m_eq03_cat_2_re", "m_eq03_cat_3_re", "m_eq03_cat_4_re",
  "m_eq05_cat_1_re", "m_eq05_cat_2_re", "m_eq05_cat_3_re", "m_eq05_cat_4_re",

  # Britishness categorical × risk
  "m_risk_cat_1_re", "m_risk_cat_2_re", "m_risk_cat_3_re", "m_risk_cat_4_re",

  # Englishness continuous base
  "m1_eng_re", "m2_eng_re", "m_wave_eng_re",

  # Englishness × eq income (0.3)
  "m_eng_eq03_0.1_re", "m_eng_eq03_1_re", "m_eng_eq03_0.2_re",
  "m_eng_eq03_2_re", "m_eng_eq03_3_re", "m_eng_eq03_4_re",

  # Englishness × eq income (0.5)
  "m_eng_eq05_0.1_re", "m_eng_eq05_1_re", "m_eng_eq05_0.2_re",
  "m_eng_eq05_2_re", "m_eng_eq05_3_re", "m_eng_eq05_4_re",

  # Englishness × risk
  "m_risk_eng_0.1_re", "m_risk_eng_1_re", "m_risk_eng_0.2_re",
  "m_risk_eng_2_re", "m_risk_eng_3_re", "m_risk_eng_4_re",

  # Diagnostics Englishness
  "m_engl_risk_noage_re", "m_engl_risk_re",

  # Englishness categorical base
  "m1_eng_cat_re", "m2_eng_cat_re", "m_wave_eng_cat_re",

  # Englishness categorical × eq income
  "m_eng_eq03_cat_1_re", "m_eng_eq03_cat_2_re", "m_eng_eq03_cat_3_re", "m_eng_eq03_cat_4_re",
  "m_eng_eq05_cat_1_re", "m_eng_eq05_cat_2_re", "m_eng_eq05_cat_3_re", "m_eng_eq05_cat_4_re",

  # Englishness categorical × risk
  "m_risk_eng_cat_1_re", "m_risk_eng_cat_2_re", "m_risk_eng_cat_3_re", "m_risk_eng_cat_4_re"
)

missing_models_re <- micro_model_names_re[!vapply(micro_model_names_re, exists, logical(1), inherits = TRUE)]
if(length(missing_models_re) > 0){
  stop(
    "These RE model objects were NOT found in the environment:\n- ",
    paste(missing_models_re, collapse = "\n- ")
  )
}

suffix_models <- function(obj_names, suffix = "_re"){
  objs <- mget(obj_names, inherits = TRUE)
  names(objs) <- paste0(obj_names, suffix)
  objs
}

models_re_all <- suffix_models(micro_model_names_re, "_re")

out_dir_re <- "~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/models_micro_re"
dir.create(out_dir_re, recursive = TRUE, showWarnings = FALSE)

saveRDS(models_re_all, file.path(out_dir_re, "models_micro_re_all.rds"))

# Thematic sub-lists
saveRDS(suffix_models(c("m1_re","m2_re","m_wave_re"), "_re"),
        file.path(out_dir_re, "models_re_base.rds"))

saveRDS(suffix_models(c("m_inc_0.1_re","m_inc_1_re","m_inc_0.2_re","m_inc_2_re","m_inc_3_re","m_inc_4_re"), "_re"),
        file.path(out_dir_re, "models_re_income_raw.rds"))

saveRDS(suffix_models(c("m_eq03_0.1_re","m_eq03_1_re","m_eq03_0.2_re","m_eq03_2_re","m_eq03_3_re","m_eq03_4_re"), "_re"),
        file.path(out_dir_re, "models_re_income_eq03.rds"))

saveRDS(suffix_models(c("m_eq05_0.1_re","m_eq05_1_re","m_eq05_0.2_re","m_eq05_2_re","m_eq05_3_re","m_eq05_4_re"), "_re"),
        file.path(out_dir_re, "models_re_income_eq05.rds"))

saveRDS(suffix_models(c("m_risk_0.1_re","m_risk_1_re","m_risk_0.2_re","m_risk_2_re","m_risk_3_re","m_risk_4_re"), "_re"),
        file.path(out_dir_re, "models_re_risk.rds"))

saveRDS(suffix_models(c("m_brit_risk_noage_re","m_brit_risk_re","m_engl_risk_noage_re","m_engl_risk_re"), "_re"),
        file.path(out_dir_re, "models_re_diagnostics.rds"))

saveRDS(suffix_models(c("m1_eng_re","m2_eng_re","m_wave_eng_re"), "_re"),
        file.path(out_dir_re, "models_re_english_base.rds"))

saveRDS(suffix_models(c("m_eng_eq03_0.1_re","m_eng_eq03_1_re","m_eng_eq03_0.2_re","m_eng_eq03_2_re","m_eng_eq03_3_re","m_eng_eq03_4_re"), "_re"),
        file.path(out_dir_re, "models_re_english_eq03.rds"))

saveRDS(suffix_models(c("m_eng_eq05_0.1_re","m_eng_eq05_1_re","m_eng_eq05_0.2_re","m_eng_eq05_2_re","m_eng_eq05_3_re","m_eng_eq05_4_re"), "_re"),
        file.path(out_dir_re, "models_re_english_eq05.rds"))

saveRDS(suffix_models(c("m_risk_eng_0.1_re","m_risk_eng_1_re","m_risk_eng_0.2_re","m_risk_eng_2_re","m_risk_eng_3_re","m_risk_eng_4_re"), "_re"),
        file.path(out_dir_re, "models_re_english_risk.rds"))

cat("Saved RE models to:", out_dir_re, "\n")
cat("Total models saved:", length(models_re_all), "\n")
```
