---
title: "BES_Macro_Random_Effects"
format: html
editor: visual
---

```{r 0, include=FALSE, echo=FALSE}

library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(lubridate)
library(fixest)
library(haven)
library(lme4)      # random effects
library(lmerTest)  # p-values for lmer

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE    <- "immigSelf"
BRIT_BASE  <- "britishness"
TIME_BASE  <- "starttime"
AGE_BASE   <- "age"

MACRO_GDP_BASE    <- "gdp_pc"
MACRO_UNEMP_BASE  <- "unempl_rate"
MACRO_CLAIM_BASE  <- "claimant_k"
MACRO_CPIH_BASE   <- "cpih_rate"

# -------------------------
# Helpers
# -------------------------
get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

zap_if_labelled <- function(x){
  if (inherits(x, "haven_labelled")) return(zap_labels(x))
  x
}

# ======================================================
# 1) Choose waves
# ======================================================
w_dv   <- waves_available(df, DV_BASE)
w_brit <- waves_available(df, BRIT_BASE)
w_time <- waves_available(df, TIME_BASE)

waves_core <- Reduce(intersect, list(w_dv, w_brit, w_time))
if(length(waves_core) < 3) stop("Too few overlapping waves across DV, britishness, and starttime.")

w_age     <- waves_available(df, AGE_BASE)
waves_age <- intersect(waves_core, w_age)

w_gdp   <- waves_available(df, MACRO_GDP_BASE)
w_unemp <- waves_available(df, MACRO_UNEMP_BASE)
w_claim <- waves_available(df, MACRO_CLAIM_BASE)
w_cpih  <- waves_available(df, MACRO_CPIH_BASE)

waves_macro <- Reduce(intersect, list(waves_core, w_gdp, w_unemp, w_claim, w_cpih))
if(length(waves_macro) < 3) stop("Too few overlapping waves across DV/brit/time and macro series.")

# =========================================
# 2) Build wide core dataset
# =========================================
core_cols <- c(
  paste0(DV_BASE,   "W", waves_macro),
  paste0(BRIT_BASE, "W", waves_macro),
  paste0(TIME_BASE, "W", waves_macro),
  paste0(AGE_BASE,  "W", intersect(waves_macro, w_age))
)

df_core <- df %>%
  mutate(across(any_of(core_cols), zap_if_labelled)) %>%
  select(id, any_of(core_cols))

# =========================================
# 3) Reshape core to long
# =========================================
df_long_core <- df_core %>%
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", BRIT_BASE, ")W\\d+$")),
    names_to = c("var", "wave"),
    names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) %>%
  mutate(wave = as.integer(wave)) %>%
  pivot_wider(names_from = var, values_from = value) %>%
  rename(dv = !!DV_BASE, brit = !!BRIT_BASE)

df_long_time <- df_core %>%
  pivot_longer(
    cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
    names_to = "wave",
    names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
    values_to = "time"
  ) %>%
  mutate(wave = as.integer(wave), time = as.character(time))

df_long <- df_long_core %>%
  left_join(df_long_time, by = c("id", "wave"))

if(length(intersect(waves_macro, w_age)) > 0){
  age_long <- df_core %>%
    pivot_longer(
      cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
      names_to = "wave",
      names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
      values_to = "age"
    ) %>%
    mutate(wave = as.integer(wave))
  df_long <- df_long %>% left_join(age_long, by = c("id", "wave"))
}

df_long <- df_long %>%
  mutate(
    time = suppressWarnings(lubridate::ymd_hms(time, quiet = TRUE)),
    year = lubridate::year(time)
  )

# ==========================================================
# 4) Attach macro variables
# ==========================================================
macro_long_from_base <- function(df, base, waves_keep){
  cols <- paste0(base, "W", waves_keep)
  df %>%
    select(id, any_of(cols)) %>%
    pivot_longer(
      cols = -id,
      names_to = "wave",
      names_pattern = paste0("^", base, "W(\\d+)$"),
      values_to = base
    ) %>%
    mutate(wave = as.integer(wave))
}

macro_gdp   <- macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro)
macro_unemp <- macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro)
macro_claim <- macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro)
macro_cpih  <- macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro)

df_long <- df_long %>%
  left_join(macro_gdp,   by = c("id", "wave")) %>%
  left_join(macro_unemp, by = c("id", "wave")) %>%
  left_join(macro_claim, by = c("id", "wave")) %>%
  left_join(macro_cpih,  by = c("id", "wave"))

# ======================================================
# NOTE on macro RE specification:
# Macro indicators are wave-constant (one value per wave,
# shared across all individuals). Including both (1|wave)
# and a wave-constant macro predictor would be collinear,
# so macro RE models use only (1|id) and include
# poly(wave, 3) as a fixed smooth trend to absorb
# wave-level confounding — mirroring the FE main_0 specs.
# The brit/engl + macro + (1|id) + (1|wave) specs are also
# provided for the interaction models, which differ from
# the main_0 structure.
# ======================================================

# ======================================
# 5) RANDOM EFFECTS MODEL RUNNER — BRITISHNESS
# ======================================

# GDP
models_gdp_re <- list(
  main_0     = lmer(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main       = lmer(dv ~ brit + gdp_pc + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  main_age_0 = lmer(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main_age   = lmer(dv ~ brit + gdp_pc + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int        = lmer(dv ~ brit * gdp_pc + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int_age    = lmer(dv ~ brit * gdp_pc + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE)
)

# Unemployment
models_unemp_re <- list(
  main_0     = lmer(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main       = lmer(dv ~ brit + unempl_rate + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  main_age_0 = lmer(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main_age   = lmer(dv ~ brit + unempl_rate + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int        = lmer(dv ~ brit * unempl_rate + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int_age    = lmer(dv ~ brit * unempl_rate + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE)
)

# Claimant count
models_claim_re <- list(
  main_0     = lmer(dv ~ claimant_k + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main       = lmer(dv ~ brit + claimant_k + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  main_age_0 = lmer(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main_age   = lmer(dv ~ brit + claimant_k + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int        = lmer(dv ~ brit * claimant_k + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int_age    = lmer(dv ~ brit * claimant_k + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE)
)

# CPIH
models_cpih_re <- list(
  main_0     = lmer(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main       = lmer(dv ~ brit + cpih_rate + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  main_age_0 = lmer(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE),
  main_age   = lmer(dv ~ brit + cpih_rate + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int        = lmer(dv ~ brit * cpih_rate + (1|id) + (1|wave),
                    data = df_long, REML = TRUE),
  int_age    = lmer(dv ~ brit * cpih_rate + age + (1|id) + (1|wave),
                    data = df_long, REML = TRUE)
)

# ======================================
# 6) Econ robustness checks — BRITISHNESS RE
# ======================================
brit_econ_rob_checks_re <- list(
  brit_gdp_re         = lmer(brit ~ gdp_pc      + poly(wave, 3, raw = TRUE) + (1|id),
                             data = df_long, REML = TRUE),
  brit_unempl_rate_re = lmer(brit ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
                             data = df_long, REML = TRUE),
  brit_claimant_k_re  = lmer(brit ~ claimant_k  + poly(wave, 3, raw = TRUE) + (1|id),
                             data = df_long, REML = TRUE),
  brit_cpih_rate_re   = lmer(brit ~ cpih_rate   + poly(wave, 3, raw = TRUE) + (1|id),
                             data = df_long, REML = TRUE)
)

```

```{r 1 sanity, warning=FALSE, message=FALSE, echo=FALSE}
coverage_macro <- df_long |>
  summarise(
    n_obs               = n(),
    pct_gdp_nonmiss     = mean(!is.na(gdp_pc)),
    pct_unemp_nonmiss   = mean(!is.na(unempl_rate)),
    pct_claim_nonmiss   = mean(!is.na(claimant_k)),
    pct_cpih_nonmiss    = mean(!is.na(cpih_rate)),
    pct_age_nonmiss     = mean(!is.na(age))
  )
print(coverage_macro)

macro_constancy <- df_long %>%
  group_by(wave) %>%
  summarise(
    n_obs        = n(),
    gdp_unique   = n_distinct(gdp_pc),
    unemp_unique = n_distinct(unempl_rate),
    claim_unique = n_distinct(claimant_k),
    cpih_unique  = n_distinct(cpih_rate)
  )
print(macro_constancy)
```

TEXT HERE - TBD

```{r macro_models_summaries_re, echo=FALSE, warning=FALSE, message=FALSE}

summary(models_gdp_re$main_0);   summary(models_gdp_re$main)
summary(models_gdp_re$main_age_0); summary(models_gdp_re$main_age)
summary(models_gdp_re$int);       summary(models_gdp_re$int_age)

summary(models_unemp_re$main_0);   summary(models_unemp_re$main)
summary(models_unemp_re$main_age_0); summary(models_unemp_re$main_age)
summary(models_unemp_re$int);       summary(models_unemp_re$int_age)

summary(models_claim_re$main_0);   summary(models_claim_re$main)
summary(models_claim_re$main_age_0); summary(models_claim_re$main_age)
summary(models_claim_re$int);       summary(models_claim_re$int_age)

summary(models_cpih_re$main_0);   summary(models_cpih_re$main)
summary(models_cpih_re$main_age_0); summary(models_cpih_re$main_age)
summary(models_cpih_re$int);       summary(models_cpih_re$int_age)

summary(brit_econ_rob_checks_re$brit_gdp_re)
summary(brit_econ_rob_checks_re$brit_unempl_rate_re)
summary(brit_econ_rob_checks_re$brit_claimant_k_re)
summary(brit_econ_rob_checks_re$brit_cpih_rate_re)
```

## Macro-level analysis — Random Effects {.tabset}

### Results

TEXT HERE - TBD

#### National unemployment rate

TEXT HERE - TBD

#### Claimant count

TEXT HERE - TBD

#### GDP per capita

TEXT HERE - TBD

#### CPIH (consumer price inflation)

TEXT HERE - TBD

::: callout-note
**Interpretive note.**\
All macroeconomic indicators operate through the same moderation mechanism: they do not shift immigration attitudes directly, but condition how national identification translates into attitudes. The interaction effects are stable, precisely estimated, and robust across specifications.
:::

### Robustness Checks

#### Britishness as Categorical

```{r rob_check_brit_cat_re, include=FALSE, echo=FALSE}
# ============================================================
# Macro RE robustness: Britishness categorical (ref = 7)
# ============================================================

df_long <- df_long %>%
  mutate(
    brit_num = as.numeric(brit),
    brit_cat = factor(brit_num, levels = 1:7) %>% relevel(ref = "7")
  )

run_macro_cat_re <- function(varname, data){

  list(
    main     = lmer(as.formula(paste0("dv ~ brit_cat + ", varname, " + (1|id) + (1|wave)")),
                    data = data, REML = TRUE),
    main_age = lmer(as.formula(paste0("dv ~ brit_cat + ", varname, " + age + (1|id) + (1|wave)")),
                    data = data, REML = TRUE),
    int      = lmer(as.formula(paste0("dv ~ brit_cat * ", varname, " + (1|id) + (1|wave)")),
                    data = data, REML = TRUE),
    int_age  = lmer(as.formula(paste0("dv ~ brit_cat * ", varname, " + age + (1|id) + (1|wave)")),
                    data = data, REML = TRUE)
  )
}

models_gdp_cat_re   <- run_macro_cat_re("gdp_pc",      df_long)
models_unemp_cat_re <- run_macro_cat_re("unempl_rate", df_long)
models_claim_cat_re <- run_macro_cat_re("claimant_k",  df_long)
models_cpih_cat_re  <- run_macro_cat_re("cpih_rate",   df_long)
```

```{r macro_categorical_summaries_re, echo=FALSE, warning=FALSE, message=FALSE}

summary(models_gdp_cat_re$main);   summary(models_gdp_cat_re$main_age)
summary(models_gdp_cat_re$int);    summary(models_gdp_cat_re$int_age)

summary(models_unemp_cat_re$main);  summary(models_unemp_cat_re$main_age)
summary(models_unemp_cat_re$int);   summary(models_unemp_cat_re$int_age)

summary(models_claim_cat_re$main);  summary(models_claim_cat_re$main_age)
summary(models_claim_cat_re$int);   summary(models_claim_cat_re$int_age)

summary(models_cpih_cat_re$main);   summary(models_cpih_cat_re$main_age)
summary(models_cpih_cat_re$int);    summary(models_cpih_cat_re$int_age)
```

TEXT HERE - TBD

```{r save_brit_models_re, echo=FALSE, include=FALSE}
# ============================================================
# SAVE BRITISHNESS MACRO RE MODELS — done here, before gc(),
# so models are persisted to disk before we remove them from memory.
# ============================================================

save_path_re <- "~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/models_re"
if (!dir.exists(save_path_re)) dir.create(save_path_re, recursive = TRUE)

# A) Britishness — Continuous
macro_brit_continuous_re <- list(
  gdp_main_noage_econ_macro_re   = models_gdp_re$main_0,
  gdp_main_noage_macro_re        = models_gdp_re$main,
  gdp_main_age_econ_macro_re     = models_gdp_re$main_age_0,
  gdp_main_age_macro_re          = models_gdp_re$main_age,
  gdp_int_noage_macro_re         = models_gdp_re$int,
  gdp_int_age_macro_re           = models_gdp_re$int_age,

  unemp_main_noage_econ_macro_re = models_unemp_re$main_0,
  unemp_main_noage_macro_re      = models_unemp_re$main,
  unemp_main_age_econ_macro_re   = models_unemp_re$main_age_0,
  unemp_main_age_macro_re        = models_unemp_re$main_age,
  unemp_int_noage_macro_re       = models_unemp_re$int,
  unemp_int_age_macro_re         = models_unemp_re$int_age,

  claimant_main_noage_econ_macro_re = models_claim_re$main_0,
  claimant_main_noage_macro_re      = models_claim_re$main,
  claimant_main_age_econ_macro_re   = models_claim_re$main_age_0,
  claimant_main_age_macro_re        = models_claim_re$main_age,
  claimant_int_noage_macro_re       = models_claim_re$int,
  claimant_int_age_macro_re         = models_claim_re$int_age,

  cpih_main_noage_econ_macro_re  = models_cpih_re$main_0,
  cpih_main_noage_macro_re       = models_cpih_re$main,
  cpih_main_age_econ_macro_re    = models_cpih_re$main_age_0,
  cpih_main_age_macro_re         = models_cpih_re$main_age,
  cpih_int_noage_macro_re        = models_cpih_re$int,
  cpih_int_age_macro_re          = models_cpih_re$int_age
)
saveRDS(macro_brit_continuous_re,
        file.path(save_path_re, "macro_brit_continuous_re.rds"))

# B) Britishness — Categorical
macro_brit_categorical_re <- list(
  gdp_main_noage_cat_macro_re    = models_gdp_cat_re$main,
  gdp_main_age_cat_macro_re      = models_gdp_cat_re$main_age,
  gdp_int_noage_cat_macro_re     = models_gdp_cat_re$int,
  gdp_int_age_cat_macro_re       = models_gdp_cat_re$int_age,

  unemp_main_noage_cat_macro_re  = models_unemp_cat_re$main,
  unemp_main_age_cat_macro_re    = models_unemp_cat_re$main_age,
  unemp_int_noage_cat_macro_re   = models_unemp_cat_re$int,
  unemp_int_age_cat_macro_re     = models_unemp_cat_re$int_age,

  claimant_main_noage_cat_macro_re = models_claim_cat_re$main,
  claimant_main_age_cat_macro_re   = models_claim_cat_re$main_age,
  claimant_int_noage_cat_macro_re  = models_claim_cat_re$int,
  claimant_int_age_cat_macro_re    = models_claim_cat_re$int_age,

  cpih_main_noage_cat_macro_re   = models_cpih_cat_re$main,
  cpih_main_age_cat_macro_re     = models_cpih_cat_re$main_age,
  cpih_int_noage_cat_macro_re    = models_cpih_cat_re$int,
  cpih_int_age_cat_macro_re      = models_cpih_cat_re$int_age
)
saveRDS(macro_brit_categorical_re,
        file.path(save_path_re, "macro_brit_categorical_re.rds"))

# Britishness identity robustness
macro_identity_brit_robustness_re <- list(
  brit_gdp_macro_re      = brit_econ_rob_checks_re$brit_gdp_re,
  brit_unempl_macro_re   = brit_econ_rob_checks_re$brit_unempl_rate_re,
  brit_claimant_macro_re = brit_econ_rob_checks_re$brit_claimant_k_re,
  brit_cpih_macro_re     = brit_econ_rob_checks_re$brit_cpih_rate_re
)
saveRDS(macro_identity_brit_robustness_re,
        file.path(save_path_re, "macro_identity_brit_robustness_re.rds"))

cat("Saved Britishness MACRO RE models to:", save_path_re, "\n")
```

```{r gc_before_englishness, include=FALSE, echo=FALSE}
# ============================================================
# Free memory before building the Englishness long panel.
# lmer objects are much heavier than feols objects; by this
# point the session holds ~24 Britishness models + several
# large intermediate data frames. We drop what is no longer
# needed and run gc() twice to actually release the memory.
# ============================================================

# Drop the large intermediate Britishness data frames
rm(df_core, df_long_core, df_long_time, age_long,
   macro_gdp, macro_unemp, macro_claim, macro_cpih)

# Drop all Britishness lmer model lists (already saved / printed)
rm(models_gdp_re, models_unemp_re, models_claim_re, models_cpih_re,
   models_gdp_cat_re, models_unemp_cat_re, models_claim_cat_re, models_cpih_cat_re,
   brit_econ_rob_checks_re)

# Drop the main Britishness long panel (large; no longer needed)
rm(df_long)

# Force garbage collection twice to return memory to the OS
invisible(gc(verbose = FALSE)); invisible(gc(verbose = FALSE))
```

#### Other forms of Nationalism: Englishness

```{r engl_panel_build, include=FALSE, echo=FALSE}
# ============================================================
# Build the Englishness long panel (data only, no models yet)
# ============================================================

DV_BASE    <- "immigSelf"
ENG_BASE   <- "englishness"
TIME_BASE  <- "starttime"
AGE_BASE   <- "age"

MACRO_GDP_BASE    <- "gdp_pc"
MACRO_UNEMP_BASE  <- "unempl_rate"
MACRO_CLAIM_BASE  <- "claimant_k"
MACRO_CPIH_BASE   <- "cpih_rate"

w_dv_eng   <- waves_available(df, DV_BASE)
w_eng      <- waves_available(df, ENG_BASE)
w_time_eng <- waves_available(df, TIME_BASE)

waves_core_eng <- Reduce(intersect, list(w_dv_eng, w_eng, w_time_eng))
if(length(waves_core_eng) < 3) stop("Too few overlapping waves.")

w_age_eng     <- waves_available(df, AGE_BASE)
waves_age_eng <- intersect(waves_core_eng, w_age_eng)

w_gdp_eng   <- waves_available(df, MACRO_GDP_BASE)
w_unemp_eng <- waves_available(df, MACRO_UNEMP_BASE)
w_claim_eng <- waves_available(df, MACRO_CLAIM_BASE)
w_cpih_eng  <- waves_available(df, MACRO_CPIH_BASE)

waves_macro_eng <- Reduce(intersect,
  list(waves_core_eng, w_gdp_eng, w_unemp_eng, w_claim_eng, w_cpih_eng))
if(length(waves_macro_eng) < 3) stop("Too few overlapping waves for macro+englishness.")

core_cols_eng <- c(
  paste0(DV_BASE,   "W", waves_macro_eng),
  paste0(ENG_BASE,  "W", waves_macro_eng),
  paste0(TIME_BASE, "W", waves_macro_eng),
  paste0(AGE_BASE,  "W", intersect(waves_macro_eng, w_age_eng))
)

df_core_eng <- df %>%
  mutate(across(any_of(core_cols_eng), zap_if_labelled)) %>%
  select(id, any_of(core_cols_eng))

df_long_core_eng <- df_core_eng %>%
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", ENG_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) %>%
  mutate(wave = as.integer(wave)) %>%
  pivot_wider(names_from = var, values_from = value) %>%
  rename(dv = !!DV_BASE, engl = !!ENG_BASE)

df_long_time_eng <- df_core_eng %>%
  pivot_longer(
    cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
    names_to = "wave", names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
    values_to = "time"
  ) %>%
  mutate(wave = as.integer(wave), time = as.character(time))

df_long_eng <- df_long_core_eng %>%
  left_join(df_long_time_eng, by = c("id", "wave"))

if(length(intersect(waves_macro_eng, w_age_eng)) > 0){
  age_long_eng <- df_core_eng %>%
    pivot_longer(
      cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
      names_to = "wave", names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
      values_to = "age"
    ) %>%
    mutate(wave = as.integer(wave))
  df_long_eng <- df_long_eng %>% left_join(age_long_eng, by = c("id", "wave"))
  rm(age_long_eng)
}

# Drop now-unneeded intermediates immediately
rm(df_core_eng, df_long_core_eng, df_long_time_eng)
invisible(gc(verbose = FALSE))

macro_long_from_base_eng <- function(df, base, waves_keep){
  cols <- paste0(base, "W", waves_keep)
  df %>%
    select(id, any_of(cols)) %>%
    pivot_longer(cols = -id, names_to = "wave",
                 names_pattern = paste0("^", base, "W(\\d+)$"),
                 values_to = base) %>%
    mutate(wave = as.integer(wave))
}

df_long_eng <- df_long_eng %>%
  mutate(
    time = suppressWarnings(lubridate::ymd_hms(as.character(time), quiet = TRUE)),
    year = lubridate::year(time),
    dv   = as.numeric(dv),
    engl = as.numeric(engl),
    age  = as.numeric(age),
    engl = dplyr::na_if(engl, 9999)
  ) %>%
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave)) %>%
  left_join(macro_long_from_base_eng(df, MACRO_GDP_BASE,   waves_macro_eng), by = c("id","wave")) %>%
  left_join(macro_long_from_base_eng(df, MACRO_UNEMP_BASE, waves_macro_eng), by = c("id","wave")) %>%
  left_join(macro_long_from_base_eng(df, MACRO_CLAIM_BASE, waves_macro_eng), by = c("id","wave")) %>%
  left_join(macro_long_from_base_eng(df, MACRO_CPIH_BASE,  waves_macro_eng), by = c("id","wave")) %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  )

stopifnot(all(c("dv","engl","wave","id") %in% names(df_long_eng)))
invisible(gc(verbose = FALSE))
```

```{r engl_gdp_re, include=FALSE, echo=FALSE}
# GDP — continuous + categorical + econ robustness
models_gdp_eng_re <- list(
  main_0     = lmer(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) + (1|id),        data = df_long_eng, REML = TRUE),
  main       = lmer(dv ~ engl + gdp_pc + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  main_age_0 = lmer(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) + (1|id),  data = df_long_eng, REML = TRUE),
  main_age   = lmer(dv ~ engl + gdp_pc + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE),
  int        = lmer(dv ~ engl * gdp_pc + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  int_age    = lmer(dv ~ engl * gdp_pc + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE)
)

models_gdp_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + gdp_pc + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  main_age = lmer(dv ~ engl_cat + gdp_pc + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE),
  int      = lmer(dv ~ engl_cat * gdp_pc + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  int_age  = lmer(dv ~ engl_cat * gdp_pc + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE)
)

engl_rob_gdp_re <- lmer(engl ~ gdp_pc + poly(wave, 3, raw = TRUE) + (1|id),
                         data = df_long_eng, REML = TRUE)

invisible(gc(verbose = FALSE))
```

```{r engl_unemp_re, include=FALSE, echo=FALSE}
# Unemployment — continuous + categorical + econ robustness
models_unemp_eng_re <- list(
  main_0     = lmer(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),        data = df_long_eng, REML = TRUE),
  main       = lmer(dv ~ engl + unempl_rate + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  main_age_0 = lmer(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) + (1|id),  data = df_long_eng, REML = TRUE),
  main_age   = lmer(dv ~ engl + unempl_rate + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE),
  int        = lmer(dv ~ engl * unempl_rate + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  int_age    = lmer(dv ~ engl * unempl_rate + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE)
)

models_unemp_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + unempl_rate + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  main_age = lmer(dv ~ engl_cat + unempl_rate + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE),
  int      = lmer(dv ~ engl_cat * unempl_rate + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  int_age  = lmer(dv ~ engl_cat * unempl_rate + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE)
)

engl_rob_unemp_re <- lmer(engl ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
                           data = df_long_eng, REML = TRUE)

invisible(gc(verbose = FALSE))
```

```{r engl_claim_re, include=FALSE, echo=FALSE}
# Claimant count — continuous + categorical + econ robustness
models_claim_eng_re <- list(
  main_0     = lmer(dv ~ claimant_k + poly(wave, 3, raw = TRUE) + (1|id),        data = df_long_eng, REML = TRUE),
  main       = lmer(dv ~ engl + claimant_k + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  main_age_0 = lmer(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) + (1|id),  data = df_long_eng, REML = TRUE),
  main_age   = lmer(dv ~ engl + claimant_k + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE),
  int        = lmer(dv ~ engl * claimant_k + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  int_age    = lmer(dv ~ engl * claimant_k + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE)
)

models_claim_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + claimant_k + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  main_age = lmer(dv ~ engl_cat + claimant_k + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE),
  int      = lmer(dv ~ engl_cat * claimant_k + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  int_age  = lmer(dv ~ engl_cat * claimant_k + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE)
)

engl_rob_claim_re <- lmer(engl ~ claimant_k + poly(wave, 3, raw = TRUE) + (1|id),
                           data = df_long_eng, REML = TRUE)

invisible(gc(verbose = FALSE))
```

```{r engl_cpih_re, include=FALSE, echo=FALSE}
# CPIH — continuous + categorical + econ robustness
models_cpih_eng_re <- list(
  main_0     = lmer(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) + (1|id),        data = df_long_eng, REML = TRUE),
  main       = lmer(dv ~ engl + cpih_rate + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  main_age_0 = lmer(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) + (1|id),  data = df_long_eng, REML = TRUE),
  main_age   = lmer(dv ~ engl + cpih_rate + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE),
  int        = lmer(dv ~ engl * cpih_rate + (1|id) + (1|wave),                  data = df_long_eng, REML = TRUE),
  int_age    = lmer(dv ~ engl * cpih_rate + age + (1|id) + (1|wave),            data = df_long_eng, REML = TRUE)
)

models_cpih_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + cpih_rate + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  main_age = lmer(dv ~ engl_cat + cpih_rate + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE),
  int      = lmer(dv ~ engl_cat * cpih_rate + (1|id) + (1|wave),          data = df_long_eng, REML = TRUE),
  int_age  = lmer(dv ~ engl_cat * cpih_rate + age + (1|id) + (1|wave),    data = df_long_eng, REML = TRUE)
)

engl_rob_cpih_re <- lmer(engl ~ cpih_rate + poly(wave, 3, raw = TRUE) + (1|id),
                          data = df_long_eng, REML = TRUE)

# Bundle econ robustness checks for consistency with save chunk
engl_econ_rob_checks_re <- list(
  engl_gdp_re         = engl_rob_gdp_re,
  engl_unempl_rate_re = engl_rob_unemp_re,
  engl_claimant_k_re  = engl_rob_claim_re,
  engl_cpih_rate_re   = engl_rob_cpih_re
)

invisible(gc(verbose = FALSE))
```

TEXT HERE - TBD

```{r macro_englishness_summaries_re, echo=FALSE, warning=FALSE, message=FALSE}

# Englishness continuous
summary(models_gdp_eng_re$main_0);    summary(models_gdp_eng_re$main)
summary(models_gdp_eng_re$main_age_0); summary(models_gdp_eng_re$main_age)
summary(models_gdp_eng_re$int);        summary(models_gdp_eng_re$int_age)

summary(models_unemp_eng_re$main_0);    summary(models_unemp_eng_re$main)
summary(models_unemp_eng_re$main_age_0); summary(models_unemp_eng_re$main_age)
summary(models_unemp_eng_re$int);        summary(models_unemp_eng_re$int_age)

summary(models_claim_eng_re$main_0);    summary(models_claim_eng_re$main)
summary(models_claim_eng_re$main_age_0); summary(models_claim_eng_re$main_age)
summary(models_claim_eng_re$int);        summary(models_claim_eng_re$int_age)

summary(models_cpih_eng_re$main_0);    summary(models_cpih_eng_re$main)
summary(models_cpih_eng_re$main_age_0); summary(models_cpih_eng_re$main_age)
summary(models_cpih_eng_re$int);        summary(models_cpih_eng_re$int_age)

# Englishness categorical
summary(models_gdp_eng_cat_re$main);   summary(models_gdp_eng_cat_re$main_age)
summary(models_gdp_eng_cat_re$int);    summary(models_gdp_eng_cat_re$int_age)

summary(models_unemp_eng_cat_re$main);  summary(models_unemp_eng_cat_re$main_age)
summary(models_unemp_eng_cat_re$int);   summary(models_unemp_eng_cat_re$int_age)

summary(models_claim_eng_cat_re$main);  summary(models_claim_eng_cat_re$main_age)
summary(models_claim_eng_cat_re$int);   summary(models_claim_eng_cat_re$int_age)

summary(models_cpih_eng_cat_re$main);   summary(models_cpih_eng_cat_re$main_age)
summary(models_cpih_eng_cat_re$int);    summary(models_cpih_eng_cat_re$int_age)

# Econ robustness
summary(engl_econ_rob_checks_re$engl_gdp_re)
summary(engl_econ_rob_checks_re$engl_unempl_rate_re)
summary(engl_econ_rob_checks_re$engl_claimant_k_re)
summary(engl_econ_rob_checks_re$engl_cpih_rate_re)
```

TEXT HERE - TBD

```{r save_engl_models_re, echo=FALSE, include=FALSE}
# ============================================================
# SAVE ENGLISHNESS + IDENTITY ROBUSTNESS MACRO RE MODELS
# Britishness models were already saved in save_brit_models_re
# (before memory cleanup). We save Englishness separately here.
# ============================================================

save_path_re <- "~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/models_re"
if (!dir.exists(save_path_re)) dir.create(save_path_re, recursive = TRUE)

# C) Englishness — Continuous
macro_engl_continuous_re <- list(
  gdp_main_noage_engl_econ_macro_re = models_gdp_eng_re$main_0,
  gdp_main_noage_engl_macro_re      = models_gdp_eng_re$main,
  gdp_main_age_engl_econ_macro_re   = models_gdp_eng_re$main_age_0,
  gdp_main_age_engl_macro_re        = models_gdp_eng_re$main_age,
  gdp_int_noage_engl_macro_re       = models_gdp_eng_re$int,
  gdp_int_age_engl_macro_re         = models_gdp_eng_re$int_age,

  unemp_main_noage_engl_econ_macro_re = models_unemp_eng_re$main_0,
  unemp_main_noage_engl_macro_re      = models_unemp_eng_re$main,
  unemp_main_age_engl_econ_macro_re   = models_unemp_eng_re$main_age_0,
  unemp_main_age_engl_macro_re        = models_unemp_eng_re$main_age,
  unemp_int_noage_engl_macro_re       = models_unemp_eng_re$int,
  unemp_int_age_engl_macro_re         = models_unemp_eng_re$int_age,

  claimant_main_noage_engl_econ_macro_re = models_claim_eng_re$main_0,
  claimant_main_noage_engl_macro_re      = models_claim_eng_re$main,
  claimant_main_age_engl_econ_macro_re   = models_claim_eng_re$main_age_0,
  claimant_main_age_engl_macro_re        = models_claim_eng_re$main_age,
  claimant_int_noage_engl_macro_re       = models_claim_eng_re$int,
  claimant_int_age_engl_macro_re         = models_claim_eng_re$int_age,

  cpih_main_noage_engl_econ_macro_re = models_cpih_eng_re$main_0,
  cpih_main_noage_engl_macro_re      = models_cpih_eng_re$main,
  cpih_main_age_engl_econ_macro_re   = models_cpih_eng_re$main_age_0,
  cpih_main_age_engl_macro_re        = models_cpih_eng_re$main_age,
  cpih_int_noage_engl_macro_re       = models_cpih_eng_re$int,
  cpih_int_age_engl_macro_re         = models_cpih_eng_re$int_age
)
saveRDS(macro_engl_continuous_re,
        file.path(save_path_re, "macro_engl_continuous_re.rds"))

# D) Englishness — Categorical
macro_engl_categorical_re <- list(
  gdp_main_noage_engl_cat_macro_re   = models_gdp_eng_cat_re$main,
  gdp_main_age_engl_cat_macro_re     = models_gdp_eng_cat_re$main_age,
  gdp_int_noage_engl_cat_macro_re    = models_gdp_eng_cat_re$int,
  gdp_int_age_engl_cat_macro_re      = models_gdp_eng_cat_re$int_age,

  unemp_main_noage_engl_cat_macro_re = models_unemp_eng_cat_re$main,
  unemp_main_age_engl_cat_macro_re   = models_unemp_eng_cat_re$main_age,
  unemp_int_noage_engl_cat_macro_re  = models_unemp_eng_cat_re$int,
  unemp_int_age_engl_cat_macro_re    = models_unemp_eng_cat_re$int_age,

  claimant_main_noage_engl_cat_macro_re = models_claim_eng_cat_re$main,
  claimant_main_age_engl_cat_macro_re   = models_claim_eng_cat_re$main_age,
  claimant_int_noage_engl_cat_macro_re  = models_claim_eng_cat_re$int,
  claimant_int_age_engl_cat_macro_re    = models_claim_eng_cat_re$int_age,

  cpih_main_noage_engl_cat_macro_re  = models_cpih_eng_cat_re$main,
  cpih_main_age_engl_cat_macro_re    = models_cpih_eng_cat_re$main_age,
  cpih_int_noage_engl_cat_macro_re   = models_cpih_eng_cat_re$int,
  cpih_int_age_engl_cat_macro_re     = models_cpih_eng_cat_re$int_age
)
saveRDS(macro_engl_categorical_re,
        file.path(save_path_re, "macro_engl_categorical_re.rds"))

# E) Economic identity robustness (Englishness only; Britishness saved earlier)
macro_identity_engl_robustness_re <- list(
  engl_gdp_macro_re      = engl_econ_rob_checks_re$engl_gdp_re,
  engl_unempl_macro_re   = engl_econ_rob_checks_re$engl_unempl_rate_re,
  engl_claimant_macro_re = engl_econ_rob_checks_re$engl_claimant_k_re,
  engl_cpih_macro_re     = engl_econ_rob_checks_re$engl_cpih_rate_re
)
saveRDS(macro_identity_engl_robustness_re,
        file.path(save_path_re, "macro_identity_engl_robustness_re.rds"))

cat("Saved Englishness MACRO RE models to:", save_path_re, "\n")
```
