---
title: "BES_Micro"
format: html
editor: visual
---

```{r 0, include=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(fixest)
library(haven)
library(purrr)

BES_subset_panel_full_v2 <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v2.rds")

df <- BES_subset_panel_full_v2

rm(BES_subset_panel_full_v2)
gc()

DV_BASE   <- "immigSelf"
BRIT_BASE <- "britishness"
TIME_BASE <- "starttime"
AGE_BASE  <- "age"   

get_wave_num2 <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available2 <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num2)))
}

make_long_with_age <- function(df,
                               dv_base   = "immigSelf",
                               brit_base = "britishness",
                               time_base = "starttime",
                               age_base  = "age"){

  w_dv   <- waves_available2(df, dv_base)
  w_brit <- waves_available2(df, brit_base)
  w_time <- waves_available2(df, time_base)
  w_age  <- waves_available2(df, age_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_age))
  if(length(waves) < 3) stop("Too few overlapping waves across DV, britishness, starttime, and age.")

  dv_cols   <- paste0(dv_base,   "W", waves)
  brit_cols <- paste0(brit_base, "W", waves)
  time_cols <- paste0(time_base, "W", waves)
  age_cols  <- paste0(age_base,  "W", waves)

  # Drop haven labels to avoid pivot_longer attribute conflicts
  df2 <- df |>
    mutate(
      across(all_of(dv_cols),   ~ as.numeric(zap_labels(.x))),
      across(all_of(brit_cols), ~ as.numeric(zap_labels(.x))),
      across(all_of(age_cols),  ~ as.numeric(zap_labels(.x)))
    )

  df2 |>
    select(id, all_of(dv_cols), all_of(brit_cols), all_of(time_cols), all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(starttime_parsed, suppressWarnings(ymd(starttime_chr, quiet = TRUE))),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv   = all_of(dv_base),
      brit = all_of(brit_base),
      age  = all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(age), !is.na(wave))
}

panel_self <- make_long_with_age(df, DV_BASE, BRIT_BASE, TIME_BASE, AGE_BASE)
```

```{r 1 sanity, warning=FALSE, message=FALSE, echo=FALSE}
# Quick sanity print
panel_self |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(id),
    min_wave = min(wave),
    max_wave = max(wave),
    min_year = min(year, na.rm = TRUE),
    max_year = max(year, na.rm = TRUE),
    age_min = min(age, na.rm = TRUE),
    age_max = max(age, na.rm = TRUE)
  )
```

H1:

```{r models, echo=FALSE, message=FALSE, warning=FALSE}

# Model 1

m1 <- feols(
  dv ~ brit | id + wave,
  data = panel_self,
  cluster = "id"
)

m1

# Model 2


  m2 <- feols(
    dv ~ brit + age | id + wave,
    data = panel_self,
    cluster = "id"
  )
m2

```

In baseline respondent fixed-effects models with wave fixed effects, increases in British national identity are associated with small but statistically precise shifts toward more restrictive immigration self-placement. The magnitude of the unconditional effect is modest, consistent with the expectation that national identity alone does not mechanically drive attitudinal change.

```{r flexible wave, echo=FALSE, warning=FALSE, message=FALSE}

m_wave <- feols(
  dv ~ i(wave, brit, ref = 7) | id,
  data = panel_self,
  cluster = "id"
)

summary(m_wave)

iplot(
  m_wave,
  xlab = "Wave",
  main = "Wave-specific effect of Britishness on immigration self-placement (ref = W7)"
)

```

Allowing the effect of British national identity to vary flexibly across waves reveals substantial temporal heterogeneity in the association between Britishness and immigration self-placement. As shown in Figure X and Table X, the within-individual effect of Britishness is negative in the early BES waves (W8–W10), indicating a modest association with more restrictive immigration preferences during the immediate post-referendum period. From approximately W14 through W23, however, the effect becomes strongly positive and statistically significant, peaking in W23, before attenuating and turning negative again in later waves (W26–W30). This non-monotonic pattern indicates that the influence of national identity on immigration attitudes is not temporally stable but instead varies sharply across political contexts. Importantly, these estimates are obtained from respondent fixed-effects models with age controls, ensuring that the observed variation reflects within-person changes rather than compositional differences across waves. Taken together, the results suggest that Britishness does not exert a constant influence on immigration self-placement; rather, its political relevance is episodic and context-dependent, consistent with the theoretical expectation that national identity becomes attitudinally consequential under specific macro-political and economic conditions rather than through a uniform time trend.

H2:

```{r income 0, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

INCOME_BASE <- "income"   # <-- THIS is the correct BES income measure

# ---------- helpers ----------
get_wave_num <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num)))
}

# ---------- build long panel with income ----------
make_long_with_income <- function(df,
                                  dv_base,
                                  brit_base,
                                  time_base,
                                  income_base,
                                  age_base = NULL){

  w_dv     <- waves_available(df, dv_base)
  w_brit   <- waves_available(df, brit_base)
  w_time   <- waves_available(df, time_base)
  w_income <- waves_available(df, income_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_income))

  if(!is.null(age_base)){
    w_age <- waves_available(df, age_base)
    waves <- intersect(waves, w_age)
  }

  if(length(waves) < 3){
    stop("Too few overlapping waves across DV, britishness, time, income (and age).")
  }

  dv_cols     <- paste0(dv_base,     "W", waves)
  brit_cols   <- paste0(brit_base,   "W", waves)
  time_cols   <- paste0(time_base,   "W", waves)
  income_cols <- paste0(income_base, "W", waves)
  age_cols    <- if(!is.null(age_base)) paste0(age_base, "W", waves) else NULL

  df2 <- df |>
    mutate(
      across(all_of(dv_cols),     ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(brit_cols),   ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(income_cols), ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(age_cols),    ~ as.numeric(haven::zap_labels(.x)))
    )

  df2 |>
    select(id,
           all_of(dv_cols),
           all_of(brit_cols),
           all_of(time_cols),
           all_of(income_cols),
           all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(
        starttime_parsed,
        suppressWarnings(ymd(starttime_chr, quiet = TRUE))
      ),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv     = all_of(dv_base),
      brit   = all_of(brit_base),
      income = all_of(income_base),
      age    = if(!is.null(age_base)) all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(income), !is.na(wave))
}

# ---------- Panel A: without age ----------
panel_income_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  INCOME_BASE,
  age_base = NULL
)

# ---------- Panel B: with age ----------
panel_income_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  INCOME_BASE,
  age_base = AGE_BASE
)

# ---------- Models ----------
# (1) Income  WITHOUT age
m_inc_1 <- feols(
  dv ~ brit + income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

# (2) Income  WITH age
m_inc_2 <- feols(
  dv ~ brit + income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)

# (3) Income moderation WITHOUT age
m_inc_3 <- feols(
  dv ~ brit * income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

# (4) Income moderation WITH age
m_inc_4 <- feols(
  dv ~ brit * income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)
```

```{r income 1, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_inc_1)
summary(m_inc_2)
summary(m_inc_3)
summary(m_inc_4)
```

Respondent fixed-effects models indicate that British national identity retains a statistically significant within-individual association with immigration self-placement in samples restricted to respondents with observed household income. In contrast, household income itself does not exert an independent within-person effect, nor does its inclusion attenuate the estimated effect of Britishness. Introducing an interaction between income and Britishness does not improve model fit and yields no evidence that income conditions the influence of national identity on immigration attitudes. Together, these results suggest that the political relevance of Britishness is not driven by individual self-assigned income levels per se, motivating a shift from resource-based measures toward indicators of economic insecurity and exposure to risk in subsequent analyses. To address differences in household composition and comparability of income across respondents, I re-estimate the micro-level income models using an equivalised measure of gross household income constructed following the OECD-modified equivalence scale and ONS guidelines (for a description of the creation of such variables, see Annex XXX).

```{r income_equivalised, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ============================================================
#Equivalised household income (ONS OECD-modified scale)
# ============================================================
# This chunk:
# 1) Loads the derived equivalised income file (id-wave)
# 2) Joins it to a long panel (built with the same DV/brit/time structure)
# 3) Estimates the same FE specifications using equivalised income
#

# --- Load equivalised income (constructed externally; keyed by id + wave) ---
eq_long <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/equivalised_income_long.rds")

# --- Build long panels using the same infrastructure as the income models ---
# use make_long_with_income() but feed any income_base that exists across waves.
# Here, the *original* income base only to create the canonical long structure,
# then merge equivalised income by (id, wave).
panel_eq_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = INCOME_BASE,   # uses your existing income base to ensure overlap
  age_base = NULL
) %>%
  left_join(eq_long, by = c("id", "wave"))

panel_eq_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = INCOME_BASE,
  age_base = AGE_BASE
) %>%
  left_join(eq_long, by = c("id", "wave"))

# --- Sanity check: merge worked and missingness is as expected ---
panel_eq_age %>%
  summarise(
    n_obs = n(),
    n_ids = n_distinct(id),
    share_eq03_missing = mean(is.na(income_eq_child03)),
    share_eq05_missing = mean(is.na(income_eq_child05))
  )

# ============================================================
# Models with equivalised income
# ============================================================

# --- Prepare analysis samples (explicit, avoids silent failures) ---
panel_eq03_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child03))
panel_eq03_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child03))

panel_eq05_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child05))
panel_eq05_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child05))

# --- Sanity checks: fail fast with a clear message if merge/coverage is an issue ---
if(nrow(panel_eq03_noage) == 0 || nrow(panel_eq03_age) == 0){
  stop("No non-missing income_eq_child03 observations after merge. Check (id,wave) join and missingness in eq_long.")
}

if(nrow(panel_eq05_noage) == 0 || nrow(panel_eq05_age) == 0){
  stop("No non-missing income_eq_child05 observations after merge. Check (id,wave) join and missingness in eq_long.")
}

# --- Bound A: child weight = 0.3 (lower bound) ---
m_eq03_1 <- feols(
  dv ~ brit + income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_2 <- feols(
  dv ~ brit + income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

m_eq03_3 <- feols(
  dv ~ brit * income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_4 <- feols(
  dv ~ brit * income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

# --- Bound B: child weight = 0.5 (upper bound) ---
m_eq05_1 <- feols(
  dv ~ brit + income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_2 <- feols(
  dv ~ brit + income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

m_eq05_3 <- feols(
  dv ~ brit * income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_4 <- feols(
  dv ~ brit * income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

```

```{r income_equivalised_results 1, echo=FALSE, warning=FALSE, message=FALSE}
# Bound A: child weight = 0.3 (lower bound)
summary(m_eq03_1)
summary(m_eq03_2)
summary(m_eq03_3)
summary(m_eq03_4)

```

Using the conservative lower-bound assumption that all dependent children receive a weight of 0.3, respondent fixed-effects models with wave fixed effects yield results that closely mirror those obtained with raw household income. Across all specifications, British national identity retains a statistically precise within-individual association with immigration self-placement, while equivalised household income itself exhibits no independent within-person effect. Including age controls does not alter these estimates, and introducing an interaction between Britishness and equivalised income provides no evidence that income conditions the attitudinal relevance of national identity. Model fit values remain virtually unchanged relative to the baseline income specifications. Taken together, these findings indicate that the null effect of income is not an artefact of household size or composition and reinforce the conclusion that individual material resources, whether measured in raw or equivalised terms, do not meaningfully activate national identity in shaping immigration attitudes.

```{r income_equivalised_results 2, echo=FALSE, warning=FALSE, message=FALSE}
# Bound B: child weight = 0.5 (upper bound)
summary(m_eq05_1)
summary(m_eq05_2)
summary(m_eq05_3)
summary(m_eq05_4)

```

As a further robustness check, I re-estimate the micro-level income models using an alternative equivalised income measure that assigns a higher weight to dependent children (0.5), corresponding to the upper bound of the OECD-modified equivalence scale. Results from respondent fixed-effects models with wave fixed effects are substantively indistinguishable from those obtained under the lower-bound specification. British national identity continues to exhibit a statistically precise within-individual association with immigration self-placement, while equivalised household income shows no independent effect and does not attenuate the estimated impact of Britishness. Adding age controls leaves the results unchanged, and interaction models provide no evidence that equivalised income conditions the relationship between national identity and immigration attitudes. Model fit remain virtually identical across specifications. Taken together, these findings demonstrate that the null effect of income is robust to alternative assumptions regarding the relative consumption needs of children and confirm that individual economic resources—whether measured using conservative or generous equivalence scales—do not meaningfully activate national identity in shaping immigration preferences.

```{r risk 0, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

RISK_BASE <- "riskUnemployment"

# ---------- build long panels ----------
panel_risk_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = RISK_BASE,   # reuse function; rename later
  age_base = NULL
)

panel_risk_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = RISK_BASE,
  age_base = AGE_BASE
)

# Rename for clarity
panel_risk_noage <- panel_risk_noage |>
  dplyr::rename(risk_unemp = income)

panel_risk_age <- panel_risk_age |>
  dplyr::rename(risk_unemp = income)

# ---------- Models ----------
# (1) Main effects, no age
m_risk_1 <- feols(
  dv ~ brit + risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (2) Main effects, with age
m_risk_2 <- feols(
  dv ~ brit + risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

# (3) Moderation, no age
m_risk_3 <- feols(
  dv ~ brit * risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (4) Moderation, with age
m_risk_4 <- feols(
  dv ~ brit * risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)
```

```{r risk 1, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_risk_1)
summary(m_risk_2)
summary(m_risk_3)
summary(m_risk_4)

```

Respondent fixed-effects models show no robust evidence that perceived unemployment risk conditions the relationship between British national identity and immigration self-placement. While the interaction between Britishness and perceived unemployment risk is small and statistically insignificant across specifications, the main effect of unemployment risk becomes weakly positive at the 10% level once the interaction term is included. This marginal association is conditional on the interaction specification, not present in non-interacted models, and substantively negligible in size. Importantly, the baseline association between Britishness and immigration self-placement remains stable and precisely estimated throughout. Taken together, these results suggest that individual-level economic insecurity does not meaningfully activate national identity in shaping immigration attitudes, motivating a shift toward contextual economic conditions in subsequent analyses.

*Note for myself: Why risk unemployment became positive after adding the interaction term? Because once an interaction is introduced, the main effect of unemployment risk is redefined as the effect at Britishness equal to zero; this changes the estimand and reallocates shared variance, which can produce small, conditional effects without altering the substantive conclusion. Once we include an interaction, the model no longer estimates an average effect of unemployment risk. Instead, it estimates the effect at a specific level of national identity, by default, when Britishness equals zero (take the derivative in relation to unemplrisk). Since that value is not substantively meaningful, we focus on the interaction and predicted effects rather than the main coefficient.*
