---
title: "BES_Micro_Cultural"
format: html
editor: visual
---

```{r 0, include=FALSE, echo=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(fixest)
library(haven)
library(purrr)

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE   <- "immigCultural"
BRIT_BASE <- "britishness"
TIME_BASE <- "starttime"
AGE_BASE  <- "age"   

get_wave_num2 <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available2 <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num2)))
}

make_long_with_age <- function(df,
                               dv_base   = "immigCultural",
                               brit_base = "britishness",
                               time_base = "starttime",
                               age_base  = "age"){

  w_dv   <- waves_available2(df, dv_base)
  w_brit <- waves_available2(df, brit_base)
  w_time <- waves_available2(df, time_base)
  w_age  <- waves_available2(df, age_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_age))
  if(length(waves) < 3) stop("Too few overlapping waves across DV, britishness, starttime, and age.")

  dv_cols   <- paste0(dv_base,   "W", waves)
  brit_cols <- paste0(brit_base, "W", waves)
  time_cols <- paste0(time_base, "W", waves)
  age_cols  <- paste0(age_base,  "W", waves)

  # Drop haven labels to avoid pivot_longer attribute conflicts
  df2 <- df |>
    mutate(
      across(all_of(dv_cols),   ~ as.numeric(zap_labels(.x))),
      across(all_of(brit_cols), ~ as.numeric(zap_labels(.x))),
      across(all_of(age_cols),  ~ as.numeric(zap_labels(.x)))
    )

  df2 |>
    select(id, all_of(dv_cols), all_of(brit_cols), all_of(time_cols), all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(starttime_parsed, suppressWarnings(ymd(starttime_chr, quiet = TRUE))),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv   = all_of(dv_base),
      brit = all_of(brit_base),
      age  = all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(age), !is.na(wave))
}

panel_self <- make_long_with_age(df, DV_BASE, BRIT_BASE, TIME_BASE, AGE_BASE)
```

```{r 1 sanity, warning=FALSE, message=FALSE, echo=FALSE}
# Quick sanity print
panel_self |>
  summarise(
    n_obs = n(),
    n_ids = n_distinct(id),
    min_wave = min(wave),
    max_wave = max(wave),
    min_year = min(year, na.rm = TRUE),
    max_year = max(year, na.rm = TRUE),
    age_min = min(age, na.rm = TRUE),
    age_max = max(age, na.rm = TRUE)
  )
```

## Micro level results

### Base Models

```{r models, echo=FALSE, message=FALSE, warning=FALSE}

# Model 1

m1 <- feols(
  dv ~ brit | id + wave,
  data = panel_self,
  cluster = "id"
)

m1

# Model 2


  m2 <- feols(
    dv ~ brit + age | id + wave,
    data = panel_self,
    cluster = "id"
  )
m2

```

```{r flexible wave, echo=FALSE, warning=FALSE, message=FALSE}

m_wave <- feols(
  dv ~ i(wave, brit) | id,
  data = panel_self,
  cluster = "id"
)

summary(m_wave)

iplot(
  m_wave,
  xlab = "Wave",
  main = "Wave-specific effect of Britishness on immigration self-placement"
)

```

### Economic Context Moderation: Individual Income

```{r income 0, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

INCOME_BASE <- "income"   # <-- THIS is the correct BES income measure

# ---------- helpers ----------
get_wave_num <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base){
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave_num)))
}

# ---------- build long panel with income ----------
make_long_with_income <- function(df,
                                  dv_base,
                                  brit_base,
                                  time_base,
                                  income_base,
                                  age_base = NULL){

  w_dv     <- waves_available(df, dv_base)
  w_brit   <- waves_available(df, brit_base)
  w_time   <- waves_available(df, time_base)
  w_income <- waves_available(df, income_base)

  waves <- Reduce(intersect, list(w_dv, w_brit, w_time, w_income))

  if(!is.null(age_base)){
    w_age <- waves_available(df, age_base)
    waves <- intersect(waves, w_age)
  }

  if(length(waves) < 3){
    stop("Too few overlapping waves across DV, britishness, time, income (and age).")
  }

  dv_cols     <- paste0(dv_base,     "W", waves)
  brit_cols   <- paste0(brit_base,   "W", waves)
  time_cols   <- paste0(time_base,   "W", waves)
  income_cols <- paste0(income_base, "W", waves)
  age_cols    <- if(!is.null(age_base)) paste0(age_base, "W", waves) else NULL

  df2 <- df |>
    mutate(
      across(all_of(dv_cols),     ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(brit_cols),   ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(income_cols), ~ as.numeric(haven::zap_labels(.x))),
      across(all_of(age_cols),    ~ as.numeric(haven::zap_labels(.x)))
    )

  df2 |>
    select(id,
           all_of(dv_cols),
           all_of(brit_cols),
           all_of(time_cols),
           all_of(income_cols),
           all_of(age_cols)) |>
    pivot_longer(
      cols = -id,
      names_to = c(".value", "wave"),
      names_pattern = "(.+)W(\\d+)$"
    ) |>
    mutate(
      wave = as.integer(wave),
      starttime_chr = as.character(.data[[time_base]]),
      starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
      starttime_parsed = coalesce(
        starttime_parsed,
        suppressWarnings(ymd(starttime_chr, quiet = TRUE))
      ),
      year = year(starttime_parsed)
    ) |>
    rename(
      dv     = all_of(dv_base),
      brit   = all_of(brit_base),
      income = all_of(income_base),
      age    = if(!is.null(age_base)) all_of(age_base)
    ) |>
    filter(!is.na(dv), !is.na(brit), !is.na(income), !is.na(wave))
}

# ---------- Panel A: without age ----------
panel_income_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  INCOME_BASE,
  age_base = NULL
)

# ---------- Panel B: with age ----------
panel_income_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  INCOME_BASE,
  age_base = AGE_BASE
)

# ---------- Models ----------
# (0.1) Income  SOLE, WITHOUT age
m_inc_0.1 <- feols(
  dv ~ income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

# (1) Income  WITHOUT age
m_inc_1 <- feols(
  dv ~ brit + income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

# (0.2) Income  WITH age
m_inc_0.2 <- feols(
  dv ~ income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)

# (2) Income  SOLE, WITH age
m_inc_2 <- feols(
  dv ~ brit + income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)

# (3) Income moderation WITHOUT age
m_inc_3 <- feols(
  dv ~ brit * income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

# (4) Income moderation WITH age
m_inc_4 <- feols(
  dv ~ brit * income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)
```

```{r income 1, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_inc_0.1)
summary(m_inc_1)
summary(m_inc_2)
summary(m_inc_0.2)
summary(m_inc_3)
summary(m_inc_4)
```

```{r income_equivalised, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# ============================================================
#Equivalised household income (ONS OECD-modified scale)
# ============================================================
# This chunk:
# 1) Loads the derived equivalised income file (id-wave)
# 2) Joins it to a long panel (built with the same DV/brit/time structure)
# 3) Estimates the same FE specifications using equivalised income
#

# --- Load equivalised income (constructed externally; keyed by id + wave) ---
eq_long <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/equivalised_income_long.rds")

eq_long <- eq_long %>%
  mutate(
    id   = as.character(id),
    wave = as.integer(wave)
  )


# --- Build long panels using the same infrastructure as the income models ---
# use make_long_with_income() but feed any income_base that exists across waves.
# Here, the *original* income base only to create the canonical long structure,
# then merge equivalised income by (id, wave).
panel_eq_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = INCOME_BASE,   # uses your existing income base to ensure overlap
  age_base = NULL
) %>%
  left_join(eq_long, by = c("id", "wave"))

panel_eq_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = INCOME_BASE,
  age_base = AGE_BASE
) %>%
  left_join(eq_long, by = c("id", "wave"))

# --- Sanity check: merge worked and missingness is as expected ---
panel_eq_age %>%
  summarise(
    n_obs = n(),
    n_ids = n_distinct(id),
    share_eq03_missing = mean(is.na(income_eq_child03)),
    share_eq05_missing = mean(is.na(income_eq_child05))
  )

# ============================================================
# Models with equivalised income
# ============================================================

# --- Prepare analysis samples (explicit, avoids silent failures) ---
panel_eq03_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child03))
panel_eq03_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child03))

panel_eq05_noage <- panel_eq_noage %>% filter(!is.na(income_eq_child05))
panel_eq05_age   <- panel_eq_age   %>% filter(!is.na(income_eq_child05))

# --- Sanity checks: fail fast with a clear message if merge/coverage is an issue ---
if(nrow(panel_eq03_noage) == 0 || nrow(panel_eq03_age) == 0){
  stop("No non-missing income_eq_child03 observations after merge. Check (id,wave) join and missingness in eq_long.")
}

if(nrow(panel_eq05_noage) == 0 || nrow(panel_eq05_age) == 0){
  stop("No non-missing income_eq_child05 observations after merge. Check (id,wave) join and missingness in eq_long.")
}

# --- Bound A: child weight = 0.3 (lower bound) ---
m_eq03_0.1 <- feols(
  dv ~ income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_1 <- feols(
  dv ~ brit + income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_0.2 <- feols(
  dv ~ income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

m_eq03_2 <- feols(
  dv ~ brit + income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

m_eq03_3 <- feols(
  dv ~ brit * income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_4 <- feols(
  dv ~ brit * income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

# --- Bound B: child weight = 0.5 (upper bound) ---
m_eq05_0.1 <- feols(
  dv ~ income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_1 <- feols(
  dv ~ brit + income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_0.2 <- feols(
  dv ~ income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

m_eq05_2 <- feols(
  dv ~ brit + income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

m_eq05_3 <- feols(
  dv ~ brit * income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_4 <- feols(
  dv ~ brit * income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

```

```{r income_equivalised_results 1, echo=FALSE, warning=FALSE, message=FALSE}
# Bound A: child weight = 0.3 (lower bound)
summary(m_eq03_0.1)
summary(m_eq03_1)
summary(m_eq03_0.2)
summary(m_eq03_2)
summary(m_eq03_3)
summary(m_eq03_4)

```

```{r income_equivalised_results 2, echo=FALSE, warning=FALSE, message=FALSE}
# Bound B: child weight = 0.5 (upper bound)
summary(m_eq05_0.1)
summary(m_eq05_1)
summary(m_eq05_0.2)
summary(m_eq05_2)
summary(m_eq05_3)
summary(m_eq05_4)

```

### Economic Context Moderation: Individual risk (fear of unemployment)

```{r risk 0, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

RISK_BASE <- "riskUnemployment"

# ---------- build long panel ----------
panel_risk_noage <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = RISK_BASE,
  age_base = NULL
)

# rename first (income -> risk_unemp), then clean
panel_risk_noage <- panel_risk_noage %>%
  rename(risk_unemp = income) %>%
  mutate(risk_unemp = if_else(between(risk_unemp, 0, 10), risk_unemp, NA_real_)) %>%
  filter(!is.na(risk_unemp))

panel_risk_age <- make_long_with_income(
  df,
  DV_BASE,
  BRIT_BASE,
  TIME_BASE,
  income_base = RISK_BASE,
  age_base = AGE_BASE
) %>%
  rename(risk_unemp = income) %>%
  mutate(risk_unemp = if_else(between(risk_unemp, 0, 10), risk_unemp, NA_real_)) %>%
  filter(!is.na(risk_unemp))


# ---------- Models ----------
# (0.1) Risk sole, no age
m_risk_0.1 <- feols(
  dv ~ risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (1) Main effects, no age
m_risk_1 <- feols(
  dv ~ brit + risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (0.2) risk sole, with age
m_risk_0.2 <- feols(
  dv ~ risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

# (2) Main effects, with age
m_risk_2 <- feols(
  dv ~ brit + risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

# (3) Moderation, no age
m_risk_3 <- feols(
  dv ~ brit * risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (4) Moderation, with age
m_risk_4 <- feols(
  dv ~ brit * risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)
```

summary(m_risk_1) summary(m_risk_2) summary(m_risk_3) summary(m_risk_4)

```{r risk 1, echo=FALSE, warning=FALSE, message=FALSE}

summary(m_risk_0.1)
summary(m_risk_1)
summary(m_risk_0.2)
summary(m_risk_2)
summary(m_risk_3)
summary(m_risk_4)

```

```{r risk 2, echo=FALSE, warning=FALSE, message=FALSE}

# ==========================================================
# Diagnostic: Does unemployment risk predict Britishness?
# ==========================================================

# (5) Britishness ~ risk (no age)
m_brit_risk_noage <- feols(
  brit ~ risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

# (6) Britishness ~ risk + age
m_brit_risk <- feols(
  brit ~ risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

summary(m_brit_risk_noage)
summary(m_brit_risk)

```

## Robustness Checks

### Brittishness as Categorical

```{r 0.1, include=FALSE, echo=FALSE}

panel_self <- panel_self |>
  mutate(
    brit_cat = factor(brit, levels = 1:7),
    brit_cat = relevel(brit_cat, ref = "7")
  )

panel_income_noage <- panel_income_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_income_age <- panel_income_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_risk_noage <- panel_risk_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_risk_age <- panel_risk_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq_noage <- panel_eq_noage |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

panel_eq_age <- panel_eq_age |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))

```

#### Base Models

```{r brit cat 1, echo=FALSE, warning=FALSE, message=FALSE}

# Model 1 (categorical Britishness; 7 = base)
m1_cat <- feols(
  dv ~ i(brit, ref = 7) | id + wave,
  data = panel_self,
  cluster = "id"
)

# Model 2 (+ age)
m2_cat <- feols(
  dv ~ i(brit, ref = 7) + age | id + wave,
  data = panel_self,
  cluster = "id"
)

m_wave_cat <- feols(
  dv ~ i(wave, brit, ref = 7) | id,
  data = panel_self,
  cluster = "id"
)


m1_cat
m2_cat
m_wave_cat

iplot(
  m_wave_cat,
  xlab = "Wave",
  main = "Wave-specific difference relative to Britishness = 7"
)

```

#### Economic Context Moderation: Individual Income

```{r brit cat 2, echo=FALSE, warning=FALSE, message=FALSE}
# Income main effects (categorical Britishness)
m_inc_cat_1 <- feols(
  dv ~ i(brit, ref = 7) + income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

m_inc_cat_2 <- feols(
  dv ~ i(brit, ref = 7) + income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)

# Income moderation (categorical Britishness × income)
m_inc_cat_3 <- feols(
  dv ~ i(brit, ref = 7) * income | id + wave,
  data = panel_income_noage,
  cluster = "id"
)

m_inc_cat_4 <- feols(
  dv ~ i(brit, ref = 7) * income + age | id + wave,
  data = panel_income_age,
  cluster = "id"
)

# --- Bound A: child weight = 0.3 (lower bound) ---
m_eq03_cat_1 <- feols(
  dv ~ i(brit, ref = 7) + income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_cat_2 <- feols(
  dv ~ i(brit, ref = 7) + income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

m_eq03_cat_3 <- feols(
  dv ~ i(brit, ref = 7) * income_eq_child03 | id + wave,
  data = panel_eq03_noage,
  cluster = "id"
)

m_eq03_cat_4 <- feols(
  dv ~ i(brit, ref = 7) * income_eq_child03 + age | id + wave,
  data = panel_eq03_age,
  cluster = "id"
)

# --- Bound B: child weight = 0.5 (upper bound) ---
m_eq05_cat_1 <- feols(
  dv ~ i(brit, ref = 7) + income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_cat_2 <- feols(
  dv ~ i(brit, ref = 7) + income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

m_eq05_cat_3 <- feols(
  dv ~ i(brit, ref = 7) * income_eq_child05 | id + wave,
  data = panel_eq05_noage,
  cluster = "id"
)

m_eq05_cat_4 <- feols(
  dv ~ i(brit, ref = 7) * income_eq_child05 + age | id + wave,
  data = panel_eq05_age,
  cluster = "id"
)

summary(m_inc_cat_1)
summary(m_inc_cat_2)
summary(m_inc_cat_3)
summary(m_inc_cat_4)
summary(m_eq03_cat_1) 
summary(m_eq03_cat_2) 
summary(m_eq03_cat_3) 
summary(m_eq03_cat_4)
summary(m_eq05_cat_1) 
summary(m_eq05_cat_2) 
summary(m_eq05_cat_3) 
summary(m_eq05_cat_4)


```

#### Economic Context Moderation: Individual risk (fear of unemployment)

```{r brit cat 3, echo=FALSE, warning=FALSE, message=FALSE}

# Risk main effects (categorical Britishness)
m_risk_cat_1 <- feols(
  dv ~ i(brit, ref = 7) + risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

m_risk_cat_2 <- feols(
  dv ~ i(brit, ref = 7) + risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

# Risk moderation (categorical Britishness × risk)
m_risk_cat_3 <- feols(
  dv ~ i(brit, ref = 7) * risk_unemp | id + wave,
  data = panel_risk_noage,
  cluster = "id"
)

m_risk_cat_4 <- feols(
  dv ~ i(brit, ref = 7) * risk_unemp + age | id + wave,
  data = panel_risk_age,
  cluster = "id"
)

summary(m_risk_cat_1)
summary(m_risk_cat_2)
summary(m_risk_cat_3)
summary(m_risk_cat_4)
```

### Other measures of nationalism

```{r eng_brit_plot, echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(tidyr)
library(ggplot2)
library(haven)
library(stringr)

ids_wave <- df %>%
  select(
    id,
    matches("^britishnessW\\d+$"),
    matches("^englishnessW\\d+$")
  ) %>%
  mutate(across(-id, ~ as.numeric(zap_labels(.)))) %>%
  pivot_longer(
    cols = -id,
    names_to = c("identity", "wave"),
    names_pattern = "(britishness|englishness)W(\\d+)",
    values_to = "value"
  ) %>%
  mutate(
    wave = as.integer(wave),
    identity = recode(identity,
                      britishness = "Britishness",
                      englishness = "Englishness"),
    value = if_else(value %in% 1:7, value, NA_real_)
  ) %>%
  group_by(identity, wave) %>%
  summarise(mean_value = mean(value, na.rm = TRUE), .groups = "drop")

ggplot(ids_wave, aes(wave, mean_value, color = identity)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(
    x = "BES Wave",
    y = "Mean identity strength (1–7)",
    color = "Identity",
    title = "Evolution of Britishness and Englishness across BES waves"
  )

ids_wave_dm <- ids_wave %>%
  group_by(identity) %>%
  mutate(mean_dm = mean_value - mean(mean_value, na.rm = TRUE))

ggplot(ids_wave_dm, aes(wave, mean_dm, color = identity)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey60") +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(
    x = "BES Wave",
    y = "Deviation from identity mean",
    color = "Identity",
    title = "Within-wave change: Britishness vs Englishness"
  )


```

```{r englishness_base_models, echo=FALSE, message=FALSE, warning=FALSE}

# -------------------------------------------------------------------
# Englishness (continuous) — Base micro models
# -------------------------------------------------------------------

ENG_BASE <- "englishness"

panel_self_eng <- make_long_with_age(
  df,
  dv_base   = DV_BASE,
  brit_base = ENG_BASE,   
  time_base = TIME_BASE,
  age_base  = AGE_BASE
) %>%
  rename(engl = brit) %>%
  mutate(engl = if_else(engl %in% 1:7, engl, NA_real_))

# Model 1: Englishness only
m1_eng <- feols(
  dv ~ engl | id + wave,
  data = panel_self_eng,
  cluster = "id"
)

# Model 2: + age
m2_eng <- feols(
  dv ~ engl + age | id + wave,
  data = panel_self_eng,
  cluster = "id"
)

# Flexible wave-specific effect (ref = W7)
m_wave_eng <- feols(
  dv ~ i(wave, engl, ref = 7) | id,
  data = panel_self_eng,
  cluster = "id"
)

```

```{r englishness_base_models_results, message=FALSE, warning=FALSE}

m1_eng
m2_eng
summary(m_wave_eng)
```

```{r englishness_income_models, echo=FALSE, message=FALSE, warning=FALSE}

# ------------------------------------------------------------
# Englishness × Equivalised income (OECD: child weight = 0.3 and 0.5)
# Correctly cleans Englishness (drops 9999 etc.)
# ------------------------------------------------------------

ENG_BASE <- "englishness"

# Build Englishness long panels, rename identity, CLEAN invalid codes, join eq income
panel_eng_eq_noage <- make_long_with_income(
  df,
  dv_base     = DV_BASE,
  brit_base   = ENG_BASE,
  time_base   = TIME_BASE,
  income_base = INCOME_BASE,
  age_base    = NULL
) %>%
  dplyr::rename(engl = brit) %>%
  dplyr::mutate(engl = dplyr::if_else(engl %in% 1:7, engl, NA_real_)) %>%
  dplyr::left_join(eq_long, by = c("id", "wave"))

panel_eng_eq_age <- make_long_with_income(
  df,
  dv_base     = DV_BASE,
  brit_base   = ENG_BASE,
  time_base   = TIME_BASE,
  income_base = INCOME_BASE,
  age_base    = AGE_BASE
) %>%
  dplyr::rename(engl = brit) %>%
  dplyr::mutate(engl = dplyr::if_else(engl %in% 1:7, engl, NA_real_)) %>%
  dplyr::left_join(eq_long, by = c("id", "wave"))

# Fail fast: must be 1–7 only (or NA)
stopifnot(all(is.na(panel_eng_eq_noage$engl) | panel_eng_eq_noage$engl %in% 1:7))
stopifnot(all(is.na(panel_eng_eq_age$engl)   | panel_eng_eq_age$engl   %in% 1:7))

# Create analysis samples for both equivalence-weight variants
panel_eng_eq03_noage <- panel_eng_eq_noage %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child03))
panel_eng_eq03_age   <- panel_eng_eq_age   %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child03))

panel_eng_eq05_noage <- panel_eng_eq_noage %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child05))
panel_eng_eq05_age   <- panel_eng_eq_age   %>% dplyr::filter(!is.na(engl), !is.na(income_eq_child05))

if(nrow(panel_eng_eq03_noage) == 0 || nrow(panel_eng_eq03_age) == 0){
  stop("No non-missing Englishness + income_eq_child03 observations after merge/cleaning.")
}
if(nrow(panel_eng_eq05_noage) == 0 || nrow(panel_eng_eq05_age) == 0){
  stop("No non-missing Englishness + income_eq_child05 observations after merge/cleaning.")
}

# -----------------------------
# Models: child weight = 0.3
# -----------------------------
m_eng_eq03_0.1 <- feols(
  dv ~ income_eq_child03 | id + wave,
  data = panel_eng_eq03_noage,
  cluster = "id"
)

m_eng_eq03_1 <- feols(
  dv ~ engl + income_eq_child03 | id + wave,
  data = panel_eng_eq03_noage,
  cluster = "id"
)

m_eng_eq03_0.2 <- feols(
  dv ~ income_eq_child03 + age | id + wave,
  data = panel_eng_eq03_age,
  cluster = "id"
)

m_eng_eq03_2 <- feols(
  dv ~ engl + income_eq_child03 + age | id + wave,
  data = panel_eng_eq03_age,
  cluster = "id"
)

m_eng_eq03_3 <- feols(
  dv ~ engl * income_eq_child03 | id + wave,
  data = panel_eng_eq03_noage,
  cluster = "id"
)

m_eng_eq03_4 <- feols(
  dv ~ engl * income_eq_child03 + age | id + wave,
  data = panel_eng_eq03_age,
  cluster = "id"
)

# -----------------------------
# Models: child weight = 0.5
# -----------------------------
m_eng_eq05_0.1 <- feols(
  dv ~ income_eq_child05 | id + wave,
  data = panel_eng_eq05_noage,
  cluster = "id"
)

m_eng_eq05_1 <- feols(
  dv ~ engl + income_eq_child05 | id + wave,
  data = panel_eng_eq05_noage,
  cluster = "id"
)

m_eng_eq05_0.2 <- feols(
  dv ~ income_eq_child05 + age | id + wave,
  data = panel_eng_eq05_age,
  cluster = "id"
)

m_eng_eq05_2 <- feols(
  dv ~ engl + income_eq_child05 + age | id + wave,
  data = panel_eng_eq05_age,
  cluster = "id"
)

m_eng_eq05_3 <- feols(
  dv ~ engl * income_eq_child05 | id + wave,
  data = panel_eng_eq05_noage,
  cluster = "id"
)

m_eng_eq05_4 <- feols(
  dv ~ engl * income_eq_child05 + age | id + wave,
  data = panel_eng_eq05_age,
  cluster = "id"
)

# Output
summary(m_eng_eq03_0.1); summary(m_eng_eq03_1); summary(m_eng_eq03_0.2); summary(m_eng_eq03_2); summary(m_eng_eq03_3); summary(m_eng_eq03_4) 
summary(m_eng_eq05_0.1); summary(m_eng_eq05_1); summary(m_eng_eq05_0.2); summary(m_eng_eq05_2); summary(m_eng_eq05_3); summary(m_eng_eq05_4)


```

```{r englishness_risk_models, echo=FALSE, message=FALSE, warning=FALSE}

# ============================================================
# Perceived unemployment risk — Englishness robustness
# (CLEAN version: Englishness + risk properly recoded)
# ============================================================

ENG_BASE  <- "englishness"
RISK_BASE <- "riskUnemployment"

# --- Build long panels (no age / with age) ---
panel_risk_noage_eng <- make_long_with_income(
  df,
  dv_base     = DV_BASE,
  brit_base   = ENG_BASE,
  time_base   = TIME_BASE,
  income_base = RISK_BASE,
  age_base    = NULL
) %>% 
  rename(
    engl       = brit,
    risk_unemp = income
  ) %>%
  mutate(
    engl       = if_else(engl %in% 1:7, engl, NA_real_),
    risk_unemp = if_else(risk_unemp >= 0 & risk_unemp <= 10, risk_unemp, NA_real_)
  )

panel_risk_age_eng <- make_long_with_income(
  df,
  dv_base     = DV_BASE,
  brit_base   = ENG_BASE,
  time_base   = TIME_BASE,
  income_base = RISK_BASE,
  age_base    = AGE_BASE
) %>% 
  rename(
    engl       = brit,
    risk_unemp = income
  ) %>%
  mutate(
    engl       = if_else(engl %in% 1:7, engl, NA_real_),
    risk_unemp = if_else(risk_unemp >= 0 & risk_unemp <= 10, risk_unemp, NA_real_)
  )

# --- Fail fast sanity checks ---
stopifnot(all(is.na(panel_risk_noage_eng$engl) | panel_risk_noage_eng$engl %in% 1:7))
stopifnot(all(is.na(panel_risk_age_eng$engl)   | panel_risk_age_eng$engl   %in% 1:7))

# --- Models: main effects ---
m_risk_eng_0.1 <- feols(
  dv ~ risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

m_risk_eng_1 <- feols(
  dv ~ engl + risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

m_risk_eng_0.2 <- feols(
  dv ~ risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

m_risk_eng_2 <- feols(
  dv ~ engl + risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

# --- Models: moderation (interaction) ---
m_risk_eng_3 <- feols(
  dv ~ engl * risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

m_risk_eng_4 <- feols(
  dv ~ engl * risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

# --- Output ---
summary(m_risk_eng_0.1)
summary(m_risk_eng_1)
summary(m_risk_eng_0.2)
summary(m_risk_eng_2)
summary(m_risk_eng_3)
summary(m_risk_eng_4)

```

```{r englishness_risk_models_1, echo=FALSE, message=FALSE, warning=FALSE}
# ==========================================================
# Diagnostic: Does unemployment risk predict Britishness?
# ==========================================================

# (5) Britishness ~ risk (no age)
m_engl_risk_noage_engl <- feols(
  engl ~ risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

# (6) Britishness ~ risk + age
m_engl_risk_engl <- feols(
  engl ~ risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

summary(m_engl_risk_noage_engl)
summary(m_engl_risk_engl)

```

```{r englishness_categorical_micro, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# ============================================================
# MICRO robustness: Englishness as categorical (ref = 7)
# ============================================================

# 0) Ensure Englishness is valid (1–7) and create factor with ref = 7
panel_self_eng <- panel_self_eng %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_num = if_else(engl_num %in% 1:7, engl_num, NA_real_),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

# (Optional but recommended) Add engl_cat to the income/risk panels too
# so the interacted specifications run on the exact same samples.
panel_eng_eq03_noage <- panel_eng_eq03_noage %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_eng_eq03_age <- panel_eng_eq03_age %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_eng_eq05_noage <- panel_eng_eq05_noage %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_eng_eq05_age <- panel_eng_eq05_age %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_risk_noage_eng <- panel_risk_noage_eng %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

panel_risk_age_eng <- panel_risk_age_eng %>%
  mutate(
    engl_num = as.numeric(engl),
    engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7")
  ) %>%
  filter(!is.na(engl_num))

# ============================================================
# A) Base models (categorical Englishness; 7 = reference)
# ============================================================

m1_eng_cat <- feols(
  dv ~ i(engl_num, ref = 7) | id + wave,
  data = panel_self_eng,
  cluster = "id"
)

m2_eng_cat <- feols(
  dv ~ i(engl_num, ref = 7) + age | id + wave,
  data = panel_self_eng,
  cluster = "id"
)

# Flexible wave-specific categorical differences (relative to engl = 7)
m_wave_eng_cat <- feols(
  dv ~ i(wave, engl_num, ref = 7) | id,
  data = panel_self_eng,
  cluster = "id"
)

# ============================================================
# B) Equivalised income robustness (categorical Englishness)
#     - child weight = 0.3 (eq03)
#     - child weight = 0.5 (eq05)
# ============================================================

# --- eq03 main effects ---
m_eng_eq03_cat_1 <- feols(
  dv ~ i(engl_num, ref = 7) + income_eq_child03 | id + wave,
  data = panel_eng_eq03_noage,
  cluster = "id"
)

m_eng_eq03_cat_2 <- feols(
  dv ~ i(engl_num, ref = 7) + income_eq_child03 + age | id + wave,
  data = panel_eng_eq03_age,
  cluster = "id"
)

# --- eq03 moderation ---
m_eng_eq03_cat_3 <- feols(
  dv ~ i(engl_num, ref = 7) * income_eq_child03 | id + wave,
  data = panel_eng_eq03_noage,
  cluster = "id"
)

m_eng_eq03_cat_4 <- feols(
  dv ~ i(engl_num, ref = 7) * income_eq_child03 + age | id + wave,
  data = panel_eng_eq03_age,
  cluster = "id"
)

# --- eq05 main effects ---
m_eng_eq05_cat_1 <- feols(
  dv ~ i(engl_num, ref = 7) + income_eq_child05 | id + wave,
  data = panel_eng_eq05_noage,
  cluster = "id"
)

m_eng_eq05_cat_2 <- feols(
  dv ~ i(engl_num, ref = 7) + income_eq_child05 + age | id + wave,
  data = panel_eng_eq05_age,
  cluster = "id"
)

# --- eq05 moderation ---
m_eng_eq05_cat_3 <- feols(
  dv ~ i(engl_num, ref = 7) * income_eq_child05 | id + wave,
  data = panel_eng_eq05_noage,
  cluster = "id"
)

m_eng_eq05_cat_4 <- feols(
  dv ~ i(engl_num, ref = 7) * income_eq_child05 + age | id + wave,
  data = panel_eng_eq05_age,
  cluster = "id"
)

# ============================================================
# C) Unemployment-risk robustness (categorical Englishness)
# ============================================================

# Risk main effects
m_risk_eng_cat_1 <- feols(
  dv ~ i(engl_num, ref = 7) + risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

m_risk_eng_cat_2 <- feols(
  dv ~ i(engl_num, ref = 7) + risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

# Risk moderation
m_risk_eng_cat_3 <- feols(
  dv ~ i(engl_num, ref = 7) * risk_unemp | id + wave,
  data = panel_risk_noage_eng,
  cluster = "id"
)

m_risk_eng_cat_4 <- feols(
  dv ~ i(engl_num, ref = 7) * risk_unemp + age | id + wave,
  data = panel_risk_age_eng,
  cluster = "id"
)

# ============================================================
# (Optional) Quick checks in render log
# ============================================================
# m1_eng_cat
# m2_eng_cat
# summary(m_wave_eng_cat)

```

```{r englishness_categorical_micro_results, echo=FALSE, message=FALSE, warning=FALSE}
# ============================================================
# DISPLAY: Englishness categorical MICRO results (mirror brit)
# Assumes the models were estimated in the previous chunk.
# ============================================================

# Base models
m1_eng_cat
m2_eng_cat
m_wave_eng_cat

# Optional: plot wave-specific categorical differences (relative to engl = 7)
iplot(
  m_wave_eng_cat,
  xlab = "Wave",
  main = "Wave-specific difference relative to Englishness = 7"
)

# Equivalised income (child weight = 0.3)
summary(m_eng_eq03_cat_1)
summary(m_eng_eq03_cat_2)
summary(m_eng_eq03_cat_3)
summary(m_eng_eq03_cat_4)

# Equivalised income (child weight = 0.5)
summary(m_eng_eq05_cat_1)
summary(m_eng_eq05_cat_2)
summary(m_eng_eq05_cat_3)
summary(m_eng_eq05_cat_4)

# Unemployment risk
summary(m_risk_eng_cat_1)
summary(m_risk_eng_cat_2)
summary(m_risk_eng_cat_3)
summary(m_risk_eng_cat_4)

```

```{r save_micro_models, echo=FALSE, message=FALSE, warning=FALSE}
# ============================================================
# Save MICRO models with "_micro" suffix (to avoid name clashes
# with meso/macro objects)
# UPDATED: adds Englishness categorical models
# ============================================================

# 1) Define the micro model object names
micro_model_names <- c(

  # --- Base models (Britishness continuous) ---
  "m1", "m2", "m_wave",

  # --- Income (raw income) ---
  "m_inc_0.1", "m_inc_1", "m_inc_0.2", "m_inc_2", "m_inc_3", "m_inc_4",

  # --- Equivalised income (child weight = 0.3) ---
  "m_eq03_0.1", "m_eq03_1", "m_eq03_0.2", "m_eq03_2", "m_eq03_3", "m_eq03_4",

  # --- Equivalised income (child weight = 0.5) ---
  "m_eq05_0.1", "m_eq05_1", "m_eq05_0.2", "m_eq05_2", "m_eq05_3", "m_eq05_4",

  # --- Risk of unemployment (Britishness) ---
  "m_risk_0.1", "m_risk_1", "m_risk_0.2", "m_risk_2", "m_risk_3", "m_risk_4",

  # --- Diagnostic: Britishness ~ risk ---
  "m_brit_risk_noage", "m_brit_risk",

  # --- Robustness: Britishness categorical ---
  "m1_cat", "m2_cat", "m_wave_cat",

  # --- Robustness: categorical Britishness × income (raw + eq income) ---
  "m_inc_cat_1", "m_inc_cat_2", "m_inc_cat_3", "m_inc_cat_4",
  "m_eq03_cat_1", "m_eq03_cat_2", "m_eq03_cat_3", "m_eq03_cat_4",
  "m_eq05_cat_1", "m_eq05_cat_2", "m_eq05_cat_3", "m_eq05_cat_4",

  # --- Robustness: categorical Britishness × risk ---
  "m_risk_cat_1", "m_risk_cat_2", "m_risk_cat_3", "m_risk_cat_4",

  # --- Englishness (continuous) base + flexible wave ---
  "m1_eng", "m2_eng", "m_wave_eng",

  # --- Englishness × equivalised income (0.3) ---
  "m_eng_eq03_0.1", "m_eng_eq03_1", "m_eng_eq03_0.2",
  "m_eng_eq03_2", "m_eng_eq03_3", "m_eng_eq03_4",

  # --- Englishness × equivalised income (0.5) ---
  "m_eng_eq05_0.1", "m_eng_eq05_1", "m_eng_eq05_0.2",
  "m_eng_eq05_2", "m_eng_eq05_3", "m_eng_eq05_4",

  # --- Englishness × risk ---
  "m_risk_eng_0.1", "m_risk_eng_1", "m_risk_eng_0.2",
  "m_risk_eng_2", "m_risk_eng_3", "m_risk_eng_4",

  # --- Diagnostic: Englishness ~ risk ---
  "m_engl_risk_noage_engl", "m_engl_risk_engl",

  # ==========================================================
  # NEW: Englishness categorical (base + interactions)
  # ==========================================================
  "m1_eng_cat", "m2_eng_cat", "m_wave_eng_cat",

  "m_eng_eq03_cat_1", "m_eng_eq03_cat_2", "m_eng_eq03_cat_3", "m_eng_eq03_cat_4",
  "m_eng_eq05_cat_1", "m_eng_eq05_cat_2", "m_eng_eq05_cat_3", "m_eng_eq05_cat_4",

  "m_risk_eng_cat_1", "m_risk_eng_cat_2", "m_risk_eng_cat_3", "m_risk_eng_cat_4"
)

# 2) Fail-fast: ensure every model exists in the environment
missing_models <- micro_model_names[!vapply(micro_model_names, exists, logical(1), inherits = TRUE)]
if(length(missing_models) > 0){
  stop(
    "These MICRO model objects were NOT found in the environment:\n- ",
    paste(missing_models, collapse = "\n- "),
    "\n\nMake sure the chunks that estimate them were run before saving."
  )
}

# 3) Helper: pull objects + suffix names
suffix_models <- function(obj_names, suffix = "_micro"){
  objs <- mget(obj_names, inherits = TRUE)
  names(objs) <- paste0(obj_names, suffix)
  objs
}

# 4) Build "ALL micro models" list (every model gets _micro)
models_micro_all <- suffix_models(micro_model_names, "_micro_Cultural")

# 5) Optional: thematic sub-lists (also suffixed)
models_micro_base <- suffix_models(c("m1","m2","m_wave"), "_micro")

models_micro_income_raw <- suffix_models(
  c("m_inc_0.1","m_inc_1","m_inc_0.2","m_inc_2","m_inc_3","m_inc_4"),
  "_micro_Cultural"
)

models_micro_income_eq03 <- suffix_models(
  c("m_eq03_0.1","m_eq03_1","m_eq03_0.2","m_eq03_2","m_eq03_3","m_eq03_4"),
  "_micro_Cultural"
)

models_micro_income_eq05 <- suffix_models(
  c("m_eq05_0.1","m_eq05_1","m_eq05_0.2","m_eq05_2","m_eq05_3","m_eq05_4"),
  "_micro_Cultural"
)

models_micro_risk <- suffix_models(
  c("m_risk_0.1","m_risk_1","m_risk_0.2","m_risk_2","m_risk_3","m_risk_4"),
  "_micro_Cultural"
)

models_micro_diag <- suffix_models(
  c("m_brit_risk_noage","m_brit_risk","m_engl_risk_noage_engl","m_engl_risk_engl"),
  "_micro_Cultural"
)

models_micro_cat_base <- suffix_models(c("m1_cat","m2_cat","m_wave_cat"), "_micro_Cultural")

models_micro_cat_income <- suffix_models(
  c("m_inc_cat_1","m_inc_cat_2","m_inc_cat_3","m_inc_cat_4",
    "m_eq03_cat_1","m_eq03_cat_2","m_eq03_cat_3","m_eq03_cat_4",
    "m_eq05_cat_1","m_eq05_cat_2","m_eq05_cat_3","m_eq05_cat_4"),
  "_micro_Cultural"
)

models_micro_cat_risk <- suffix_models(
  c("m_risk_cat_1","m_risk_cat_2","m_risk_cat_3","m_risk_cat_4"),
  "_micro_Cultural"
)

models_micro_english_base <- suffix_models(c("m1_eng","m2_eng","m_wave_eng"), "_micro_Cultural")

models_micro_english_eq03 <- suffix_models(
  c("m_eng_eq03_0.1","m_eng_eq03_1","m_eng_eq03_0.2","m_eng_eq03_2","m_eng_eq03_3","m_eng_eq03_4"),
  "_micro_Cultural"
)

models_micro_english_eq05 <- suffix_models(
  c("m_eng_eq05_0.1","m_eng_eq05_1","m_eng_eq05_0.2","m_eng_eq05_2","m_eng_eq05_3","m_eng_eq05_4"),
  "_micro_Cultural"
)

models_micro_english_risk <- suffix_models(
  c("m_risk_eng_0.1","m_risk_eng_1","m_risk_eng_0.2","m_risk_eng_2","m_risk_eng_3","m_risk_eng_4"),
  "_micro_Cultural"
)

# NEW: Englishness categorical thematic lists
models_micro_english_cat_base <- suffix_models(
  c("m1_eng_cat","m2_eng_cat","m_wave_eng_cat"),
  "_micro_Cultural"
)

models_micro_english_cat_eq03 <- suffix_models(
  c("m_eng_eq03_cat_1","m_eng_eq03_cat_2","m_eng_eq03_cat_3","m_eng_eq03_cat_4"),
  "_micro_Cultural"
)

models_micro_english_cat_eq05 <- suffix_models(
  c("m_eng_eq05_cat_1","m_eng_eq05_cat_2","m_eng_eq05_cat_3","m_eng_eq05_cat_4"),
  "_micro_Cultural"
)

models_micro_english_cat_risk <- suffix_models(
  c("m_risk_eng_cat_1","m_risk_eng_cat_2","m_risk_eng_cat_3","m_risk_eng_cat_4"),
  "_micro_Cultural"
)

# 6) Save
out_dir <- "~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/models_micro_Cultural"
dir.create(out_dir, recursive = TRUE, showWarnings = FALSE)

saveRDS(models_micro_all,                file.path(out_dir, "models_micro_all.rds"))
saveRDS(models_micro_base,               file.path(out_dir, "models_micro_base.rds"))
saveRDS(models_micro_income_raw,         file.path(out_dir, "models_micro_income_raw.rds"))
saveRDS(models_micro_income_eq03,        file.path(out_dir, "models_micro_income_eq03.rds"))
saveRDS(models_micro_income_eq05,        file.path(out_dir, "models_micro_income_eq05.rds"))
saveRDS(models_micro_risk,               file.path(out_dir, "models_micro_risk.rds"))
saveRDS(models_micro_diag,               file.path(out_dir, "models_micro_diagnostics.rds"))
saveRDS(models_micro_cat_base,           file.path(out_dir, "models_micro_cat_base.rds"))
saveRDS(models_micro_cat_income,         file.path(out_dir, "models_micro_cat_income.rds"))
saveRDS(models_micro_cat_risk,           file.path(out_dir, "models_micro_cat_risk.rds"))
saveRDS(models_micro_english_base,       file.path(out_dir, "models_micro_english_base.rds"))
saveRDS(models_micro_english_eq03,       file.path(out_dir, "models_micro_english_eq03.rds"))
saveRDS(models_micro_english_eq05,       file.path(out_dir, "models_micro_english_eq05.rds"))
saveRDS(models_micro_english_risk,       file.path(out_dir, "models_micro_english_risk.rds"))

# NEW: save Englishness categorical bundles
saveRDS(models_micro_english_cat_base,   file.path(out_dir, "models_micro_english_cat_base.rds"))
saveRDS(models_micro_english_cat_eq03,   file.path(out_dir, "models_micro_english_cat_eq03.rds"))
saveRDS(models_micro_english_cat_eq05,   file.path(out_dir, "models_micro_english_cat_eq05.rds"))
saveRDS(models_micro_english_cat_risk,   file.path(out_dir, "models_micro_english_cat_risk.rds"))

cat("Saved MICRO models to:", out_dir, "\n")
cat("Total models saved:", length(models_micro_all), "\n")
```
