---
title: "Online Appendix C: Macro-Level Models"
subtitle: "National Economic Context, National Identity, and Immigration Attitudes"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-location: left
    theme: cosmo
    embed-resources: true
    echo: false
    warning: false
    message: false
    fig-width: 8
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(lubridate)
library(fixest)
library(haven)
library(modelsummary)
library(kableExtra)

options(modelsummary_factory_default = "kableExtra")

GOF_MAP <- tribble(
  ~raw,                  ~clean,          ~fmt,
  "nobs",                "Observations",  0,
  "FE: id",              "Individual FE", 0,
  "FE: wave",            "Wave FE",       0,
  "adj.r.squared",       "Adj. R²",       3,
  "within.r.squared",    "Within R²",     6,
  "rmse",                "RMSE",          3
)

zap_if_labelled <- function(x) {
  if (inherits(x, "haven_labelled")) return(zap_labels(x))
  x
}

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE          <- "immigSelf"
BRIT_BASE        <- "britishness"
ENG_BASE         <- "englishness"
TIME_BASE        <- "starttime"
AGE_BASE         <- "age"
MACRO_GDP_BASE   <- "gdp_pc"
MACRO_UNEMP_BASE <- "unempl_rate"
MACRO_CLAIM_BASE <- "claimant_k"
MACRO_CPIH_BASE  <- "cpih_rate"

get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base) {
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

macro_long_from_base <- function(df, base, waves_keep) {
  cols <- paste0(base, "W", waves_keep)
  df |>
    select(id, any_of(cols)) |>
    pivot_longer(cols = -id, names_to = "wave",
                 names_pattern = paste0("^", base, "W(\\d+)$"),
                 values_to = base) |>
    mutate(wave = as.integer(wave))
}
```

```{r build-panel-brit, include=FALSE}
w_dv   <- waves_available(df, DV_BASE)
w_brit <- waves_available(df, BRIT_BASE)
w_time <- waves_available(df, TIME_BASE)
w_age  <- waves_available(df, AGE_BASE)
w_gdp  <- waves_available(df, MACRO_GDP_BASE)
w_unemp<- waves_available(df, MACRO_UNEMP_BASE)
w_claim<- waves_available(df, MACRO_CLAIM_BASE)
w_cpih <- waves_available(df, MACRO_CPIH_BASE)

waves_core  <- Reduce(intersect, list(w_dv, w_brit, w_time))
waves_macro <- Reduce(intersect, list(waves_core, w_gdp, w_unemp, w_claim, w_cpih))
waves_age   <- intersect(waves_macro, w_age)

core_cols <- c(
  paste0(DV_BASE,   "W", waves_macro),
  paste0(BRIT_BASE, "W", waves_macro),
  paste0(TIME_BASE, "W", waves_macro),
  paste0(AGE_BASE,  "W", waves_age)
)

df_core <- df |>
  mutate(across(any_of(core_cols), zap_if_labelled)) |>
  select(id, any_of(core_cols))

# DV + Britishness
df_long_core <- df_core |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", BRIT_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), brit = all_of(BRIT_BASE))

# starttime
df_long_time <- df_core |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long <- left_join(df_long_core, df_long_time, by = c("id", "wave"))

# age
if (length(waves_age) > 0) {
  age_long <- df_core |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long <- left_join(df_long, age_long, by = c("id", "wave"))
}

df_long <- df_long |>
  mutate(time = suppressWarnings(ymd_hms(time, quiet = TRUE)),
         year = year(time),
         brit = as.numeric(brit),
         dv   = as.numeric(dv),
         age  = as.numeric(age))

# macro indicators
df_long <- df_long |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro), by = c("id", "wave"))

# categorical Britishness
df_long <- df_long |>
  mutate(brit_num = as.numeric(brit),
         brit_cat = relevel(factor(brit_num, levels = 1:7), ref = "7"))
```

```{r build-panel-engl, include=FALSE}
w_eng <- waves_available(df, ENG_BASE)
waves_core_eng  <- Reduce(intersect, list(w_dv, w_eng, w_time))
waves_macro_eng <- Reduce(intersect, list(waves_core_eng, w_gdp, w_unemp, w_claim, w_cpih))
waves_age_eng   <- intersect(waves_macro_eng, w_age)

core_cols_eng <- c(
  paste0(DV_BASE,  "W", waves_macro_eng),
  paste0(ENG_BASE, "W", waves_macro_eng),
  paste0(TIME_BASE,"W", waves_macro_eng),
  paste0(AGE_BASE, "W", waves_age_eng)
)

df_core_eng <- df |>
  mutate(across(any_of(core_cols_eng), zap_if_labelled)) |>
  select(id, any_of(core_cols_eng))

df_long_core_eng <- df_core_eng |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", ENG_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), engl = all_of(ENG_BASE))

df_long_time_eng <- df_core_eng |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long_eng <- left_join(df_long_core_eng, df_long_time_eng, by = c("id", "wave"))

if (length(waves_age_eng) > 0) {
  age_long_eng <- df_core_eng |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long_eng <- left_join(df_long_eng, age_long_eng, by = c("id", "wave"))
}

df_long_eng <- df_long_eng |>
  mutate(time = suppressWarnings(ymd_hms(time, quiet = TRUE)),
         year = year(time),
         dv   = as.numeric(dv),
         engl = as.numeric(engl),
         age  = as.numeric(age),
         engl = dplyr::na_if(engl, 9999)) |>
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave))

df_long_eng <- df_long_eng |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro_eng), by = c("id", "wave"))

df_long_eng <- df_long_eng |>
  mutate(engl_num = as.numeric(engl),
         engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7"))

stopifnot(all(c("dv", "engl", "wave", "id") %in% names(df_long_eng)))
```

```{r estimate-brit, include=FALSE}
# ── Britishness continuous ────────────────────────────────────────────────────
# NOTE: macro indicators vary only at the national–wave level.
# In id + wave FE models their main effect is absorbed by wave FE.
# poly(wave, 3) models replace wave FE with a cubic polynomial to allow
# identification of the macro indicator's direct association.

models_gdp <- list(
  main_poly    = feols(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main         = feols(dv ~ brit + gdp_pc        | id + wave, data = df_long, cluster = ~id),
  main_age_poly= feols(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age     = feols(dv ~ brit + gdp_pc + age  | id + wave, data = df_long, cluster = ~id),
  int          = feols(dv ~ brit * gdp_pc        | id + wave, data = df_long, cluster = ~id),
  int_age      = feols(dv ~ brit * gdp_pc + age  | id + wave, data = df_long, cluster = ~id)
)

models_unemp <- list(
  main_poly    = feols(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main         = feols(dv ~ brit + unempl_rate        | id + wave, data = df_long, cluster = ~id),
  main_age_poly= feols(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age     = feols(dv ~ brit + unempl_rate + age  | id + wave, data = df_long, cluster = ~id),
  int          = feols(dv ~ brit * unempl_rate        | id + wave, data = df_long, cluster = ~id),
  int_age      = feols(dv ~ brit * unempl_rate + age  | id + wave, data = df_long, cluster = ~id)
)

models_claim <- list(
  main_poly    = feols(dv ~ claimant_k + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main         = feols(dv ~ brit + claimant_k        | id + wave, data = df_long, cluster = ~id),
  main_age_poly= feols(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age     = feols(dv ~ brit + claimant_k + age  | id + wave, data = df_long, cluster = ~id),
  int          = feols(dv ~ brit * claimant_k        | id + wave, data = df_long, cluster = ~id),
  int_age      = feols(dv ~ brit * claimant_k + age  | id + wave, data = df_long, cluster = ~id)
)

models_cpih <- list(
  main_poly    = feols(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main         = feols(dv ~ brit + cpih_rate        | id + wave, data = df_long, cluster = ~id),
  main_age_poly= feols(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  main_age     = feols(dv ~ brit + cpih_rate + age  | id + wave, data = df_long, cluster = ~id),
  int          = feols(dv ~ brit * cpih_rate        | id + wave, data = df_long, cluster = ~id),
  int_age      = feols(dv ~ brit * cpih_rate + age  | id + wave, data = df_long, cluster = ~id)
)

# ── Britishness economic robustness (does macro predict identity?) ─────────────
brit_econ_rob <- list(
  gdp    = feols(brit ~ gdp_pc      + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  unemp  = feols(brit ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  claim  = feols(brit ~ claimant_k  + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id),
  cpih   = feols(brit ~ cpih_rate   + poly(wave, 3, raw = TRUE) | id, data = df_long, cluster = ~id)
)
```

```{r estimate-brit-cat, include=FALSE}
run_macro_cat_brit <- function(varname) {
  list(
    main     = feols(as.formula(paste0("dv ~ brit_cat + ", varname, " | id + wave")),
                     data = df_long, cluster = ~id),
    main_age = feols(as.formula(paste0("dv ~ brit_cat + ", varname, " + age | id + wave")),
                     data = df_long, cluster = ~id),
    int      = feols(as.formula(paste0("dv ~ brit_cat * ", varname, " | id + wave")),
                     data = df_long, cluster = ~id),
    int_age  = feols(as.formula(paste0("dv ~ brit_cat * ", varname, " + age | id + wave")),
                     data = df_long, cluster = ~id)
  )
}

models_gdp_cat   <- run_macro_cat_brit("gdp_pc")
models_unemp_cat <- run_macro_cat_brit("unempl_rate")
models_claim_cat <- run_macro_cat_brit("claimant_k")
models_cpih_cat  <- run_macro_cat_brit("cpih_rate")
```

```{r estimate-engl, include=FALSE}
models_gdp_eng <- list(
  main_poly    = feols(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main         = feols(dv ~ engl + gdp_pc        | id + wave, data = df_long_eng, cluster = ~id),
  main_age_poly= feols(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age     = feols(dv ~ engl + gdp_pc + age  | id + wave, data = df_long_eng, cluster = ~id),
  int          = feols(dv ~ engl * gdp_pc        | id + wave, data = df_long_eng, cluster = ~id),
  int_age      = feols(dv ~ engl * gdp_pc + age  | id + wave, data = df_long_eng, cluster = ~id)
)

models_unemp_eng <- list(
  main_poly    = feols(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main         = feols(dv ~ engl + unempl_rate        | id + wave, data = df_long_eng, cluster = ~id),
  main_age_poly= feols(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age     = feols(dv ~ engl + unempl_rate + age  | id + wave, data = df_long_eng, cluster = ~id),
  int          = feols(dv ~ engl * unempl_rate        | id + wave, data = df_long_eng, cluster = ~id),
  int_age      = feols(dv ~ engl * unempl_rate + age  | id + wave, data = df_long_eng, cluster = ~id)
)

models_claim_eng <- list(
  main_poly    = feols(dv ~ claimant_k + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main         = feols(dv ~ engl + claimant_k        | id + wave, data = df_long_eng, cluster = ~id),
  main_age_poly= feols(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age     = feols(dv ~ engl + claimant_k + age  | id + wave, data = df_long_eng, cluster = ~id),
  int          = feols(dv ~ engl * claimant_k        | id + wave, data = df_long_eng, cluster = ~id),
  int_age      = feols(dv ~ engl * claimant_k + age  | id + wave, data = df_long_eng, cluster = ~id)
)

models_cpih_eng <- list(
  main_poly    = feols(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main         = feols(dv ~ engl + cpih_rate        | id + wave, data = df_long_eng, cluster = ~id),
  main_age_poly= feols(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  main_age     = feols(dv ~ engl + cpih_rate + age  | id + wave, data = df_long_eng, cluster = ~id),
  int          = feols(dv ~ engl * cpih_rate        | id + wave, data = df_long_eng, cluster = ~id),
  int_age      = feols(dv ~ engl * cpih_rate + age  | id + wave, data = df_long_eng, cluster = ~id)
)

engl_econ_rob <- list(
  gdp    = feols(engl ~ gdp_pc      + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  unemp  = feols(engl ~ unempl_rate + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  claim  = feols(engl ~ claimant_k  + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id),
  cpih   = feols(engl ~ cpih_rate   + poly(wave, 3, raw = TRUE) | id, data = df_long_eng, cluster = ~id)
)
```

```{r estimate-engl-cat, include=FALSE}
run_macro_cat_engl <- function(varname) {
  list(
    main     = feols(as.formula(paste0("dv ~ engl_cat + ", varname, " | id + wave")),
                     data = df_long_eng, cluster = ~id),
    main_age = feols(as.formula(paste0("dv ~ engl_cat + ", varname, " + age | id + wave")),
                     data = df_long_eng, cluster = ~id),
    int      = feols(as.formula(paste0("dv ~ engl_cat * ", varname, " | id + wave")),
                     data = df_long_eng, cluster = ~id),
    int_age  = feols(as.formula(paste0("dv ~ engl_cat * ", varname, " + age | id + wave")),
                     data = df_long_eng, cluster = ~id)
  )
}

models_gdp_eng_cat   <- run_macro_cat_engl("gdp_pc")
models_unemp_eng_cat <- run_macro_cat_engl("unempl_rate")
models_claim_eng_cat <- run_macro_cat_engl("claimant_k")
models_cpih_eng_cat  <- run_macro_cat_engl("cpih_rate")
```

---

This appendix reports the full model output supporting the macro-level analysis in Section 4.4 of the main text. All models use individual fixed effects with standard errors clustered at the respondent level. The outcome throughout is `immigSelf`. The macro-level analysis introduces a design feature absent from the micro and meso appendices: because all four macro indicators — national unemployment rate, claimant count, GDP per capita, and CPIH inflation — vary only at the national–wave level, their main effects are fully absorbed by wave fixed effects in standard `id + wave` FE specifications. To allow identification of each indicator's direct association with immigration attitudes, the script therefore also includes `id`-FE-only models with a cubic wave polynomial (`poly(wave, 3)`) that controls for smooth temporal trends without absorbing wave-level variation entirely. These polynomial models appear as the "direct effect" columns in each table; the `id + wave` FE models (with wave FE absorbing the macro main effect) are the preferred specifications for the interaction tests. Section C.1 presents the main Britishness models for all four indicators; Section C.2 reports the categorical Britishness robustness check; Section C.3 presents the Englishness models; Section C.4 reports the categorical Englishness robustness check; Section C.5 reports auxiliary models testing whether macro conditions predict national identification itself; and Section C.6 describes the macro variables.

---

# C.1 Main Models: Britishness (Continuous) {#sec-c1-brit}

## C.1.1 National Unemployment Rate {#sec-c1-brit-unemp}

In the polynomial-trend specifications, the national unemployment rate exhibits a positive direct association with immigration attitudes, indicating that periods of higher national unemployment coincide with more restrictive preferences on average. Once wave fixed effects are included, this main effect is absorbed, but the interaction between unemployment and Britishness is negative and statistically significant: the attitudinal relevance of national identification is amplified during periods of elevated national unemployment, with more restrictive attitudes concentrated among weaker identifiers relative to stronger ones.

```{r c1-brit-unemp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_unemp$main_poly,
    "(2) + Britishness"      = models_unemp$main,
    "(3) Direct + Age (poly)"= models_unemp$main_age_poly,
    "(4) + Britishness"      = models_unemp$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.1. National Unemployment Rate and Immigration Attitudes: Main Effects (Britishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r c1-brit-unemp-int}
modelsummary(
  list(
    "(1) Interaction"       = models_unemp$int,
    "(2) Interaction + Age" = models_unemp$int_age
  ),
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate",
                  "brit:unempl_rate" = "Britishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.2. National Unemployment Rate × Britishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## C.1.2 National Claimant Count {#sec-c1-brit-claim}

The claimant count results closely parallel the unemployment findings. In polynomial-trend models, higher national claimant intensity is associated with more restrictive immigration attitudes. In the interaction specifications with wave FE, the claimant count × Britishness interaction is negative and significant, indicating that periods of elevated national welfare dependency are associated with sharper identity-based attitudinal stratification — more restrictive attitudes among weaker identifiers, attenuating as Britishness increases.

```{r c1-brit-claim-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_claim$main_poly,
    "(2) + Britishness"      = models_claim$main,
    "(3) Direct + Age (poly)"= models_claim$main_age_poly,
    "(4) + Britishness"      = models_claim$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.3. National Claimant Count and Immigration Attitudes: Main Effects (Britishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r c1-brit-claim-int}
modelsummary(
  list(
    "(1) Interaction"       = models_claim$int,
    "(2) Interaction + Age" = models_claim$int_age
  ),
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)",
                  "brit:claimant_k" = "Britishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.4. National Claimant Count × Britishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## C.1.3 GDP per Capita {#sec-c1-brit-gdp}

In polynomial-trend specifications, GDP per capita is negatively associated with immigration attitudes, indicating that periods of higher national prosperity coincide with more permissive preferences on average. In the interaction models with wave FE, the GDP × Britishness interaction is negative and statistically significant, consistent with the other macro indicators: national economic conditions condition how strongly Britishness structures immigration attitudes, with the identity–attitude association weakening as GDP rises.

```{r c1-brit-gdp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_gdp$main_poly,
    "(2) + Britishness"      = models_gdp$main,
    "(3) Direct + Age (poly)"= models_gdp$main_age_poly,
    "(4) + Britishness"      = models_gdp$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.5. GDP per Capita and Immigration Attitudes: Main Effects (Britishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r c1-brit-gdp-int}
modelsummary(
  list(
    "(1) Interaction"       = models_gdp$int,
    "(2) Interaction + Age" = models_gdp$int_age
  ),
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita",
                  "brit:gdp_pc" = "Britishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.6. GDP per Capita × Britishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## C.1.4 CPIH Inflation {#sec-c1-brit-cpih}

CPIH shows no significant direct association with immigration attitudes in polynomial-trend specifications. In the interaction models, however, the CPIH × Britishness interaction is negative and highly significant — the strongest interaction effect among the four macro indicators. Periods of elevated consumer-price inflation sharpen identity-based attitudinal stratification, with weaker British identifiers becoming markedly more restrictive relative to stronger identifiers. This pattern is fully robust to age controls.

```{r c1-brit-cpih-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_cpih$main_poly,
    "(2) + Britishness"      = models_cpih$main,
    "(3) Direct + Age (poly)"= models_cpih$main_age_poly,
    "(4) + Britishness"      = models_cpih$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.7. CPIH Inflation and Immigration Attitudes: Main Effects (Britishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r c1-brit-cpih-int}
modelsummary(
  list(
    "(1) Interaction"       = models_cpih$int,
    "(2) Interaction + Age" = models_cpih$int_age
  ),
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation",
                  "brit:cpih_rate" = "Britishness × CPIH", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C1.8. CPIH Inflation × Britishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

---

# C.2 Robustness: Britishness (Categorical) {#sec-c2-brit-cat}

Re-estimating all four macro interaction models with Britishness entered as a categorical variable (reference: 7, "very strongly British") confirms the gradient structure and the moderation patterns documented in Section C.1. Britishness category coefficients are positive, precisely estimated, and monotonically ordered across all four indicators. Interaction terms reveal that macro-economic conditions widen attitudinal gaps most clearly between weakly and strongly British respondents, with conditional effects concentrated at lower identity positions and attenuating toward the reference category.

## C.2.1 National Unemployment Rate {#sec-c2-brit-unemp}

```{r c2-brit-unemp}
modelsummary(
  list("(1) No age" = models_unemp_cat$main, "(2) Age" = models_unemp_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.1. Unemployment Rate: Britishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c2-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_cat$int, "(2) Interaction + Age" = models_unemp_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.2. Unemployment Rate × Britishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.2.2 National Claimant Count {#sec-c2-brit-claim}

```{r c2-brit-claim}
modelsummary(
  list("(1) No age" = models_claim_cat$main, "(2) Age" = models_claim_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.3. Claimant Count: Britishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c2-brit-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_cat$int, "(2) Interaction + Age" = models_claim_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.4. Claimant Count × Britishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.2.3 GDP per Capita {#sec-c2-brit-gdp}

```{r c2-brit-gdp}
modelsummary(
  list("(1) No age" = models_gdp_cat$main, "(2) Age" = models_gdp_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.5. GDP per Capita: Britishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c2-brit-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_cat$int, "(2) Interaction + Age" = models_gdp_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.6. GDP per Capita × Britishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.2.4 CPIH Inflation {#sec-c2-brit-cpih}

```{r c2-brit-cpih}
modelsummary(
  list("(1) No age" = models_cpih_cat$main, "(2) Age" = models_cpih_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.7. CPIH Inflation: Britishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c2-brit-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_cat$int, "(2) Interaction + Age" = models_cpih_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C2.8. CPIH Inflation × Britishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.3 Main Models: Englishness (Continuous) {#sec-c3-engl}

Re-estimating the full set of macro models with Englishness as the identity measure reveals a consistent pattern: macro-economic conditions condition immigration attitudes more strongly through Englishness than through Britishness. All four interaction terms are negative and significant under Englishness, and their magnitudes exceed the corresponding Britishness estimates, particularly for CPIH and claimant count. This reinforces the interpretation that Englishness is the more economically reactive identity dimension at the macro level.

## C.3.1 National Unemployment Rate {#sec-c3-engl-unemp}

```{r c3-engl-unemp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_unemp_eng$main_poly,
    "(2) + Englishness"      = models_unemp_eng$main,
    "(3) Direct + Age (poly)"= models_unemp_eng$main_age_poly,
    "(4) + Englishness"      = models_unemp_eng$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.1. National Unemployment Rate and Immigration Attitudes: Main Effects (Englishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c3-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng$int, "(2) Interaction + Age" = models_unemp_eng$int_age),
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate",
                  "engl:unempl_rate" = "Englishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.2. National Unemployment Rate × Englishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.3.2 National Claimant Count {#sec-c3-engl-claim}

```{r c3-engl-claim-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_claim_eng$main_poly,
    "(2) + Englishness"      = models_claim_eng$main,
    "(3) Direct + Age (poly)"= models_claim_eng$main_age_poly,
    "(4) + Englishness"      = models_claim_eng$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.3. National Claimant Count and Immigration Attitudes: Main Effects (Englishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c3-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng$int, "(2) Interaction + Age" = models_claim_eng$int_age),
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)",
                  "engl:claimant_k" = "Englishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.4. National Claimant Count × Englishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.3.3 GDP per Capita {#sec-c3-engl-gdp}

```{r c3-engl-gdp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_gdp_eng$main_poly,
    "(2) + Englishness"      = models_gdp_eng$main,
    "(3) Direct + Age (poly)"= models_gdp_eng$main_age_poly,
    "(4) + Englishness"      = models_gdp_eng$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.5. GDP per Capita and Immigration Attitudes: Main Effects (Englishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c3-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng$int, "(2) Interaction + Age" = models_gdp_eng$int_age),
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita",
                  "engl:gdp_pc" = "Englishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.6. GDP per Capita × Englishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.3.4 CPIH Inflation {#sec-c3-engl-cpih}

```{r c3-engl-cpih-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_cpih_eng$main_poly,
    "(2) + Englishness"      = models_cpih_eng$main,
    "(3) Direct + Age (poly)"= models_cpih_eng$main_age_poly,
    "(4) + Englishness"      = models_cpih_eng$main_age
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.7. CPIH Inflation and Immigration Attitudes: Main Effects (Englishness)",
  notes   = "Cols 1 & 3: individual FE + cubic wave polynomial; cols 2 & 4: individual and wave FE. SEs clustered by respondent. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c3-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng$int, "(2) Interaction + Age" = models_cpih_eng$int_age),
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation",
                  "engl:cpih_rate" = "Englishness × CPIH", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C3.8. CPIH Inflation × Englishness: Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. DV: immigSelf. Macro main effect absorbed by wave FE.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.4 Robustness: Englishness (Categorical) {#sec-c4-engl-cat}

Categorical Englishness specifications confirm the gradient and moderation patterns documented in Section C.3. All four macro indicators widen attitudinal gaps along the Englishness dimension, with interaction effects concentrated among weaker identifiers and attenuating toward the reference category (Englishness = 7). The CPIH and claimant interactions are the largest in magnitude, consistent with the continuous results.

## C.4.1 National Unemployment Rate {#sec-c4-engl-unemp}

```{r c4-engl-unemp}
modelsummary(
  list("(1) No age" = models_unemp_eng_cat$main, "(2) Age" = models_unemp_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.1. Unemployment Rate: Englishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c4-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng_cat$int, "(2) Interaction + Age" = models_unemp_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.2. Unemployment Rate × Englishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.4.2 National Claimant Count {#sec-c4-engl-claim}

```{r c4-engl-claim}
modelsummary(
  list("(1) No age" = models_claim_eng_cat$main, "(2) Age" = models_claim_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.3. Claimant Count: Englishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c4-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng_cat$int, "(2) Interaction + Age" = models_claim_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.4. Claimant Count × Englishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.4.3 GDP per Capita {#sec-c4-engl-gdp}

```{r c4-engl-gdp}
modelsummary(
  list("(1) No age" = models_gdp_eng_cat$main, "(2) Age" = models_gdp_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.5. GDP per Capita: Englishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c4-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng_cat$int, "(2) Interaction + Age" = models_gdp_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.6. GDP per Capita × Englishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.4.4 CPIH Inflation {#sec-c4-engl-cpih}

```{r c4-engl-cpih}
modelsummary(
  list("(1) No age" = models_cpih_eng_cat$main, "(2) Age" = models_cpih_eng_cat$main_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.7. CPIH Inflation: Englishness (Categorical) Main Effects",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c4-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng_cat$int, "(2) Interaction + Age" = models_cpih_eng_cat$int_age),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C4.8. CPIH Inflation × Englishness (Categorical): Interaction Models",
  notes   = "Individual and wave FE. SEs clustered by respondent. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.5 Auxiliary: Do Macro Conditions Predict National Identification? {#sec-c5-rob}

A potential confound in the interaction models is the possibility that macro-economic conditions themselves predict changes in Britishness or Englishness within individuals, which would imply that the interaction captures indirect pathways rather than pure moderation. The tables below address this concern directly: the dependent variable is national identification itself, regressed on each macro indicator with individual fixed effects and a cubic wave polynomial. None of the four macro indicators predict within-individual changes in either Britishness or Englishness, confirming that the interaction effects reported in Sections C.1–C.4 reflect contextual moderation of a stable identity–attitudes relationship rather than macro-induced identity change.

```{r c5-brit-rob}
modelsummary(
  list(
    "GDP"       = brit_econ_rob$gdp,
    "Unemp."    = brit_econ_rob$unemp,
    "Claimant"  = brit_econ_rob$claim,
    "CPIH"      = brit_econ_rob$cpih
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C5.1. Auxiliary: Do Macro Conditions Predict Britishness?",
  notes   = "Individual FE + cubic wave polynomial. SEs clustered by respondent. Dependent variable: Britishness (1–7). Wave polynomial coefficients suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c5-engl-rob}
modelsummary(
  list(
    "GDP"       = engl_econ_rob$gdp,
    "Unemp."    = engl_econ_rob$unemp,
    "Claimant"  = engl_econ_rob$claim,
    "CPIH"      = engl_econ_rob$cpih
  ),
  coef_omit   = "poly\\(wave",
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C5.2. Auxiliary: Do Macro Conditions Predict Englishness?",
  notes   = "Individual FE + cubic wave polynomial. SEs clustered by respondent. Dependent variable: Englishness (1–7). Wave polynomial coefficients suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.6 Description of Macro-Level Variables {#sec-c6-vars}

The macro-level indicators used in this appendix capture objective national economic conditions in the United Kingdom. All variables are derived from official ONS sources and merged to the BES panel using fieldwork year, before being reshaped to match the wave-based structure of the survey.

**National unemployment rate.** The share of the economically active population that is unemployed, based on ONS labour market statistics. Available at quarterly frequency; collapsed to annual means corresponding to each BES fieldwork year. Captures aggregate labour-market conditions and economy-wide employment-related stress.

**Claimant count.** The number of individuals claiming unemployment-related benefits nationally (Jobseeker's Allowance and the unemployment component of Universal Credit), from ONS claimant-count statistics. Available quarterly and aggregated to annual means per BES wave. Reflects welfare-based labour-market strain and the administrative visibility of economic hardship.

**GDP per capita.** National output per person from ONS national accounts. Available quarterly and collapsed to annual means per fieldwork year. Proxies aggregate economic prosperity rather than labour-market insecurity.

**Inflation (CPIH).** Consumer price inflation including owner-occupiers' housing costs, from ONS price statistics. Available quarterly and aggregated to annual means per BES wave. Captures cost-of-living pressure and purchasing-power erosion — a dimension of macro-economic strain not directly captured by labour-market indicators.

---

*End of Appendix C.*
