---
title: "Online Appendix C.6b: Macro-Level Models — Random Effects (Englishness)"
subtitle: "Estimator Comparison for National Economic Context — Englishness Specifications"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-location: left
    theme: cosmo
    embed-resources: true
    echo: false
    warning: false
    message: false
    fig-width: 8
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(lubridate)
library(haven)
library(lme4)
library(lmerTest)
library(modelsummary)
library(kableExtra)

options(modelsummary_factory_default = "kableExtra")

GOF_MAP <- tribble(
  ~raw,            ~clean,         ~fmt,
  "nobs",          "Observations", 0,
  "adj.r.squared", "Adj. R²",      3,
  "r.squared",     "R²",           3,
  "AIC",           "AIC",          1,
  "BIC",           "BIC",          1
)

OMIT_WAVE <- "factor\\(wave\\)|poly\\(wave"
ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

zap_if_labelled <- function(x) {
  if (inherits(x, "haven_labelled")) return(zap_labels(x))
  x
}

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE          <- "immigSelf"
ENG_BASE         <- "englishness"
TIME_BASE        <- "starttime"
AGE_BASE         <- "age"
MACRO_GDP_BASE   <- "gdp_pc"
MACRO_UNEMP_BASE <- "unempl_rate"
MACRO_CLAIM_BASE <- "claimant_k"
MACRO_CPIH_BASE  <- "cpih_rate"

get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base) {
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

macro_long_from_base <- function(df, base, waves_keep) {
  cols <- paste0(base, "W", waves_keep)
  df |>
    select(id, any_of(cols)) |>
    pivot_longer(cols = -id, names_to = "wave",
                 names_pattern = paste0("^", base, "W(\\d+)$"),
                 values_to = base) |>
    mutate(wave = as.integer(wave))
}
```

```{r build-panel-engl, include=FALSE}
w_dv    <- waves_available(df, DV_BASE)
w_eng   <- waves_available(df, ENG_BASE)
w_time  <- waves_available(df, TIME_BASE)
w_age   <- waves_available(df, AGE_BASE)
w_gdp   <- waves_available(df, MACRO_GDP_BASE)
w_unemp <- waves_available(df, MACRO_UNEMP_BASE)
w_claim <- waves_available(df, MACRO_CLAIM_BASE)
w_cpih  <- waves_available(df, MACRO_CPIH_BASE)

waves_core_eng  <- Reduce(intersect, list(w_dv, w_eng, w_time))
waves_macro_eng <- Reduce(intersect, list(waves_core_eng, w_gdp, w_unemp, w_claim, w_cpih))
waves_age_eng   <- intersect(waves_macro_eng, w_age)

core_cols_eng <- c(
  paste0(DV_BASE,  "W", waves_macro_eng),
  paste0(ENG_BASE, "W", waves_macro_eng),
  paste0(TIME_BASE,"W", waves_macro_eng),
  paste0(AGE_BASE, "W", waves_age_eng)
)

df_core_eng <- df |>
  mutate(across(any_of(core_cols_eng), zap_if_labelled)) |>
  select(id, any_of(core_cols_eng))

df_long_core_eng <- df_core_eng |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", ENG_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), engl = all_of(ENG_BASE))

df_long_time_eng <- df_core_eng |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long_eng <- left_join(df_long_core_eng, df_long_time_eng, by = c("id", "wave"))

if (length(waves_age_eng) > 0) {
  age_long_eng <- df_core_eng |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long_eng <- left_join(df_long_eng, age_long_eng, by = c("id", "wave"))
  rm(age_long_eng)
}

rm(df_core_eng, df_long_core_eng, df_long_time_eng)
invisible(gc(verbose = FALSE))

df_long_eng <- df_long_eng |>
  mutate(
    time = suppressWarnings(ymd_hms(as.character(time), quiet = TRUE)),
    year = year(time),
    dv   = as.numeric(dv),
    engl = as.numeric(engl),
    age  = as.numeric(age),
    engl = dplyr::na_if(engl, 9999)
  ) |>
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave)) |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro_eng), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro_eng), by = c("id", "wave")) |>
  mutate(engl_num = as.numeric(engl),
         engl_cat = relevel(factor(engl_num, levels = 1:7), ref = "7"))

stopifnot(all(c("dv", "engl", "wave", "id") %in% names(df_long_eng)))
invisible(gc(verbose = FALSE))
```

---

This appendix (Part b) reports random-effects models for Englishness. The companion file, Appendix C.6a, covers the Britishness specifications. Models are estimated one indicator at a time with memory freed between indicators to avoid exhausting RAM. All RE models use REML with a random intercept for respondent (`1|id`). Wave effects are handled as cubic polynomial `poly(wave, 3)` in direct-effect models and as fixed wave dummies `factor(wave)` in interaction models. Wave polynomial and dummy coefficients are suppressed from all tables for readability.

---

# C.6.3 Main Models: Englishness (Continuous) {#sec-c6-engl}

The Englishness RE macro models replicate the Britishness structure with Englishness as the identity moderator. Macro-economic conditions condition immigration attitudes more strongly through Englishness than through Britishness across all four indicators: interaction terms are negative and significant throughout, and their magnitudes tend to exceed the corresponding Britishness estimates, particularly for CPIH and claimant count.

```{r estimate-unemp, include=FALSE}
models_unemp_eng_re <- list(
  main_0     = lmer(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ engl + unempl_rate + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ engl + unempl_rate + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ engl * unempl_rate + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ engl * unempl_rate + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl)
)
models_unemp_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + unempl_rate + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  main_age = lmer(dv ~ engl_cat + unempl_rate + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int      = lmer(dv ~ engl_cat * unempl_rate + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int_age  = lmer(dv ~ engl_cat * unempl_rate + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl)
)
```

## C.6.3.1 National Unemployment Rate {#sec-c6-engl-unemp}

```{r c6-engl-unemp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_unemp_eng_re$main_0,
    "(2) + Englishness"      = models_unemp_eng_re$main,
    "(3) Direct + Age (poly)"= models_unemp_eng_re$main_age_0,
    "(4) + Englishness"      = models_unemp_eng_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.17. National Unemployment Rate: RE Main Effects (Englishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng_re$int, "(2) Interaction + Age" = models_unemp_eng_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", unempl_rate = "Nat. unemp. rate",
                  "engl:unempl_rate" = "Englishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.18. National Unemployment Rate × Englishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.17.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

# C.6.4 Robustness: Englishness (Categorical) — Unemployment {#sec-c6-cat-engl-unemp}

```{r c6-cat-engl-unemp}
modelsummary(
  list("(1) No age" = models_unemp_eng_cat_re$main, "(2) Age" = models_unemp_eng_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.25. Unemployment Rate: Englishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_eng_cat_re$int, "(2) + Age" = models_unemp_eng_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.26. Unemployment Rate × Englishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r gc-free-unemp, include=FALSE}
rm(models_unemp_eng_re, models_unemp_eng_cat_re)
invisible(gc(verbose = FALSE))

models_claim_eng_re <- list(
  main_0     = lmer(dv ~ claimant_k + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ engl + claimant_k + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ engl + claimant_k + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ engl * claimant_k + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ engl * claimant_k + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl)
)
models_claim_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + claimant_k + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  main_age = lmer(dv ~ engl_cat + claimant_k + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int      = lmer(dv ~ engl_cat * claimant_k + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int_age  = lmer(dv ~ engl_cat * claimant_k + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl)
)
```

## C.6.3.2 National Claimant Count {#sec-c6-engl-claim}

```{r c6-engl-claim-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_claim_eng_re$main_0,
    "(2) + Englishness"      = models_claim_eng_re$main,
    "(3) Direct + Age (poly)"= models_claim_eng_re$main_age_0,
    "(4) + Englishness"      = models_claim_eng_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.19. National Claimant Count: RE Main Effects (Englishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng_re$int, "(2) Interaction + Age" = models_claim_eng_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", claimant_k = "Claimant count (nat.)",
                  "engl:claimant_k" = "Englishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.20. National Claimant Count × Englishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.19.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.4.2 (Categorical) National Claimant Count {#sec-c6-cat-engl-claim}

```{r c6-cat-engl-claim}
modelsummary(
  list("(1) No age" = models_claim_eng_cat_re$main, "(2) Age" = models_claim_eng_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.27. Claimant Count: Englishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-engl-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_eng_cat_re$int, "(2) + Age" = models_claim_eng_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.28. Claimant Count × Englishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r gc-free-claim, include=FALSE}
rm(models_claim_eng_re, models_claim_eng_cat_re)
invisible(gc(verbose = FALSE))

models_gdp_eng_re <- list(
  main_0     = lmer(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ engl + gdp_pc + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ engl + gdp_pc + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ engl * gdp_pc + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ engl * gdp_pc + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl)
)
models_gdp_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + gdp_pc + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  main_age = lmer(dv ~ engl_cat + gdp_pc + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int      = lmer(dv ~ engl_cat * gdp_pc + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int_age  = lmer(dv ~ engl_cat * gdp_pc + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl)
)
```

## C.6.3.3 GDP per Capita {#sec-c6-engl-gdp}

```{r c6-engl-gdp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_gdp_eng_re$main_0,
    "(2) + Englishness"      = models_gdp_eng_re$main,
    "(3) Direct + Age (poly)"= models_gdp_eng_re$main_age_0,
    "(4) + Englishness"      = models_gdp_eng_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.21. GDP per Capita: RE Main Effects (Englishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng_re$int, "(2) Interaction + Age" = models_gdp_eng_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", gdp_pc = "GDP per capita",
                  "engl:gdp_pc" = "Englishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.22. GDP per Capita × Englishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.21.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.4.3 (Categorical) GDP per Capita {#sec-c6-cat-engl-gdp}

```{r c6-cat-engl-gdp}
modelsummary(
  list("(1) No age" = models_gdp_eng_cat_re$main, "(2) Age" = models_gdp_eng_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.29. GDP per Capita: Englishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-engl-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_eng_cat_re$int, "(2) + Age" = models_gdp_eng_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.30. GDP per Capita × Englishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r gc-free-gdp, include=FALSE}
rm(models_gdp_eng_re, models_gdp_eng_cat_re)
invisible(gc(verbose = FALSE))

models_cpih_eng_re <- list(
  main_0     = lmer(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ engl + cpih_rate + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ engl + cpih_rate + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ engl * cpih_rate + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ engl * cpih_rate + age + factor(wave) + (1|id),
                    data = df_long_eng, REML = TRUE, control = ctrl)
)
models_cpih_eng_cat_re <- list(
  main     = lmer(dv ~ engl_cat + cpih_rate + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  main_age = lmer(dv ~ engl_cat + cpih_rate + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int      = lmer(dv ~ engl_cat * cpih_rate + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl),
  int_age  = lmer(dv ~ engl_cat * cpih_rate + age + factor(wave) + (1|id),
                  data = df_long_eng, REML = TRUE, control = ctrl)
)
engl_econ_rob_re <- list(
  gdp   = lmer(engl ~ gdp_pc      + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long_eng, REML = TRUE, control = ctrl),
  unemp = lmer(engl ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long_eng, REML = TRUE, control = ctrl),
  claim = lmer(engl ~ claimant_k  + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long_eng, REML = TRUE, control = ctrl),
  cpih  = lmer(engl ~ cpih_rate   + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long_eng, REML = TRUE, control = ctrl)
)
```

## C.6.3.4 CPIH Inflation {#sec-c6-engl-cpih}

```{r c6-engl-cpih-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_cpih_eng_re$main_0,
    "(2) + Englishness"      = models_cpih_eng_re$main,
    "(3) Direct + Age (poly)"= models_cpih_eng_re$main_age_0,
    "(4) + Englishness"      = models_cpih_eng_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.23. CPIH Inflation: RE Main Effects (Englishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng_re$int, "(2) Interaction + Age" = models_cpih_eng_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(engl = "Englishness", cpih_rate = "CPIH inflation",
                  "engl:cpih_rate" = "Englishness × CPIH", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.24. CPIH Inflation × Englishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.23.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.4.4 (Categorical) CPIH Inflation {#sec-c6-cat-engl-cpih}

```{r c6-cat-engl-cpih}
modelsummary(
  list("(1) No age" = models_cpih_eng_cat_re$main, "(2) Age" = models_cpih_eng_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.31. CPIH Inflation: Englishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-engl-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_eng_cat_re$int, "(2) + Age" = models_cpih_eng_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.32. CPIH Inflation × Englishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Englishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.6.6 Auxiliary: Do Macro Conditions Predict Englishness? {#sec-c6-rob-engl}

None of the four macro indicators predicts within-individual changes in Englishness, confirming that the interaction effects in Sections C.6.3–C.6.4 reflect contextual moderation rather than macro-induced identity change.

```{r c6-rob-engl}
modelsummary(
  list("GDP" = engl_econ_rob_re$gdp, "Unemp." = engl_econ_rob_re$unemp,
       "Claimant" = engl_econ_rob_re$claim, "CPIH" = engl_econ_rob_re$cpih),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.34. Auxiliary: Do Macro Conditions Predict Englishness? (RE)",
  notes   = "REML. Random intercept + cubic wave polynomial. DV: Englishness (1-7). Wave polynomial suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

*End of Appendix C.6b.*
