---
title: "Online Appendix C.6a: Macro-Level Models — Random Effects (Britishness)"
subtitle: "Estimator Comparison for National Economic Context — Britishness Specifications"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-location: left
    theme: cosmo
    embed-resources: true
    echo: false
    warning: false
    message: false
    fig-width: 8
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
library(lubridate)
library(haven)
library(lme4)
library(lmerTest)
library(modelsummary)
library(kableExtra)

options(modelsummary_factory_default = "kableExtra")

GOF_MAP <- tribble(
  ~raw,            ~clean,         ~fmt,
  "nobs",          "Observations", 0,
  "adj.r.squared", "Adj. R²",      3,
  "r.squared",     "R²",           3,
  "AIC",           "AIC",          1,
  "BIC",           "BIC",          1
)

OMIT_WAVE <- "factor\\(wave\\)|poly\\(wave"
ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

zap_if_labelled <- function(x) {
  if (inherits(x, "haven_labelled")) return(zap_labels(x))
  x
}

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE          <- "immigSelf"
BRIT_BASE        <- "britishness"
TIME_BASE        <- "starttime"
AGE_BASE         <- "age"
MACRO_GDP_BASE   <- "gdp_pc"
MACRO_UNEMP_BASE <- "unempl_rate"
MACRO_CLAIM_BASE <- "claimant_k"
MACRO_CPIH_BASE  <- "cpih_rate"

get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base) {
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

macro_long_from_base <- function(df, base, waves_keep) {
  cols <- paste0(base, "W", waves_keep)
  df |>
    select(id, any_of(cols)) |>
    pivot_longer(cols = -id, names_to = "wave",
                 names_pattern = paste0("^", base, "W(\\d+)$"),
                 values_to = base) |>
    mutate(wave = as.integer(wave))
}
```

```{r build-panel-brit, include=FALSE}
w_dv    <- waves_available(df, DV_BASE)
w_brit  <- waves_available(df, BRIT_BASE)
w_time  <- waves_available(df, TIME_BASE)
w_age   <- waves_available(df, AGE_BASE)
w_gdp   <- waves_available(df, MACRO_GDP_BASE)
w_unemp <- waves_available(df, MACRO_UNEMP_BASE)
w_claim <- waves_available(df, MACRO_CLAIM_BASE)
w_cpih  <- waves_available(df, MACRO_CPIH_BASE)

waves_core  <- Reduce(intersect, list(w_dv, w_brit, w_time))
waves_macro <- Reduce(intersect, list(waves_core, w_gdp, w_unemp, w_claim, w_cpih))
waves_age   <- intersect(waves_macro, w_age)

core_cols <- c(
  paste0(DV_BASE,   "W", waves_macro),
  paste0(BRIT_BASE, "W", waves_macro),
  paste0(TIME_BASE, "W", waves_macro),
  paste0(AGE_BASE,  "W", waves_age)
)

df_core <- df |>
  mutate(across(any_of(core_cols), zap_if_labelled)) |>
  select(id, any_of(core_cols))

df_long_core <- df_core |>
  pivot_longer(
    cols = matches(paste0("^(", DV_BASE, "|", BRIT_BASE, ")W\\d+$")),
    names_to = c("var", "wave"), names_pattern = "^(.*)W(\\d+)$",
    values_to = "value"
  ) |>
  mutate(wave = as.integer(wave)) |>
  pivot_wider(names_from = var, values_from = value) |>
  rename(dv = all_of(DV_BASE), brit = all_of(BRIT_BASE))

df_long_time <- df_core |>
  pivot_longer(cols = matches(paste0("^", TIME_BASE, "W\\d+$")),
               names_to = "wave",
               names_pattern = paste0("^", TIME_BASE, "W(\\d+)$"),
               values_to = "time") |>
  mutate(wave = as.integer(wave), time = as.character(time))

df_long <- left_join(df_long_core, df_long_time, by = c("id", "wave"))

if (length(waves_age) > 0) {
  age_long <- df_core |>
    pivot_longer(cols = matches(paste0("^", AGE_BASE, "W\\d+$")),
                 names_to = "wave",
                 names_pattern = paste0("^", AGE_BASE, "W(\\d+)$"),
                 values_to = "age") |>
    mutate(wave = as.integer(wave))
  df_long <- left_join(df_long, age_long, by = c("id", "wave"))
}

df_long <- df_long |>
  mutate(
    time = suppressWarnings(ymd_hms(time, quiet = TRUE)),
    year = year(time),
    brit = as.numeric(brit),
    dv   = as.numeric(dv),
    age  = as.numeric(age)
  ) |>
  left_join(macro_long_from_base(df, MACRO_GDP_BASE,   waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_UNEMP_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CLAIM_BASE, waves_macro), by = c("id", "wave")) |>
  left_join(macro_long_from_base(df, MACRO_CPIH_BASE,  waves_macro), by = c("id", "wave")) |>
  mutate(brit_num = as.numeric(brit),
         brit_cat = relevel(factor(brit_num, levels = 1:7), ref = "7"))
```

```{r estimate-brit, include=FALSE}
models_unemp_re <- list(
  main_0     = lmer(dv ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ brit + unempl_rate + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ unempl_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ brit + unempl_rate + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ brit * unempl_rate + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ brit * unempl_rate + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl)
)

models_claim_re <- list(
  main_0     = lmer(dv ~ claimant_k + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ brit + claimant_k + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ claimant_k + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ brit + claimant_k + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ brit * claimant_k + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ brit * claimant_k + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl)
)

models_gdp_re <- list(
  main_0     = lmer(dv ~ gdp_pc + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ brit + gdp_pc + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ gdp_pc + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ brit + gdp_pc + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ brit * gdp_pc + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ brit * gdp_pc + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl)
)

models_cpih_re <- list(
  main_0     = lmer(dv ~ cpih_rate + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main       = lmer(dv ~ brit + cpih_rate + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age_0 = lmer(dv ~ cpih_rate + age + poly(wave, 3, raw = TRUE) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  main_age   = lmer(dv ~ brit + cpih_rate + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int        = lmer(dv ~ brit * cpih_rate + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl),
  int_age    = lmer(dv ~ brit * cpih_rate + age + factor(wave) + (1|id),
                    data = df_long, REML = TRUE, control = ctrl)
)

brit_econ_rob_re <- list(
  gdp   = lmer(brit ~ gdp_pc      + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long, REML = TRUE, control = ctrl),
  unemp = lmer(brit ~ unempl_rate + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long, REML = TRUE, control = ctrl),
  claim = lmer(brit ~ claimant_k  + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long, REML = TRUE, control = ctrl),
  cpih  = lmer(brit ~ cpih_rate   + poly(wave, 3, raw = TRUE) + (1|id),
               data = df_long, REML = TRUE, control = ctrl)
)
```

```{r estimate-brit-cat, include=FALSE}
run_macro_cat_brit_re <- function(varname) {
  list(
    main     = lmer(as.formula(paste0("dv ~ brit_cat + ", varname, " + factor(wave) + (1|id)")),
                    data = df_long, REML = TRUE, control = ctrl),
    main_age = lmer(as.formula(paste0("dv ~ brit_cat + ", varname, " + age + factor(wave) + (1|id)")),
                    data = df_long, REML = TRUE, control = ctrl),
    int      = lmer(as.formula(paste0("dv ~ brit_cat * ", varname, " + factor(wave) + (1|id)")),
                    data = df_long, REML = TRUE, control = ctrl),
    int_age  = lmer(as.formula(paste0("dv ~ brit_cat * ", varname, " + age + factor(wave) + (1|id)")),
                    data = df_long, REML = TRUE, control = ctrl)
  )
}

models_unemp_cat_re <- run_macro_cat_brit_re("unempl_rate")
models_claim_cat_re <- run_macro_cat_brit_re("claimant_k")
models_gdp_cat_re   <- run_macro_cat_brit_re("gdp_pc")
models_cpih_cat_re  <- run_macro_cat_brit_re("cpih_rate")
```

---

This appendix (Part a) reports random-effects models for Britishness. The companion file, Appendix C.6b, covers the Englishness specifications. All RE models are estimated via REML with a random intercept for respondent (`1|id`). Because all four macro indicators vary only at the national–wave level, wave effects are handled two ways: cubic polynomial `poly(wave, 3)` in the "direct effect" models where the macro indicator's own coefficient needs to be identified, and fixed wave dummies `factor(wave)` in the interaction models. Wave polynomial and dummy coefficients are suppressed from all tables for readability.

---

# C.6.1 Main Models: Britishness (Continuous) {#sec-c6-brit}

## C.6.1.1 National Unemployment Rate {#sec-c6-brit-unemp}

```{r c6-brit-unemp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_unemp_re$main_0,
    "(2) + Britishness"      = models_unemp_re$main,
    "(3) Direct + Age (poly)"= models_unemp_re$main_age_0,
    "(4) + Britishness"      = models_unemp_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.1. National Unemployment Rate: RE Main Effects (Britishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_re$int, "(2) Interaction + Age" = models_unemp_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", unempl_rate = "Nat. unemp. rate",
                  "brit:unempl_rate" = "Britishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.2. National Unemployment Rate × Britishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.1 for direct effect.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.1.2 National Claimant Count {#sec-c6-brit-claim}

```{r c6-brit-claim-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_claim_re$main_0,
    "(2) + Britishness"      = models_claim_re$main,
    "(3) Direct + Age (poly)"= models_claim_re$main_age_0,
    "(4) + Britishness"      = models_claim_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.3. National Claimant Count: RE Main Effects (Britishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-brit-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_re$int, "(2) Interaction + Age" = models_claim_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", claimant_k = "Claimant count (nat.)",
                  "brit:claimant_k" = "Britishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.4. National Claimant Count × Britishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.3.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.1.3 GDP per Capita {#sec-c6-brit-gdp}

```{r c6-brit-gdp-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_gdp_re$main_0,
    "(2) + Britishness"      = models_gdp_re$main,
    "(3) Direct + Age (poly)"= models_gdp_re$main_age_0,
    "(4) + Britishness"      = models_gdp_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.5. GDP per Capita: RE Main Effects (Britishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-brit-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_re$int, "(2) Interaction + Age" = models_gdp_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", gdp_pc = "GDP per capita",
                  "brit:gdp_pc" = "Britishness × GDP per capita", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.6. GDP per Capita × Britishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.5.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.1.4 CPIH Inflation {#sec-c6-brit-cpih}

```{r c6-brit-cpih-main}
modelsummary(
  list(
    "(1) Direct (poly)"      = models_cpih_re$main_0,
    "(2) + Britishness"      = models_cpih_re$main,
    "(3) Direct + Age (poly)"= models_cpih_re$main_age_0,
    "(4) + Britishness"      = models_cpih_re$main_age
  ),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.7. CPIH Inflation: RE Main Effects (Britishness)",
  notes   = "REML. Cols 1 & 3: random intercept + cubic wave polynomial. Cols 2 & 4: random intercept + wave dummies. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-brit-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_re$int, "(2) Interaction + Age" = models_cpih_re$int_age),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(brit = "Britishness", cpih_rate = "CPIH inflation",
                  "brit:cpih_rate" = "Britishness × CPIH", age = "Age"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.8. CPIH Inflation × Britishness: RE Interaction",
  notes   = "REML. Random intercept + wave dummies. Macro main effect absorbed by wave dummies; see Table C6.7.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.6.2 Robustness: Britishness (Categorical) {#sec-c6-brit-cat}

The categorical RE specifications confirm the gradient structure and moderation patterns documented in Section C.6.1. Britishness category coefficients are positive, precisely estimated, and monotonically ordered across all four indicators.

## C.6.2.1 National Unemployment Rate {#sec-c6-cat-brit-unemp}

```{r c6-cat-brit-unemp}
modelsummary(
  list("(1) No age" = models_unemp_cat_re$main, "(2) Age" = models_unemp_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.9. Unemployment Rate: Britishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = models_unemp_cat_re$int, "(2) + Age" = models_unemp_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.10. Unemployment Rate × Britishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.2.2 National Claimant Count {#sec-c6-cat-brit-claim}

```{r c6-cat-brit-claim}
modelsummary(
  list("(1) No age" = models_claim_cat_re$main, "(2) Age" = models_claim_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.11. Claimant Count: Britishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-brit-claim-int}
modelsummary(
  list("(1) Interaction" = models_claim_cat_re$int, "(2) + Age" = models_claim_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.12. Claimant Count × Britishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.2.3 GDP per Capita {#sec-c6-cat-brit-gdp}

```{r c6-cat-brit-gdp}
modelsummary(
  list("(1) No age" = models_gdp_cat_re$main, "(2) Age" = models_gdp_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.13. GDP per Capita: Britishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-brit-gdp-int}
modelsummary(
  list("(1) Interaction" = models_gdp_cat_re$int, "(2) + Age" = models_gdp_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.14. GDP per Capita × Britishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

## C.6.2.4 CPIH Inflation {#sec-c6-cat-brit-cpih}

```{r c6-cat-brit-cpih}
modelsummary(
  list("(1) No age" = models_cpih_cat_re$main, "(2) Age" = models_cpih_cat_re$main_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.15. CPIH Inflation: Britishness (Categorical) RE Main Effects",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

```{r c6-cat-brit-cpih-int}
modelsummary(
  list("(1) Interaction" = models_cpih_cat_re$int, "(2) + Age" = models_cpih_cat_re$int_age),
  coef_omit = OMIT_WAVE, gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title = "Table C6.16. CPIH Inflation × Britishness (Categorical): RE Interaction",
  notes = "REML. Random intercept + wave dummies. Reference: Britishness = 7. DV: immigSelf.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

# C.6.5 Auxiliary: Do Macro Conditions Predict Britishness? {#sec-c6-rob-brit}

None of the four macro indicators predicts within-individual changes in Britishness, confirming that the interaction effects in Sections C.6.1–C.6.2 reflect contextual moderation rather than macro-induced identity change.

```{r c6-rob-brit}
modelsummary(
  list("GDP" = brit_econ_rob_re$gdp, "Unemp." = brit_econ_rob_re$unemp,
       "Claimant" = brit_econ_rob_re$claim, "CPIH" = brit_econ_rob_re$cpih),
  coef_omit   = OMIT_WAVE,
  coef_rename = c(gdp_pc = "GDP per capita", unempl_rate = "Nat. unemp. rate",
                  claimant_k = "Claimant count", cpih_rate = "CPIH inflation"),
  gof_map = GOF_MAP, stars = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table C6.33. Auxiliary: Do Macro Conditions Predict Britishness? (RE)",
  notes   = "REML. Random intercept + cubic wave polynomial. DV: Britishness (1-7). Wave polynomial suppressed.",
  escape = FALSE, output = "kableExtra"
) |> kable_styling()
```

---

*End of Appendix C.6a. See Appendix C.6b for Englishness specifications.*
