---
title: "Online Appendix B.6: Meso-Level Models — Random Effects"
subtitle: "Estimator Comparison for Constituency-Level Economic Context (Britishness and Englishness)"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-float: true
    toc-location: left
    theme: cosmo
    embed-resources: true
    echo: false
    warning: false
    message: false
    fig-width: 8
    fig-height: 5
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(haven)
library(purrr)
library(lme4)
library(lmerTest)
library(modelsummary)
library(kableExtra)

options(modelsummary_factory_default = "kableExtra")

GOF_MAP <- tribble(
  ~raw,            ~clean,         ~fmt,
  "nobs",          "Observations", 0,
  "adj.r.squared", "Adj. R²",      3,
  "r.squared",     "R²",           3,
  "AIC",           "AIC",          1,
  "BIC",           "BIC",          1
)

# bobyqa + fixed wave dummies throughout (same strategy as Appendix A.6 v2)
ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

df <- readRDS("~/Library/CloudStorage/OneDrive-UniversityofGlasgow/BES/BES/BES_subset_panel_full_v3_England.rds")

DV_BASE          <- "immigSelf"
BRIT_BASE        <- "britishness"
ENG_BASE         <- "englishness"
TIME_BASE        <- "starttime"
AGE_BASE         <- "age"
MESO_UNEMP_BASE  <- "unemp_rate_mean"
MESO_CLAIM_BASE  <- "claimant_mean"
MESO_INCOME_BASE <- "income"

get_wave <- function(x) as.integer(str_extract(x, "\\d+$"))

waves_available <- function(df, base) {
  vars <- names(df)[str_detect(names(df), paste0("^", base, "W\\d+$"))]
  sort(unique(map_int(vars, get_wave)))
}

make_meso_long <- function(df, base, out_name, waves_keep) {
  cols <- names(df) |> str_subset(paste0("^", base, "W\\d+$"))
  if (length(cols) == 0) return(NULL)
  tmp <- tibble(col = cols) |>
    mutate(wave = as.integer(str_extract(col, "\\d+$"))) |>
    filter(wave %in% waves_keep)
  if (nrow(tmp) == 0) return(NULL)
  use_cols <- tmp$col
  df |>
    select(id, all_of(use_cols)) |>
    mutate(across(all_of(use_cols),
                  ~ as.numeric(if (inherits(.x, "haven_labelled")) zap_labels(.x) else .x))) |>
    pivot_longer(cols = -id, names_to = "wave", values_to = out_name,
                 names_pattern = paste0("^", base, "W(\\d+)$")) |>
    mutate(wave = as.integer(wave))
}
```

```{r build-panels-brit, include=FALSE}
w_dv   <- waves_available(df, DV_BASE)
w_brit <- waves_available(df, BRIT_BASE)
w_time <- waves_available(df, TIME_BASE)
w_age  <- waves_available(df, AGE_BASE)

waves      <- Reduce(intersect, list(w_dv, w_brit, w_time))
waves_age  <- intersect(waves, w_age)

core_cols <- c(
  paste0(DV_BASE,   "W", waves),
  paste0(BRIT_BASE, "W", waves),
  paste0(TIME_BASE, "W", waves),
  paste0(AGE_BASE,  "W", waves_age)
)

panel_long <- df |>
  mutate(across(any_of(core_cols), ~ {
    x <- .x; if (inherits(x, "haven_labelled")) x <- zap_labels(x); x
  })) |>
  select(id, any_of(core_cols)) |>
  pivot_longer(cols = -id, names_to = c(".value", "wave"),
               names_pattern = "(.+)W(\\d+)$") |>
  mutate(
    wave             = as.integer(wave),
    starttime_chr    = as.character(.data[[TIME_BASE]]),
    starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
    starttime_parsed = coalesce(starttime_parsed,
                                suppressWarnings(ymd(starttime_chr, quiet = TRUE))),
    year = year(starttime_parsed)
  ) |>
  rename(dv = all_of(DV_BASE), brit = all_of(BRIT_BASE), age = all_of(AGE_BASE)) |>
  mutate(dv = as.numeric(dv), brit = as.numeric(brit), age = as.numeric(age)) |>
  filter(!is.na(dv), !is.na(brit), !is.na(wave))

meso_unemp  <- make_meso_long(df, MESO_UNEMP_BASE,  "unemp_rate_mean", waves)
meso_claim  <- make_meso_long(df, MESO_CLAIM_BASE,  "claimant_mean",   waves)
meso_income <- make_meso_long(df, MESO_INCOME_BASE, "income_meso",     waves)

panel_meso <- panel_long
if (!is.null(meso_unemp))  panel_meso <- left_join(panel_meso, meso_unemp,  by = c("id", "wave"))
if (!is.null(meso_claim))  panel_meso <- left_join(panel_meso, meso_claim,  by = c("id", "wave"))
if (!is.null(meso_income)) panel_meso <- left_join(panel_meso, meso_income, by = c("id", "wave"))

# categorical panels
panel_meso_cat <- panel_meso |>
  mutate(brit = as.numeric(haven::zap_labels(brit)),
         age  = as.numeric(haven::zap_labels(age)),
         dv   = as.numeric(haven::zap_labels(dv))) |>
  filter(!is.na(dv), !is.na(brit), brit %in% 1:7, !is.na(wave)) |>
  mutate(brit_cat = relevel(factor(brit, levels = 1:7), ref = "7"))
```

```{r build-panels-engl, include=FALSE}
w_eng      <- waves_available(df, ENG_BASE)
waves_eng  <- Reduce(intersect, list(w_dv, w_eng, w_time))
waves_eng_age <- intersect(waves_eng, w_age)

core_cols_eng <- c(
  paste0(DV_BASE,  "W", waves_eng),
  paste0(ENG_BASE, "W", waves_eng),
  paste0(TIME_BASE,"W", waves_eng),
  paste0(AGE_BASE, "W", waves_eng_age)
)

panel_long_eng <- df |>
  mutate(across(any_of(core_cols_eng), ~ {
    x <- .x; if (inherits(x, "haven_labelled")) x <- zap_labels(x); x
  })) |>
  select(id, any_of(core_cols_eng)) |>
  pivot_longer(cols = -id, names_to = c(".value", "wave"),
               names_pattern = "(.+)W(\\d+)$") |>
  mutate(
    wave             = as.integer(wave),
    starttime_chr    = as.character(.data[[TIME_BASE]]),
    starttime_parsed = suppressWarnings(ymd_hms(starttime_chr, quiet = TRUE)),
    starttime_parsed = coalesce(starttime_parsed,
                                suppressWarnings(ymd(starttime_chr, quiet = TRUE))),
    year = year(starttime_parsed)
  ) |>
  rename(dv = all_of(DV_BASE), engl = all_of(ENG_BASE), age = all_of(AGE_BASE)) |>
  mutate(
    dv   = as.numeric(dv),
    engl = as.numeric(engl),
    age  = as.numeric(age),
    engl = dplyr::na_if(engl, 9999)
  ) |>
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave))

meso_unemp_eng  <- make_meso_long(df, MESO_UNEMP_BASE,  "unemp_rate_mean", waves_eng)
meso_claim_eng  <- make_meso_long(df, MESO_CLAIM_BASE,  "claimant_mean",   waves_eng)
meso_income_eng <- make_meso_long(df, MESO_INCOME_BASE, "income_meso",     waves_eng)

panel_meso_eng <- panel_long_eng
if (!is.null(meso_unemp_eng))  panel_meso_eng <- left_join(panel_meso_eng, meso_unemp_eng,  by = c("id", "wave"))
if (!is.null(meso_claim_eng))  panel_meso_eng <- left_join(panel_meso_eng, meso_claim_eng,  by = c("id", "wave"))
if (!is.null(meso_income_eng)) panel_meso_eng <- left_join(panel_meso_eng, meso_income_eng, by = c("id", "wave"))

panel_meso_eng_cat <- panel_meso_eng |>
  mutate(engl = as.numeric(if (inherits(engl, "haven_labelled")) haven::zap_labels(engl) else engl),
         age  = as.numeric(if (inherits(age,  "haven_labelled")) haven::zap_labels(age)  else age),
         dv   = as.numeric(if (inherits(dv,   "haven_labelled")) haven::zap_labels(dv)   else dv),
         engl = dplyr::na_if(engl, 9999)) |>
  filter(!is.na(dv), !is.na(engl), engl %in% 1:7, !is.na(wave)) |>
  mutate(engl_cat = relevel(factor(engl, levels = 1:7), ref = "7"))
```

```{r estimate-brit, include=FALSE}
panel_u <- panel_meso |> filter(!is.na(unemp_rate_mean))
panel_c <- panel_meso |> filter(!is.na(claimant_mean))
panel_i <- panel_meso |> filter(!is.na(income_meso))

# Unemployment — Britishness continuous
m_u0.1_re <- lmer(dv ~ unemp_rate_mean             + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)
m_u1_re   <- lmer(dv ~ brit + unemp_rate_mean       + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)
m_u0.2_re <- lmer(dv ~ unemp_rate_mean + age        + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)
m_u2_re   <- lmer(dv ~ brit + unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)
m_u3_re   <- lmer(dv ~ brit * unemp_rate_mean       + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)
m_u4_re   <- lmer(dv ~ brit * unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u, REML = TRUE, control = ctrl)

# Claimant — Britishness continuous
m_c0.1_re <- lmer(dv ~ claimant_mean               + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)
m_c1_re   <- lmer(dv ~ brit + claimant_mean         + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)
m_c0.2_re <- lmer(dv ~ claimant_mean + age          + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)
m_c2_re   <- lmer(dv ~ brit + claimant_mean + age   + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)
m_c3_re   <- lmer(dv ~ brit * claimant_mean         + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)
m_c4_re   <- lmer(dv ~ brit * claimant_mean + age   + factor(wave) + (1|id), data = panel_c, REML = TRUE, control = ctrl)

# Income — Britishness continuous
m_i0.1_re <- lmer(dv ~ income_meso                 + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
m_i1_re   <- lmer(dv ~ brit + income_meso           + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
m_i0.2_re <- lmer(dv ~ income_meso + age            + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
m_i2_re   <- lmer(dv ~ brit + income_meso + age     + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
m_i3_re   <- lmer(dv ~ brit * income_meso           + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
m_i4_re   <- lmer(dv ~ brit * income_meso + age     + factor(wave) + (1|id), data = panel_i, REML = TRUE, control = ctrl)
```

```{r estimate-brit-cat, include=FALSE}
panel_u_cat <- panel_meso_cat |> filter(!is.na(unemp_rate_mean))
panel_c_cat <- panel_meso_cat |> filter(!is.na(claimant_mean))
panel_i_cat <- panel_meso_cat |> filter(!is.na(income_meso))

m_u1_cat_re <- lmer(dv ~ brit_cat + unemp_rate_mean       + factor(wave) + (1|id), data = panel_u_cat, REML = TRUE, control = ctrl)
m_u2_cat_re <- lmer(dv ~ brit_cat + unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u_cat, REML = TRUE, control = ctrl)
m_u3_cat_re <- lmer(dv ~ brit_cat * unemp_rate_mean       + factor(wave) + (1|id), data = panel_u_cat, REML = TRUE, control = ctrl)
m_u4_cat_re <- lmer(dv ~ brit_cat * unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u_cat, REML = TRUE, control = ctrl)

m_c1_cat_re <- lmer(dv ~ brit_cat + claimant_mean         + factor(wave) + (1|id), data = panel_c_cat, REML = TRUE, control = ctrl)
m_c2_cat_re <- lmer(dv ~ brit_cat + claimant_mean + age   + factor(wave) + (1|id), data = panel_c_cat, REML = TRUE, control = ctrl)
m_c3_cat_re <- lmer(dv ~ brit_cat * claimant_mean         + factor(wave) + (1|id), data = panel_c_cat, REML = TRUE, control = ctrl)
m_c4_cat_re <- lmer(dv ~ brit_cat * claimant_mean + age   + factor(wave) + (1|id), data = panel_c_cat, REML = TRUE, control = ctrl)

m_i1_cat_re <- lmer(dv ~ brit_cat + income_meso           + factor(wave) + (1|id), data = panel_i_cat, REML = TRUE, control = ctrl)
m_i2_cat_re <- lmer(dv ~ brit_cat + income_meso + age     + factor(wave) + (1|id), data = panel_i_cat, REML = TRUE, control = ctrl)
# No categorical × income interaction tables (see note in B.6.2.3)
```

```{r estimate-engl, include=FALSE}
panel_u_eng <- panel_meso_eng |> filter(!is.na(unemp_rate_mean))
panel_c_eng <- panel_meso_eng |> filter(!is.na(claimant_mean))
panel_i_eng <- panel_meso_eng |> filter(!is.na(income_meso))

m_u0.1_eng_re <- lmer(dv ~ unemp_rate_mean              + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)
m_u1_eng_re   <- lmer(dv ~ engl + unemp_rate_mean        + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)
m_u0.2_eng_re <- lmer(dv ~ unemp_rate_mean + age         + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)
m_u2_eng_re   <- lmer(dv ~ engl + unemp_rate_mean + age  + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)
m_u3_eng_re   <- lmer(dv ~ engl * unemp_rate_mean        + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)
m_u4_eng_re   <- lmer(dv ~ engl * unemp_rate_mean + age  + factor(wave) + (1|id), data = panel_u_eng, REML = TRUE, control = ctrl)

m_c0.1_eng_re <- lmer(dv ~ claimant_mean                 + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)
m_c1_eng_re   <- lmer(dv ~ engl + claimant_mean          + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)
m_c0.2_eng_re <- lmer(dv ~ claimant_mean + age           + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)
m_c2_eng_re   <- lmer(dv ~ engl + claimant_mean + age    + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)
m_c3_eng_re   <- lmer(dv ~ engl * claimant_mean          + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)
m_c4_eng_re   <- lmer(dv ~ engl * claimant_mean + age    + factor(wave) + (1|id), data = panel_c_eng, REML = TRUE, control = ctrl)

m_i0.1_eng_re <- lmer(dv ~ income_meso                   + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
m_i1_eng_re   <- lmer(dv ~ engl + income_meso            + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
m_i0.2_eng_re <- lmer(dv ~ income_meso + age             + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
m_i2_eng_re   <- lmer(dv ~ engl + income_meso + age      + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
m_i3_eng_re   <- lmer(dv ~ engl * income_meso            + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
m_i4_eng_re   <- lmer(dv ~ engl * income_meso + age      + factor(wave) + (1|id), data = panel_i_eng, REML = TRUE, control = ctrl)
```

```{r estimate-engl-cat, include=FALSE}
panel_u_eng_cat <- panel_meso_eng_cat |> filter(!is.na(unemp_rate_mean))
panel_c_eng_cat <- panel_meso_eng_cat |> filter(!is.na(claimant_mean))
panel_i_eng_cat <- panel_meso_eng_cat |> filter(!is.na(income_meso))

m_u1_eng_cat_re <- lmer(dv ~ engl_cat + unemp_rate_mean       + factor(wave) + (1|id), data = panel_u_eng_cat, REML = TRUE, control = ctrl)
m_u2_eng_cat_re <- lmer(dv ~ engl_cat + unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u_eng_cat, REML = TRUE, control = ctrl)
m_u3_eng_cat_re <- lmer(dv ~ engl_cat * unemp_rate_mean       + factor(wave) + (1|id), data = panel_u_eng_cat, REML = TRUE, control = ctrl)
m_u4_eng_cat_re <- lmer(dv ~ engl_cat * unemp_rate_mean + age + factor(wave) + (1|id), data = panel_u_eng_cat, REML = TRUE, control = ctrl)

m_c1_eng_cat_re <- lmer(dv ~ engl_cat + claimant_mean         + factor(wave) + (1|id), data = panel_c_eng_cat, REML = TRUE, control = ctrl)
m_c2_eng_cat_re <- lmer(dv ~ engl_cat + claimant_mean + age   + factor(wave) + (1|id), data = panel_c_eng_cat, REML = TRUE, control = ctrl)
m_c3_eng_cat_re <- lmer(dv ~ engl_cat * claimant_mean         + factor(wave) + (1|id), data = panel_c_eng_cat, REML = TRUE, control = ctrl)
m_c4_eng_cat_re <- lmer(dv ~ engl_cat * claimant_mean + age   + factor(wave) + (1|id), data = panel_c_eng_cat, REML = TRUE, control = ctrl)

m_i1_eng_cat_re <- lmer(dv ~ engl_cat + income_meso           + factor(wave) + (1|id), data = panel_i_eng_cat, REML = TRUE, control = ctrl)
m_i2_eng_cat_re <- lmer(dv ~ engl_cat + income_meso + age     + factor(wave) + (1|id), data = panel_i_eng_cat, REML = TRUE, control = ctrl)
# No categorical × income interaction tables (see note in B.6.4.3)
```

---

This appendix reports random-effects (RE) equivalents of the fixed-effects meso-level models in Appendix B. All RE models are estimated via REML with a random intercept for respondent (`1|id`); wave effects are modelled as fixed dummies (`factor(wave)`), consistent with the identification strategy of Appendix B and avoiding the instability of estimating a wave-level variance component from the small number of available survey waves. Unlike the individual FE estimator, the RE estimator draws on both within- and between-person covariance, so RE identity coefficients are substantially larger throughout. Where RE and FE interaction terms converge, confidence in the underlying signal is strengthened; where they diverge, a significant RE interaction alongside a null FE interaction indicates stable cross-sectional sorting rather than within-individual activation of the kind the paper's theoretical arguments require. This interpretive frame applies throughout Sections B.6.1–B.6.4. Wave dummy coefficients are suppressed from all tables for readability.

---

# B.6.1 Main Models: Britishness (Continuous) {#sec-b6-brit}

## B.6.1.1 Local Unemployment Rate {#sec-b6-brit-unemp}

The RE unemployment main-effect coefficients are comparable in sign and direction to the FE estimates in Appendix B.1, though the Britishness coefficient is larger under RE as expected. The interaction structure mirrors the FE pattern: higher local unemployment is associated with more restrictive attitudes among weaker identifiers, and the interaction term is negative and significant, indicating attenuation as Britishness increases. Where the RE interaction is larger in magnitude than the FE counterpart, this reflects the additional between-person sorting captured by the RE estimator — more strongly British respondents in persistently lower-unemployment areas. The FE estimate remains the preferred test of within-person activation.

```{r b6-brit-unemp-main}
modelsummary(
  list(
    "(1) Unemp only"    = m_u0.1_re,
    "(2) + Britishness" = m_u1_re,
    "(3) Unemp + Age"   = m_u0.2_re,
    "(4) + Britishness" = m_u2_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", unemp_rate_mean = "Unemp. rate (local)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.1. Local Unemployment Rate: Random-Effects Main Effects (Britishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-brit-unemp-int}
modelsummary(
  list(
    "(1) Interaction"       = m_u3_re,
    "(2) Interaction + Age" = m_u4_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", unemp_rate_mean = "Unemp. rate (local)",
                  "brit:unemp_rate_mean" = "Britishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.2. Local Unemployment Rate × Britishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## B.6.1.2 Claimant Count {#sec-b6-brit-claimant}

The claimant-count RE results closely parallel the unemployment pattern. The RE interaction is negative and significant, consistent with the FE evidence in Appendix B.1. Any excess magnitude relative to the FE estimate reflects the between-person component — persistently more strongly British respondents living in areas with lower welfare dependency — rather than within-individual activation. The null FE result therefore remains the appropriate benchmark for H2 at the meso level.

```{r b6-brit-claimant-main}
modelsummary(
  list(
    "(1) Claimant only"  = m_c0.1_re,
    "(2) + Britishness"  = m_c1_re,
    "(3) Claimant + Age" = m_c0.2_re,
    "(4) + Britishness"  = m_c2_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", claimant_mean = "Claimant count (local)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.3. Claimant Count: Random-Effects Main Effects (Britishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-brit-claimant-int}
modelsummary(
  list(
    "(1) Interaction"       = m_c3_re,
    "(2) Interaction + Age" = m_c4_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", claimant_mean = "Claimant count (local)",
                  "brit:claimant_mean" = "Britishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.4. Claimant Count × Britishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## B.6.1.3 Local Income (ASHE) {#sec-b6-brit-income}

As in the FE models of Appendix B.1, local income shows no significant main effect or interaction with Britishness under RE. This null is stable across all specifications and is not an artefact of the FE design: the absence of an income effect persists even when the between-person component is included. This consistency reinforces the substantive conclusion that constituency-level prosperity, as distinct from labour-market insecurity and welfare exposure, does not shape immigration attitudes through either within-person change or cross-sectional sorting.

```{r b6-brit-income-main}
modelsummary(
  list(
    "(1) Income only"   = m_i0.1_re,
    "(2) + Britishness" = m_i1_re,
    "(3) Income + Age"  = m_i0.2_re,
    "(4) + Britishness" = m_i2_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", income_meso = "Local income (ASHE)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.5. Local Income (ASHE): Random-Effects Main Effects (Britishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-brit-income-int}
modelsummary(
  list(
    "(1) Interaction"       = m_i3_re,
    "(2) Interaction + Age" = m_i4_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(brit = "Britishness", income_meso = "Local income (ASHE)",
                  "brit:income_meso" = "Britishness × Local income", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.6. Local Income (ASHE) × Britishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

---

# B.6.2 Robustness: Britishness (Categorical) {#sec-b6-brit-cat}

The categorical RE specifications confirm the gradient structure observed in Appendix B.2. Britishness category coefficients are positive, precisely estimated, and monotonically ordered across all three indicators, consistent with the FE categorical results. For unemployment and claimant count, categorical interaction models reveal conditional effects concentrated among weaker and intermediate identity positions, paralleling the FE patterns in Appendix B.2. Income categorical interactions are not reported here — as in Appendix A.6.5, between-person income sorting does not follow a coherent identity gradient, and the FE categorical income results in Appendix B.2 remain the appropriate reference.

## B.6.2.1 Local Unemployment Rate {#sec-b6-cat-brit-unemp}

```{r b6-cat-brit-unemp-main}
modelsummary(
  list("(1) No age" = m_u1_cat_re, "(2) Age" = m_u2_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.7. Local Unemployment Rate: Britishness (Categorical) RE Main Effects",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Britishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

```{r b6-cat-brit-unemp-int}
modelsummary(
  list("(1) Interaction" = m_u3_cat_re, "(2) Interaction + Age" = m_u4_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.8. Local Unemployment Rate × Britishness (Categorical): RE Interaction",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Britishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

## B.6.2.2 Claimant Count {#sec-b6-cat-brit-claimant}

```{r b6-cat-brit-claimant-main}
modelsummary(
  list("(1) No age" = m_c1_cat_re, "(2) Age" = m_c2_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.9. Claimant Count: Britishness (Categorical) RE Main Effects",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Britishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

```{r b6-cat-brit-claimant-int}
modelsummary(
  list("(1) Interaction" = m_c3_cat_re, "(2) Interaction + Age" = m_c4_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.10. Claimant Count × Britishness (Categorical): RE Interaction",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Britishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

## B.6.2.3 Local Income (ASHE) {#sec-b6-cat-brit-income}

Income categorical interaction terms are not reported in this appendix. As discussed in Appendix A.6, the between-person income sorting observed in the continuous RE models does not reflect a coherent activation gradient across identity positions, and the categorical × income interaction models are computationally expensive without adding interpretive value. The additive categorical baseline below confirms that the Britishness gradient is stable after conditioning on local income.

```{r b6-cat-brit-income-main}
modelsummary(
  list("(1) No age" = m_i1_cat_re, "(2) Age" = m_i2_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.11. Local Income (ASHE): Britishness (Categorical) RE Additive Models",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Britishness = 7. Interaction models not shown; see text.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

---

# B.6.3 Main Models: Englishness (Continuous) {#sec-b6-engl}

The Englishness RE meso models replicate the Britishness structure but with the identity dimension replaced by Englishness, following the same logic as Appendix B.3. RE Englishness coefficients are larger than their FE counterparts for the same reason as Britishness: the between-person component — persistently more strongly English respondents holding more restrictive preferences — is added to the within-individual signal. The divergence between RE and FE interaction terms again indicates between-person sorting wherever it appears, and the FE null remains the preferred test for within-individual activation at the meso level.

## B.6.3.1 Local Unemployment Rate {#sec-b6-engl-unemp}

```{r b6-engl-unemp-main}
modelsummary(
  list(
    "(1) Unemp only"    = m_u0.1_eng_re,
    "(2) + Englishness" = m_u1_eng_re,
    "(3) Unemp + Age"   = m_u0.2_eng_re,
    "(4) + Englishness" = m_u2_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", unemp_rate_mean = "Unemp. rate (local)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.12. Local Unemployment Rate: Random-Effects Main Effects (Englishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-engl-unemp-int}
modelsummary(
  list(
    "(1) Interaction"       = m_u3_eng_re,
    "(2) Interaction + Age" = m_u4_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", unemp_rate_mean = "Unemp. rate (local)",
                  "engl:unemp_rate_mean" = "Englishness × Unemp. rate", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.13. Local Unemployment Rate × Englishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## B.6.3.2 Claimant Count {#sec-b6-engl-claimant}

```{r b6-engl-claimant-main}
modelsummary(
  list(
    "(1) Claimant only"  = m_c0.1_eng_re,
    "(2) + Englishness"  = m_c1_eng_re,
    "(3) Claimant + Age" = m_c0.2_eng_re,
    "(4) + Englishness"  = m_c2_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", claimant_mean = "Claimant count (local)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.14. Claimant Count: Random-Effects Main Effects (Englishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-engl-claimant-int}
modelsummary(
  list(
    "(1) Interaction"       = m_c3_eng_re,
    "(2) Interaction + Age" = m_c4_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", claimant_mean = "Claimant count (local)",
                  "engl:claimant_mean" = "Englishness × Claimant count", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.15. Claimant Count × Englishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

## B.6.3.3 Local Income (ASHE) {#sec-b6-engl-income}

As in Appendix B.3, the Englishness income interaction displays a small but discernible conditional structure under RE that is absent in the Britishness models. Where significant, this reflects primarily the between-person component — wealthier-area respondents with lower Englishness holding more permissive attitudes in cross-section — rather than within-individual income activation. The FE null in Appendix B.3 remains the appropriate benchmark.

```{r b6-engl-income-main}
modelsummary(
  list(
    "(1) Income only"   = m_i0.1_eng_re,
    "(2) + Englishness" = m_i1_eng_re,
    "(3) Income + Age"  = m_i0.2_eng_re,
    "(4) + Englishness" = m_i2_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", income_meso = "Local income (ASHE)", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.16. Local Income (ASHE): Random-Effects Main Effects (Englishness)",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

```{r b6-engl-income-int}
modelsummary(
  list(
    "(1) Interaction"       = m_i3_eng_re,
    "(2) Interaction + Age" = m_i4_eng_re
  ),
  coef_omit   = "factor\\(wave\\)",
  coef_rename = c(engl = "Englishness", income_meso = "Local income (ASHE)",
                  "engl:income_meso" = "Englishness × Local income", age = "Age"),
  gof_map = GOF_MAP,
  stars   = c("*" = .05, "**" = .01, "***" = .001),
  title   = "Table B6.17. Local Income (ASHE) × Englishness: Random-Effects Interaction",
  notes   = "REML estimation. Random intercept for respondent. Wave dummies included but suppressed. DV: immigSelf.",
  escape  = FALSE,
  output  = "kableExtra"
) |> kable_styling()
```

---

# B.6.4 Robustness: Englishness (Categorical) {#sec-b6-engl-cat}

The categorical Englishness RE specifications confirm the gradient structure observed in Appendix B.4. Englishness category coefficients are positive, precisely estimated, and monotonically ordered. For unemployment and claimant count, conditional effects under RE are concentrated among weaker identity positions, consistent with the FE categorical patterns. As for Britishness, income categorical interaction models are not reported; the additive baseline confirms that the Englishness gradient is stable after conditioning on local income.

## B.6.4.1 Local Unemployment Rate {#sec-b6-cat-engl-unemp}

```{r b6-cat-engl-unemp-main}
modelsummary(
  list("(1) No age" = m_u1_eng_cat_re, "(2) Age" = m_u2_eng_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.18. Local Unemployment Rate: Englishness (Categorical) RE Main Effects",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Englishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

```{r b6-cat-engl-unemp-int}
modelsummary(
  list("(1) Interaction" = m_u3_eng_cat_re, "(2) Interaction + Age" = m_u4_eng_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.19. Local Unemployment Rate × Englishness (Categorical): RE Interaction",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Englishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

## B.6.4.2 Claimant Count {#sec-b6-cat-engl-claimant}

```{r b6-cat-engl-claimant-main}
modelsummary(
  list("(1) No age" = m_c1_eng_cat_re, "(2) Age" = m_c2_eng_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.20. Claimant Count: Englishness (Categorical) RE Main Effects",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Englishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

```{r b6-cat-engl-claimant-int}
modelsummary(
  list("(1) Interaction" = m_c3_eng_cat_re, "(2) Interaction + Age" = m_c4_eng_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.21. Claimant Count × Englishness (Categorical): RE Interaction",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Englishness = 7.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

## B.6.4.3 Local Income (ASHE) {#sec-b6-cat-engl-income}

Income categorical interaction models are not reported here for the same reasons as B.6.2.3. The additive baseline confirms that the Englishness gradient is stable after conditioning on local income.

```{r b6-cat-engl-income-main}
modelsummary(
  list("(1) No age" = m_i1_eng_cat_re, "(2) Age" = m_i2_eng_cat_re),
  coef_omit = "factor\\(wave\\)",
  gof_map   = GOF_MAP,
  stars     = c("*" = .05, "**" = .01, "***" = .001),
  title     = "Table B6.22. Local Income (ASHE): Englishness (Categorical) RE Additive Models",
  notes     = "REML estimation. Random intercept for respondent. Wave dummies suppressed. Reference: Englishness = 7. Interaction models not shown; see text.",
  escape    = FALSE,
  output    = "kableExtra"
) |> kable_styling()
```

---

*End of Appendix B.6.*
